---
title: "GTM_4_dim_var_process"
author: "Meng Luo"
date: "2023-08-29"
output: html_document
    toc: true
    toc_float: true
---
# use the mature age's FP as the input for GCAM


#########################################################
## update of the this version
# add FULL_matrix_for_MFP_continue

# Content
## link to github
  S0 link to github
## Setting Up
  S1 needed R package and dir
 
  
  
  
  
# link to github
```{r S0 link to github , include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
```

# Setting Up
## Loading Needed R Packages and Setting Directory

```{r S1 needed R package and dir }
library(tidyverse)
library(tidyr)
#install.packages("rlang")
library(rlang)
library(dplyr)
library(gcamdata)
library('drake')
## run this in console devtools::load_all()

#################################################################################################
## need to modify 
 
# Chen lab desktop
root<-"O:/"

# 2023 laptop
root<-"D:/"

## ssp1




## ssp3




## ssp5
scenario<-"585" #  n for SSPn e.g. 1 for SSP1
version_num <-"1"
case_name<-"_climate_productivityC"




## end of need to modify 
#################################################################################################



main_Sagb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_aboveCD/region_5ymean_alltypes_wrapper/")


main_Sbgb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_belowCD/region_5ymean_alltypes_wrapper/")


# choose aggregation methods #####################
# 1 is agg A1 first, then LC1
# 2 is agg LC1 first, then A1
# 3 is using FP for the mature age


XML_version <- paste0(version_num ,case_name,"_ssp",scenario) 

## end need to modify 
#########################







main_GTM_mid_xml_path  <-"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/useful/"
main_my_XML_path <- "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/new_XML/"
# produce outputs in GCAM 7.0 release package 
main_v7_XML_path <- "E/Docker_GCAM_v7_forest/gcam-master/input/gcamdata/xml/"

fig_save_path <- paste0(root,"E/new laptop2/PHD/my_2024_1_manuscript/Figure&table/figure/check_npp_rh_scaler_4in1_file/")

```


## read GTM output txt file
separate each var and save in csv

# function section


```{r S2 function save_result }
save_csv_result <- function(result_DF, result_csv_name,row_names) {

full_save_path <- paste0(root,main_GTM_path, result_csv_name)
if (row_names == TRUE) {
write.csv(result_DF,full_save_path, row.names = TRUE)
} else {
write.csv(result_DF,full_save_path, row.names = FALSE)
}

}
```

# preprocessing for GCAM XML
## I am right here


```{r S2 automatically read the file}




agb_files <- list.files(path = main_Sagb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)


bgb_files <- list.files(path = main_Sbgb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)

print(agb_files)
print(bgb_files)
```


```{r S3 read detailed land area in each subregion }
detailed_land_area_main_path<-paste0(root,"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM_db_extact_dat/CSV/")

in_all_gfdl_area<-read.csv(paste0(detailed_land_area_main_path,"detailed.land.allocation.SSP126_v3_classic_gfdl_default_updateall_fixed.csv"))%>%
  rename(all_area=value)
  
in_orifor_gfdl_area<-read.csv(paste0(detailed_land_area_main_path,"detailed.land.allocation.SSP126_v3_classic_gfdl_default_updateall_orifor_fixed.csv"))%>%
  rename(orifor_area=value)
  

in_ori_area<-read.csv(paste0(detailed_land_area_main_path,"detailed.land.allocation.SSP126_v3_ori.csv"))%>%
 rename(ori_area=value)



in_area_combined <-in_ori_area%>%
  left_join(in_orifor_gfdl_area, by=c("Units","scenario","region","landleaf","year"))%>%
  left_join(in_all_gfdl_area, by=c("Units","scenario","region","landleaf","year"))%>%
  filter(year>=2015)

  


```

```{r read the C density of above, below}
```



```{r plot and save bgb scaler group map}

# for (data_idx in 5:6) {
#   # data_idx<-1
#   in_Sbgb_file <- bgb_files[data_idx]
#   in_Sbgb <- read.csv(in_Sbgb_file, check.names = FALSE)
# 
#   bgb_file_name <- basename(in_Sbgb_file)
#   desired_name_part <- sub("_fullscaler.*", "", bgb_file_name)
# 
#   check_belowCD_long <- in_Sbgb %>%
#     dplyr::select(-3,-2) %>%
#     filter( harm_type!= "Other")%>%
#     left_join(in_Harmolandtype_area,
#               by = c("out_reg_code", "out_lu_code", "harm_type")) %>%
#     
#     group_by(region, harm_type) %>%
#     mutate(region_pft_area = sum(pft_area_total, na.rm = TRUE)) %>%
#     mutate(region_pft_area_weight = pft_area_total / region_pft_area) %>%
#     summarize(across(
#       .cols = 8:22,
#       .fns = ~ weighted.mean(.x, w = region_pft_area_weight, na.rm = TRUE)
#     )) %>%
#     ungroup() %>%
#     pivot_longer(cols = 3:ncol(.),
#                  names_to = "year",
#                  values_to = "scaler") %>%
#     mutate(year = as.numeric(year)) %>%
#     na.omit()
#   
#   
#   # Create individual plots
#   pc3 <- ggplot(check_belowCD_long %>% filter(harm_type == "c3Crop"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
#     geom_line() +
#     labs(title = paste0("bgb c3Crop scaler_", desired_name_part),
#          x = "Year",
#          y = "Value",
#          color = "Region") +
#     theme_minimal()
# 
#   pc4 <- ggplot(check_belowCD_long %>% filter(harm_type == "c4Crop"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
#     geom_line() +
#     labs(title = paste0("bgb c4Crop scaler_", desired_name_part),
#          x = "Year",
#          y = "Value",
#          color = "Region") +
#     theme_minimal()
# 
#   pf <- ggplot(check_belowCD_long %>% filter(harm_type == "Forest"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
#     geom_line() +
#     labs(title = paste0("bgb Forest scaler_", desired_name_part),
#          x = "Year",
#          y = "Value",
#          color = "Region") +
#     theme_minimal()
# 
#   pg <- ggplot(check_belowCD_long %>% filter(harm_type == "Grass"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
#     geom_line() +
#     labs(title = paste0("bgb Grass scaler_", desired_name_part),
#          x = "Year",
#          y = "Value",
#          color = "Region") +
#     theme_minimal()
# 
#   # Combine the plots into one figure
#   combined_plot <- (pc3 + pc4) / (pf + pg) +
#     # plot_layout(guides = 'collect') +
#     plot_annotation(title = paste0("Combined bgb Scaler_", desired_name_part))
# 
#   
#     # combined_plot <- (pc3 + pc4) / (pf + pg) + plot_annotation(title = paste0("Combined agb scaler_", desired_name_part))
#   
#   # Save the combined plot
#   ggsave(paste0(fig_save_path, "/", desired_name_part, "_combined_Sbgb_regions.svg"), plot = combined_plot, width = 20, height = 20, units = "in")
#   ggsave(paste0(fig_save_path, "/", desired_name_part, "_combined_Sbgb_regions.png"), plot = combined_plot, width = 20, height = 20, units = "in", dpi = 300)
# 
#   ####################################################################
# 
#   check_belowCD_long_gmean <- in_Sbgb %>%
#     dplyr::select(-3, -2) %>%
#   filter( harm_type!= "Other")%>%
#     left_join(in_Harmolandtype_area,
#               by = c("out_reg_code", "out_lu_code", "harm_type")) %>%
#     
#     group_by(harm_type) %>%
#     mutate(global_pft_area = sum(pft_area_total, na.rm = TRUE)) %>%
#     mutate(global_pft_area_weight = pft_area_total / global_pft_area) %>%
#     summarize(across(
#       .cols = 8:22,
#       .fns = ~ weighted.mean(.x, w = global_pft_area_weight, na.rm = TRUE)
#     )) %>%
#     ungroup() %>%
#     pivot_longer(cols = 3:ncol(.),
#                  names_to = "year",
#                  values_to = "scaler") %>%
#     mutate(year = as.numeric(year)) %>%
#     na.omit()
# 
#   p2 <- ggplot(check_belowCD_long_gmean, aes(x = as.numeric(year), y = scaler, group = harm_type, color = harm_type)) +
#     geom_line() +
#     labs(title = paste0("global mean bgb scaler_", desired_name_part),
#          x = "Year",
#          y = "Value",
#          color = "harm_type") +
#     theme_minimal()
# 
#   # Save the global mean plot
#   ggsave(paste0(fig_save_path, "/", desired_name_part, "_Sbgb_global.svg"), plot = p2, width = 5, height = 5, units = "in")
#   ggsave(paste0(fig_save_path, "/", desired_name_part, "_Sbgb_global.png"), plot = p2, width = 5, height = 5, units = "in", dpi = 300)
# }

```
