---
title: "GTM_4_dim_var_process"
author: "Meng Luo"
date: "2023-08-29"
output: html_document
    toc: true
    toc_float: true
---
# use the mature age's FP as the input for GCAM


#########################################################
## update of the this version
# add FULL_matrix_for_MFP_continue

# Content
## link to github
  S0 link to github
## Setting Up
  S1 needed R package and dir
 
  
  
  
  
# link to github
```{r S0 link to github , include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
```

# Setting Up
## Loading Needed R Packages and Setting Directory

```{r S1 needed R package and dir }
#install.packages("drake")
library('drake')
#install.packages("cowplot")
library(cowplot)
############
require(devtools)
#Please use this in console if needed: install_github('JGCRI/rgcam', build_vignettes=TRUE, force =TRUE)
library (rgcam)
library(tidyverse)
library(tidyr)

library(rlang)
library(dplyr)
# install.packages("patchwork")
library(patchwork)
# install.packages("sf")
library(sf)
# install.packages("svglite")
library(svglite)
library(cowplot)
library(gridExtra)
library(ggthemes)
library(stringr)
library(ggplot2)
library(RColorBrewer)


## run this in console devtools::load_all()

Fig_num_name<-"Fig16_C_scalar"
version_num <-"4"
case_name<-"_climate_productivityC"
#################################################################################################
## need to modify 
# plot_case<-1 # diff SSPs
plot_case<-2 # diff CC component
 
cases<-c("3SSPs","CC_components")

case<-cases[plot_case]


## end of need to modify 
# read from hard disk ##############################################################
# # Chen lab desktop
# # root<-"O:/"
# 
# # 2023 laptop
# root<-"D:/"
# 
# 
# main_Sagb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_aboveCD/region_5ymean_alltypes_wrapper/")
# 
# 
# main_Sbgb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_belowCD/region_5ymean_alltypes_wrapper/")
# 
# 
# 
# XML_version <- paste0(version_num ,case_name,"_ssp",case) 

####

# main_GTM_mid_xml_path  <-"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/useful/"
# main_my_XML_path <- "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/new_XML/"
# # produce outputs in GCAM 7.0 release package 
# main_v7_XML_path <- "E/Docker_GCAM_v7_forest/gcam-master/input/gcamdata/xml/"
# 
# fig_save_path <- paste0(root,"E/new laptop2/PHD/my_2024_1_manuscript/Figure&table/figure/check_npp_rh_scaler_4in1_file/")

# Harmolandtype_area_main_path<-paste0(root,"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/")
# read from 2023 laptop  ##############################################################

# 2023 laptop
# root <- "C:/MengLuo/chapter 2_backup/"

# NAS
root <- "Z:/Meng/back_up_all/9_updates/"

########################################################################################


main_Sagb_path <- paste0(root, "climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_aboveCD/region_5ymean_alltypes_wrapper/")


main_Sbgb_path <- paste0(root, "climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_belowCD/region_5ymean_alltypes_wrapper/")

XML_version <- paste0(version_num ,case_name,"_ssp",case) 


#####

main_GTM_mid_xml_path  <-"climate_FPC_GCAM/Data/GCAM data system_forestversion/useful/"
main_my_XML_path <- "climate_FPC_GCAM/Data/GCAM data system_forestversion/new_XML/"
# produce outputs in GCAM 7.0 release package 
main_v7_XML_path <- "XML_save/"

fig_save_path <- paste0(root,"my_2024_1_manuscript/Figure&table/figure/check_npp_rh_scaler_4in1_file/")

Harmolandtype_area_main_path<-paste0(root,"climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/")



shp_path <- paste0(root, "climate_FPC_GCAM/Code/boundary/gcam_boundaries_moirai_3p1_0p5arcmin_wgs84/gcam_boundaries_moirai_3p1_0p5arcmin_wgs84/main_outputs/region_boundaries_moirai_combined_3p1_0p5arcmin.shp")

data_sf <- st_read(shp_path)
```


## read GTM output txt file
separate each var and save in csv

# function section


```{r S2 function save_result }
save_csv_result <- function(result_DF, result_csv_name,row_names) {

full_save_path <- paste0(root,main_GTM_path, result_csv_name)
if (row_names == TRUE) {
write.csv(result_DF,full_save_path, row.names = TRUE)
} else {
write.csv(result_DF,full_save_path, row.names = FALSE)
}

}
```

# preprocessing for GCAM XML
## I am right here


```{r S3 automatically read the file}

# agb_files <- list.files(path = main_Sagb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)
# 
# 
# bgb_files <- list.files(path = main_Sbgb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)
# 
# print(agb_files)
# print(bgb_files)
```

```{r S4 read the file}



if (plot_case == 1){
### diff SSPs
sub_case_names<-c("SSP126","SSP370","SSP585")


agb_file_SSP126_gfdl <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp126_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP370_gfdl <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp370_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP585_gfdl <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")


bgb_file_SSP126_gfdl <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp126_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP370_gfdl <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp370_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP585_gfdl <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")

agb_files<-c(agb_file_SSP126_gfdl,agb_file_SSP370_gfdl,agb_file_SSP585_gfdl)
bgb_files<-c(bgb_file_SSP126_gfdl,bgb_file_SSP370_gfdl,bgb_file_SSP585_gfdl)
##############################
} else if(plot_case==2){
### diff CC component
sub_case_names<-c("CO2","N deposition","precipi and temp")
  
agb_file_SSP585_default <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP585_2015co2 <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_2015co2_fullscalerc3c4_agb_v3.csv")
agb_file_SSP585_ndep <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_ssp585ndep_fullscalerc3c4_agb_v3.csv")


bgb_file_SSP585_default <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP585_2015co2 <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_2015co2_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP585_ndep <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_ssp585ndep_fullscalerc3c4_bgb_v3.csv")

agb_files<-c(agb_file_SSP585_default,agb_file_SSP585_2015co2,agb_file_SSP585_ndep)
bgb_files<-c(bgb_file_SSP585_default,bgb_file_SSP585_2015co2,bgb_file_SSP585_ndep)
}

```


```{r S5 read harmonized land type area in each subregion table }


in_forest_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_forest.csv"))%>%
  mutate(harm_type="Forest")
  
in_c3crop_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_c3crop.csv"))%>%
  mutate(harm_type="c3Crop")

in_c4crop_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_c4crop.csv"))%>%
  mutate(harm_type="c4Crop")

in_grass_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_grass.csv"))%>%
  mutate(harm_type="Grass")

in_Harmolandtype_area <-bind_rows(in_forest_area,in_c3crop_area,in_c4crop_area,in_grass_area)
  


```


```{r break label function}
generateQuantileLabels <- function(quantile_breaks) {
  sapply(1:(length(quantile_breaks) - 1), function(i) {
    paste(format(round(quantile_breaks[i], 3), nsmall = 3),
          "-",
          format(round(quantile_breaks[i + 1], 3), nsmall = 3),
          sep = "")
  })
}
## keep 2 decimal
generateQuantileLabels2 <- function(quantile_breaks) {
  sapply(1:(length(quantile_breaks) - 1), function(i) {
    paste(format(round(quantile_breaks[i], 2), nsmall = 2),
          "-",
          format(round(quantile_breaks[i + 1], 2), nsmall = 2),
          sep = "")
  })
}
## keep int
generateQuantileLabels_int <- function(quantile_breaks) {
  sapply(1:(length(quantile_breaks) - 1), function(i) {
    paste(format(round(quantile_breaks[i], 0)),
          "-",
          format(round(quantile_breaks[i + 1], 0)),
          sep = "")
  })
}

```

```{r S6 data_process_plot functions}
process_in_file <- function(data, harmolandtype_area) {
    # Read the CSV file
    # in_Sagb_co2->data
    # Process the data
    data %>%
      dplyr::select(-3) %>%
    filter(harm_type != "Other") %>%
    group_by(child.nodes) %>%
    pivot_wider(names_from = "year",values_from = "scalar")%>%
    ungroup()%>%
    dplyr::select(-2) %>%
    left_join(in_Harmolandtype_area, by = c("out_reg_code", "out_lu_code", "harm_type")) %>%
      dplyr::select(-7, -6) %>%
      group_by(region, harm_type) %>%
      mutate(region_pft_area = sum(pft_area_total, na.rm = TRUE)) %>%
      mutate(region_pft_area_weight = pft_area_total / region_pft_area) %>%
      summarize(across(
        .cols = 4:20,
        .fns = ~ weighted.mean(.x, w = region_pft_area_weight, na.rm = TRUE)
      )) %>%
      ungroup() %>%
      pivot_longer(cols = 3:ncol(.),
                   names_to = "year",
                   values_to = "scalar") %>%
      mutate(year = as.numeric(year)) %>%
      na.omit()%>%
    pivot_wider(names_from = harm_type, values_from = scalar) %>%
    ungroup() %>%
  # rename(
  #   SSP1 = GCAM_SSP1,
  #   SSP2 = GCAM_SSP2,
  #   SSP3 = GCAM_SSP3,
  #   SSP4 = GCAM_SSP4,
  #   SSP5 = GCAM_SSP5
  # ) %>%
  left_join(data_sf, by = c("region" = "reg_nm"))
}
###########################################
# Function to create individual plots
create_plot <- function(data,y_var, harm_type, x_label = "", y_label = "", title, ylim_range = c(-0.4, 0.8)) {
  ggplot(data %>% filter(harm_type == harm_type), aes(x = as.numeric(year), y = !!sym(y_var),group = region, color = region)) +
    geom_line() +
    labs(title = title,
         x = x_label,
         y = y_label,
         color = "Region") +
    theme_minimal() +
    theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
          legend.position = "none",
          plot.title = element_text(hjust = 0.5)) +
    ylim(ylim_range)
}
###############################################
# Function to save the regional combined plots for each CC component
# Define plot size

save_combined_plot <- function(plot, name_suffix,wid_size=17*0.7,hei_size=10*0.7) {
  file_base <- paste0(fig_save_path, "/",Fig_num_name, "_combined_", name_suffix, "_regions_v", version_num)
  
  ggsave(paste0(file_base, ".svg"), plot = plot, width = wid_size, height = hei_size, units = "in")
  ggsave(paste0(file_base, ".pdf"), plot = plot, width = wid_size, height = hei_size, units = "in")
  ggsave(paste0(file_base, ".png"), plot = plot, width = wid_size, height = hei_size, units = "in", dpi = 300)
  ggsave(filename = paste0(file_base, ".tif"), plot = plot, width = wid_size, height = hei_size, units = "in", device = "tiff", dpi = 300)
}

```

```{r S7 plot and save regional agb scaler group map}



##########################
# Initialize empty lists to store plots and processed data
pagb_list <- list()
check_belowCD_long_gmean_list <- list()

# For each dataset (this loop can be uncommented and used if needed)
# for (data_idx in c(1,2,3)) {
  y_titles <- c("Agb Carbon Scalars", "", "")
  

# Define file paths and process each agb file
in_Sagb_file_default <- agb_files[1]
in_Sagb_file_2015co2 <- agb_files[2]
in_Sagb_file_ndep <- agb_files[3]

in_Sagb_default1 <- read.csv(in_Sagb_file_default , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "default")
in_Sagb_2015co21 <- read.csv(in_Sagb_file_2015co2 , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "co22015")
in_Sagb_ndep1 <- read.csv(in_Sagb_file_ndep , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "ndep585")


in_Sagb_co2<-in_Sagb_default1%>%
  left_join(in_Sagb_2015co21, by=c("region","child.nodes","above.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = default-co22015)%>%
  select(-c("default","co22015"))

in_Sagb_N_dep<-in_Sagb_default1%>%
  left_join(in_Sagb_ndep1, by=c("region","child.nodes","above.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ndep585-default)%>%
  select(-c("default","ndep585"))

in_Sagb_tempperci<-in_Sagb_2015co21%>%
  mutate(scalar = co22015-1)%>%
  select(-c("co22015"))





##################


check_aboveCD_long_co2 <- process_in_file(in_Sagb_co2, in_Harmolandtype_area) 

check_aboveCD_long_N_dep <- process_in_file(in_Sagb_N_dep, in_Harmolandtype_area) 

check_aboveCD_long_tempperci <- process_in_file(in_Sagb_tempperci, in_Harmolandtype_area) 

########################

quantile_breaks_b <-
  quantile(
    c(check_aboveCD_long_co2$Forest, check_aboveCD_long_co2$Grass, check_aboveCD_long_co2$c3Crop, check_aboveCD_long_co2$c4Crop,
      check_aboveCD_long_N_dep$Forest, check_aboveCD_long_N_dep$Grass, check_aboveCD_long_N_dep$c3Crop, check_aboveCD_long_N_dep$c4Crop,
      check_aboveCD_long_tempperci$Forest, check_aboveCD_long_tempperci$Grass, check_aboveCD_long_tempperci$c3Crop, check_aboveCD_long_tempperci$c4Crop
      ),
    probs = seq(0, 1, by = 1 / 7),
    na.rm = TRUE
  )

quantile_breaks_b[1] <- -0.45
quantile_breaks_b[2] <- -0.342
quantile_breaks_b[3] <- -0.233
quantile_breaks_b[4] <- -0.125
quantile_breaks_b[5] <- -0.017
quantile_breaks_b[6] <- 0.092
quantile_breaks_b[7] <- 0.200

  
  quantile_labels_b <- generateQuantileLabels(quantile_breaks_b)
# quantile_labels_FP_re[1] <- "<0.2"
# 
# quantile_labels_FP_re[7] <- ">25"
color_values_FP_b <-
  c("#e5f5e0",
    "#c7e9c0",
    "#a1d99b",
    "#74c476",
    "#41ab5d",
    "#238b45",
    "#006d2c")
reversed_color_values_b <- rev(color_values_FP_b)

assign_colors <- function(x, breaks, colors) {
  cut(x,
      breaks = breaks,
      include.lowest = TRUE,
      labels = FALSE) %>%
    {
      colors[.]
    }
}


assign_quantile_categories <- function(x, breaks) {
  cut(x,
      breaks = breaks,
      include.lowest = TRUE,
      labels = FALSE) %>%
    factor(levels = 1:length(breaks))
}
#################################################################################
#################################################################################
#################################################################################
#################################################################################
check_aboveCD_long_co2$quantile_cat_1 <-
  assign_quantile_categories(check_aboveCD_long_co2$Forest, quantile_breaks_b)
check_aboveCD_long_co2$quantile_cat_2 <-
  assign_quantile_categories(check_aboveCD_long_co2$Grass, quantile_breaks_b)
check_aboveCD_long_co2$quantile_cat_3 <-
  assign_quantile_categories(check_aboveCD_long_co2$c3Crop, quantile_breaks_b)
check_aboveCD_long_co2$quantile_cat_4 <-
  assign_quantile_categories(check_aboveCD_long_co2$c4Crop, quantile_breaks_b)



check_aboveCD_long_N_dep$quantile_cat_1 <-
  assign_quantile_categories(check_aboveCD_long_N_dep$Forest, quantile_breaks_b)
check_aboveCD_long_N_dep$quantile_cat_2 <-
  assign_quantile_categories(check_aboveCD_long_N_dep$Grass, quantile_breaks_b)
check_aboveCD_long_N_dep$quantile_cat_3 <-
  assign_quantile_categories(check_aboveCD_long_N_dep$c3Crop, quantile_breaks_b)
check_aboveCD_long_N_dep$quantile_cat_4 <-
  assign_quantile_categories(check_aboveCD_long_N_dep$c4Crop, quantile_breaks_b)



check_aboveCD_long_tempperci$quantile_cat_1 <-
  assign_quantile_categories(check_aboveCD_long_tempperci$Forest, quantile_breaks_b)
check_aboveCD_long_tempperci$quantile_cat_2 <-
  assign_quantile_categories(check_aboveCD_long_tempperci$Grass, quantile_breaks_b)
check_aboveCD_long_tempperci$quantile_cat_3 <-
  assign_quantile_categories(check_aboveCD_long_tempperci$c3Crop, quantile_breaks_b)
check_aboveCD_long_tempperci$quantile_cat_4 <-
  assign_quantile_categories(check_aboveCD_long_tempperci$c4Crop, quantile_breaks_b)
#################################################################################
# First, find the max and min for each of the SSP columns
C_max_values_b1 <-
  sapply(check_aboveCD_long_co2[c("Forest", "Grass", "c3Crop", "c4Crop")], max, na.rm = TRUE)
C_min_values_b1 <-
  sapply(check_aboveCD_long_co2[c("Forest", "Grass", "c3Crop", "c4Crop")], min, na.rm = TRUE)

C_max_values_b2 <-
  sapply(check_aboveCD_long_N_dep[c("Forest", "Grass", "c3Crop", "c4Crop")], max, na.rm = TRUE)
C_min_values_b2 <-
  sapply(check_aboveCD_long_N_dep[c("Forest", "Grass", "c3Crop", "c4Crop")], min, na.rm = TRUE)

C_max_values_b3 <-
  sapply(check_aboveCD_long_tempperci[c("Forest", "Grass", "c3Crop", "c4Crop")], max, na.rm = TRUE)
C_min_values_b3 <-
  sapply(check_aboveCD_long_tempperci[c("Forest", "Grass", "c3Crop", "c4Crop")], min, na.rm = TRUE)

# Now find the overall max and min across all the SSP columns
C_overall_max_b <- max(C_max_values_b1,C_max_values_b2,C_max_values_b3)
C_overall_min_b <- min(C_min_values_b1,C_min_values_b2,C_min_values_b3)

# Print the max and min for each column
print(C_overall_max_b)
print(C_overall_min_b)

# Print the overall max and min
print(paste("Overall Max:", C_overall_max_b))
print(paste("Overall Min:", C_overall_min_b))





  
  plot_C_scalar <- function(data, fill_col, Title,num_label,h_value,show_legend = FALSE) {
    
    # data<-check_belowCD_long
    # fill_col<-"quantile_cat_1"
    # Title<-"Forest"
    # num_label<-"a"
    # h_value<-21
    # show_legend <- TRUE
    
    
  
  x_ticks <- seq(-180, 180, by = 90)  # Longitude range from -180 to 180 with 60-degree increments
  y_ticks <- seq(-60, 85, by = 45)    # Latitude range from -90 to 90 with 30-degree increments

  x_labels <- paste0(x_ticks, "°E")  # Append "°E" to each x tick label
  y_labels <- paste0(y_ticks, "°N")  # Append "°N" to each y tick label
  
  
 # p1<- 
   ggplot(data) +
    geom_sf(aes(geometry = geometry, fill = !!sym(fill_col)), color = "grey25") +
    scale_fill_manual(
      values = color_values_FP_b,
      name = expression("C scalar difference"),
      # new add
      limits = c("1","2","3","4","5","6","7"),# make sure every legend level will be shown
      labels = quantile_labels_b
    ) +
    theme_base() +
    labs(
      y = '',
      x = '',
      title = paste0(Title)
    ) +
     scale_x_continuous(breaks = x_ticks, labels = x_labels) +
    scale_y_continuous(breaks = y_ticks, labels = y_labels) +
    theme(
      panel.grid = element_blank(),
      panel.background = element_rect(fill = "white", colour = NA),
      plot.background = element_rect(fill = "white", colour = NA),
      plot.title = element_text(hjust = 0.5, size = 15),
      axis.title.x = element_text(size = 15),
      axis.title.y = element_text(size = 15),
      axis.text.x = element_text(size = 14.5),
      axis.text.y = element_text(size = 14.5),
      legend.text = element_text(size = 15),
      legend.title = element_text(size = 15),
      legend.position = ifelse(show_legend, "right", "none"),
      plot.margin = margin(t = 0, r = 0, b = 0, l = 0)
    ) +
    annotate(
      "text",
      x = Inf,
      y = Inf,
      label = paste0("(", num_label, ")"),
      hjust = h_value,
      vjust = 1.5,
      size = 4.5
    ) +
    guides(fill = guide_legend(keyheight = unit(1, "cm"), keywidth = unit(1, "cm")))
}

# plot_FP_scenario_re(FP_spatial_plot1_re, "quantile_cat_5", "5","e",0,show_legend = TRUE)
#plot_C_scalar <- function(data, fill_col, Title,num_label,h_value,show_legend = FALSE)
# Apply the function to your scenarios
p_C_Forest1 <- plot_C_scalar(check_aboveCD_long_co2,"quantile_cat_1", "Forest","a",18)
p_C_Grass1 <- plot_C_scalar(check_aboveCD_long_co2,"quantile_cat_2", "Grass","d",18)
p_C_c3crop1 <- plot_C_scalar(check_aboveCD_long_co2,"quantile_cat_3", "C3crop","g",18)
p_C_C4crop1 <- plot_C_scalar(check_aboveCD_long_co2,"quantile_cat_4", "C4crop","j",18)

p_C_Forest2 <- plot_C_scalar(check_aboveCD_long_N_dep,"quantile_cat_1", "Forest","b",18)
p_C_Grass2 <- plot_C_scalar(check_aboveCD_long_N_dep,"quantile_cat_2", "Grass","e",18)
p_C_c3crop2 <- plot_C_scalar(check_aboveCD_long_N_dep,"quantile_cat_3", "C3crop","h",18)
p_C_C4crop2 <- plot_C_scalar(check_aboveCD_long_N_dep,"quantile_cat_4", "C4crop","k",18)

p_C_Forest3 <- plot_C_scalar(check_aboveCD_long_tempperci,"quantile_cat_1", "Forest","c",18)
p_C_Grass3 <- plot_C_scalar(check_aboveCD_long_tempperci,"quantile_cat_2", "Grass","f",18)
p_C_c3crop3 <- plot_C_scalar(check_aboveCD_long_tempperci,"quantile_cat_3", "C3crop","i",18)
p_C_C4crop3 <- plot_C_scalar(check_aboveCD_long_tempperci,"quantile_cat_4", "C4crop","l",18)

P_C_legend <- plot_C_scalar(check_aboveCD_long_co2,"quantile_cat_4", "C4crop","d",21,show_legend = TRUE)
##############################################################################################################
##############################################################################################################  
##############################################################################################################
 

legend <- cowplot::get_legend(P_C_legend)

################################################################

combined_agb_plots <- wrap_plots(p_C_Forest1,p_C_Forest2,p_C_Forest3,
                                 p_C_Grass1,p_C_Grass2,p_C_Grass3,
                                 p_C_c3crop1,p_C_c3crop2,p_C_c3crop3,
                                 p_C_C4crop1, p_C_C4crop2, p_C_C4crop3, 
                                 nrow = 4)


combined_global_agb_plot <- plot_grid(
  combined_agb_plots,  # Vertical stack of AGB and BGB plots
  legend,                 # Legend
  ncol = 2,                      # Two columns: one for plots, one for the legend
  rel_widths = c(3, 0.2)         # Relative widths, giving most space to the plots and less to the legend
)
######################################################

# Save the combined plots
save_combined_plot(combined_agb_plots, "Sagb_CC_components")


 
```
#########################
I am right here
```{r S8 plot and save regional bgb scaler group map}



##########################
# Initialize empty lists to store plots and processed data
pbgb_list <- list()
check_belowCD_long_gmean_list <- list()

# For each dataset (this loop can be uncommented and used if needed)
# for (data_idx in c(1,2,3)) {
  
  
  # Define file paths and process each agb file
in_Sbgb_file_default <- bgb_files[1]
in_Sbgb_file_2015co2 <- bgb_files[2]
in_Sbgb_file_ndep <- bgb_files[3]

in_Sbgb_default1 <- read.csv(in_Sbgb_file_default , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "default")
in_Sbgb_2015co21 <- read.csv(in_Sbgb_file_2015co2 , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "co22015")
in_Sbgb_ndep1 <- read.csv(in_Sbgb_file_ndep , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "ndep585")


in_Sbgb_co2<-in_Sbgb_default1%>%
  left_join(in_Sbgb_2015co21, by=c("region","child.nodes","below.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = default-co22015)%>%
  select(-c("default","co22015"))

in_Sbgb_N_dep<-in_Sbgb_default1%>%
  left_join(in_Sbgb_ndep1, by=c("region","child.nodes","below.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ndep585-default)%>%
  select(-c("default","ndep585"))

in_Sbgb_tempperci<-in_Sbgb_2015co21%>%
  mutate(scalar = co22015-1)%>%
  select(-c("co22015"))





##################


check_belowCD_long_co2 <- process_in_file(in_Sbgb_co2, in_Harmolandtype_area) 

check_belowCD_long_N_dep <- process_in_file(in_Sbgb_N_dep, in_Harmolandtype_area) 

check_belowCD_long_tempperci <- process_in_file(in_Sbgb_tempperci, in_Harmolandtype_area) 

########################

quantile_breaks_b <-
  quantile(
    c(check_belowCD_long_co2$Forest, check_belowCD_long_co2$Grass, check_belowCD_long_co2$c3Crop, check_belowCD_long_co2$c4Crop,
      check_belowCD_long_N_dep$Forest, check_belowCD_long_N_dep$Grass, check_belowCD_long_N_dep$c3Crop, check_belowCD_long_N_dep$c4Crop,
      check_belowCD_long_tempperci$Forest, check_belowCD_long_tempperci$Grass, check_belowCD_long_tempperci$c3Crop, check_belowCD_long_tempperci$c4Crop
      ),
    probs = seq(0, 1, by = 1 / 7),
    na.rm = TRUE
  )

# quantile_breaks_b[1] <- -0.45
# quantile_breaks_b[2] <- -0.342
# quantile_breaks_b[3] <- -0.233
# quantile_breaks_b[4] <- -0.125
# quantile_breaks_b[5] <- -0.017
# quantile_breaks_b[6] <- 0.092
# quantile_breaks_b[7] <- 0.200

  
  quantile_labels_b <- generateQuantileLabels(quantile_breaks_b)
# quantile_labels_FP_re[1] <- "<0.2"
# 
# quantile_labels_FP_re[7] <- ">25"
color_values_FP_b <-
  c("#e5f5e0",
    "#c7e9c0",
    "#a1d99b",
    "#74c476",
    "#41ab5d",
    "#238b45",
    "#006d2c")
reversed_color_values_b <- rev(color_values_FP_b)

assign_colors <- function(x, breaks, colors) {
  cut(x,
      breaks = breaks,
      include.lowest = TRUE,
      labels = FALSE) %>%
    {
      colors[.]
    }
}


assign_quantile_categories <- function(x, breaks) {
  cut(x,
      breaks = breaks,
      include.lowest = TRUE,
      labels = FALSE) %>%
    factor(levels = 1:length(breaks))
}
#################################################################################
#################################################################################
#################################################################################
#################################################################################
check_belowCD_long_co2$quantile_cat_1 <-
  assign_quantile_categories(check_belowCD_long_co2$Forest, quantile_breaks_b)
check_belowCD_long_co2$quantile_cat_2 <-
  assign_quantile_categories(check_belowCD_long_co2$Grass, quantile_breaks_b)
check_belowCD_long_co2$quantile_cat_3 <-
  assign_quantile_categories(check_belowCD_long_co2$c3Crop, quantile_breaks_b)
check_belowCD_long_co2$quantile_cat_4 <-
  assign_quantile_categories(check_belowCD_long_co2$c4Crop, quantile_breaks_b)



check_belowCD_long_N_dep$quantile_cat_1 <-
  assign_quantile_categories(check_belowCD_long_N_dep$Forest, quantile_breaks_b)
check_belowCD_long_N_dep$quantile_cat_2 <-
  assign_quantile_categories(check_belowCD_long_N_dep$Grass, quantile_breaks_b)
check_belowCD_long_N_dep$quantile_cat_3 <-
  assign_quantile_categories(check_belowCD_long_N_dep$c3Crop, quantile_breaks_b)
check_belowCD_long_N_dep$quantile_cat_4 <-
  assign_quantile_categories(check_belowCD_long_N_dep$c4Crop, quantile_breaks_b)



check_belowCD_long_tempperci$quantile_cat_1 <-
  assign_quantile_categories(check_belowCD_long_tempperci$Forest, quantile_breaks_b)
check_belowCD_long_tempperci$quantile_cat_2 <-
  assign_quantile_categories(check_belowCD_long_tempperci$Grass, quantile_breaks_b)
check_belowCD_long_tempperci$quantile_cat_3 <-
  assign_quantile_categories(check_belowCD_long_tempperci$c3Crop, quantile_breaks_b)
check_belowCD_long_tempperci$quantile_cat_4 <-
  assign_quantile_categories(check_belowCD_long_tempperci$c4Crop, quantile_breaks_b)
#################################################################################
# First, find the max and min for each of the SSP columns
C_max_values_b1 <-
  sapply(check_belowCD_long_co2[c("Forest", "Grass", "c3Crop", "c4Crop")], max, na.rm = TRUE)
C_min_values_b1 <-
  sapply(check_belowCD_long_co2[c("Forest", "Grass", "c3Crop", "c4Crop")], min, na.rm = TRUE)

C_max_values_b2 <-
  sapply(check_belowCD_long_N_dep[c("Forest", "Grass", "c3Crop", "c4Crop")], max, na.rm = TRUE)
C_min_values_b2 <-
  sapply(check_belowCD_long_N_dep[c("Forest", "Grass", "c3Crop", "c4Crop")], min, na.rm = TRUE)

C_max_values_b3 <-
  sapply(check_belowCD_long_tempperci[c("Forest", "Grass", "c3Crop", "c4Crop")], max, na.rm = TRUE)
C_min_values_b3 <-
  sapply(check_belowCD_long_tempperci[c("Forest", "Grass", "c3Crop", "c4Crop")], min, na.rm = TRUE)

# Now find the overall max and min across all the SSP columns
C_overall_max_b <- max(C_max_values_b1,C_max_values_b2,C_max_values_b3)
C_overall_min_b <- min(C_min_values_b1,C_min_values_b2,C_min_values_b3)

# Print the max and min for each column
print(C_overall_max_b)
print(C_overall_min_b)

# Print the overall max and min
print(paste("Overall Max:", C_overall_max_b))
print(paste("Overall Min:", C_overall_min_b))





  
  plot_C_scalar <- function(data, fill_col, Title,num_label,h_value,show_legend = FALSE) {
    
    # data<-check_belowCD_long
    # fill_col<-"quantile_cat_1"
    # Title<-"Forest"
    # num_label<-"a"
    # h_value<-21
    # show_legend <- TRUE
    
    
  
  x_ticks <- seq(-180, 180, by = 90)  # Longitude range from -180 to 180 with 60-degree increments
  y_ticks <- seq(-60, 85, by = 45)    # Latitude range from -90 to 90 with 30-degree increments

  x_labels <- paste0(x_ticks, "°E")  # Append "°E" to each x tick label
  y_labels <- paste0(y_ticks, "°N")  # Append "°N" to each y tick label
  
  
 # p1<- 
   ggplot(data) +
    geom_sf(aes(geometry = geometry, fill = !!sym(fill_col)), color = "grey25") +
    scale_fill_manual(
      values = color_values_FP_b,
      name = expression("C scalar difference"),
      # new add
      limits = c("1","2","3","4","5","6","7"),# make sure every legend level will be shown
      labels = quantile_labels_b
    ) +
    theme_base() +
    labs(
      y = '',
      x = '',
      title = paste0(Title)
    ) +
     scale_x_continuous(breaks = x_ticks, labels = x_labels) +
    scale_y_continuous(breaks = y_ticks, labels = y_labels) +
    theme(
      panel.grid = element_blank(),
      panel.background = element_rect(fill = "white", colour = NA),
      plot.background = element_rect(fill = "white", colour = NA),
      plot.title = element_text(hjust = 0.5, size = 15),
      axis.title.x = element_text(size = 15),
      axis.title.y = element_text(size = 15),
      axis.text.x = element_text(size = 14.5),
      axis.text.y = element_text(size = 14.5),
      legend.text = element_text(size = 15),
      legend.title = element_text(size = 15),
      legend.position = ifelse(show_legend, "right", "none"),
      plot.margin = margin(t = 0, r = 0, b = 0, l = 0)
    ) +
    annotate(
      "text",
      x = Inf,
      y = Inf,
      label = paste0("(", num_label, ")"),
      hjust = h_value,
      vjust = 1.5,
      size = 4.5
    ) +
    guides(fill = guide_legend(keyheight = unit(1, "cm"), keywidth = unit(1, "cm")))
}

# plot_FP_scenario_re(FP_spatial_plot1_re, "quantile_cat_5", "5","e",0,show_legend = TRUE)
#plot_C_scalar <- function(data, fill_col, Title,num_label,h_value,show_legend = FALSE)
# Apply the function to your scenarios
p_C_Forest1 <- plot_C_scalar(check_belowCD_long_co2,"quantile_cat_1", "Forest","a",18)
p_C_Grass1 <- plot_C_scalar(check_belowCD_long_co2,"quantile_cat_2", "Grass","d",18)
p_C_c3crop1 <- plot_C_scalar(check_belowCD_long_co2,"quantile_cat_3", "C3crop","g",18)
p_C_C4crop1 <- plot_C_scalar(check_belowCD_long_co2,"quantile_cat_4", "C4crop","j",18)

p_C_Forest2 <- plot_C_scalar(check_belowCD_long_N_dep,"quantile_cat_1", "Forest","b",18)
p_C_Grass2 <- plot_C_scalar(check_belowCD_long_N_dep,"quantile_cat_2", "Grass","e",18)
p_C_c3crop2 <- plot_C_scalar(check_belowCD_long_N_dep,"quantile_cat_3", "C3crop","h",18)
p_C_C4crop2 <- plot_C_scalar(check_belowCD_long_N_dep,"quantile_cat_4", "C4crop","k",18)

p_C_Forest3 <- plot_C_scalar(check_belowCD_long_tempperci,"quantile_cat_1", "Forest","c",18)
p_C_Grass3 <- plot_C_scalar(check_belowCD_long_tempperci,"quantile_cat_2", "Grass","f",18)
p_C_c3crop3 <- plot_C_scalar(check_belowCD_long_tempperci,"quantile_cat_3", "C3crop","i",18)
p_C_C4crop3 <- plot_C_scalar(check_belowCD_long_tempperci,"quantile_cat_4", "C4crop","l",18)

P_C_legend <- plot_C_scalar(check_belowCD_long_co2,"quantile_cat_4", "C4crop","d",21,show_legend = TRUE)
##############################################################################################################
##############################################################################################################  
##############################################################################################################
 

legend <- cowplot::get_legend(P_C_legend)

################################################################

combined_bgb_plots <- wrap_plots(p_C_Forest1,p_C_Forest2,p_C_Forest3,
                                 p_C_Grass1,p_C_Grass2,p_C_Grass3,
                                 p_C_c3crop1,p_C_c3crop2,p_C_c3crop3,
                                 p_C_C4crop1, p_C_C4crop2, p_C_C4crop3, 
                                 nrow = 4)


combined_global_bgb_plot <- plot_grid(
  combined_bgb_plots,  # Vertical stack of bgb and BGB plots
  legend,                 # Legend
  ncol = 2,                      # Two columns: one for plots, one for the legend
  rel_widths = c(3, 0.2)         # Relative widths, giving most space to the plots and less to the legend
)
######################################################

# Save the combined plots
save_combined_plot(combined_bgb_plots, "Sbgb_CC_components")



```







