---
title: "GTM_4_dim_var_process"
author: "Meng Luo"
date: "2023-08-29"
output: html_document
    toc: true
    toc_float: true
---
# use the mature age's FP as the input for GCAM


#########################################################
## update of the this version
# add FULL_matrix_for_MFP_continue

# Content
## link to github
  S0 link to github
## Setting Up
  S1 needed R package and dir
 
  
  
  
  
# link to github
```{r S0 link to github , include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
```

# Setting Up
## Loading Needed R Packages and Setting Directory

```{r S1 needed R package and dir }

library(cowplot)
############
require(devtools)
#Please use this in console if needed: install_github('JGCRI/rgcam', build_vignettes=TRUE, force =TRUE)
library (rgcam)
library(tidyverse)
library(tidyr)

library(rlang)
library(dplyr)
# install.packages("patchwork")
library(patchwork)
# install.packages("sf")
library(sf)
# install.packages("svglite")
library(svglite)
library(cowplot)
library(gridExtra)
library(ggthemes)
library(stringr)
library(ggplot2)
library(RColorBrewer)



## run this in console devtools::load_all()

Fig_num_name<-"Fig24_C_scalar"
version_num <-"4"
case_name<-"_climate_productivityC"
#################################################################################################
## need to modify 
# plot_case<-1 # diff SSPs
plot_case<-1 # diff CC component
 
cases<-c("3SSPs")

case<-cases[plot_case]


## end of need to modify 
# read from hard disk ##############################################################
# # Chen lab desktop
# # root<-"O:/"
# 
# # 2023 laptop
# root<-"D:/"
# 
# 
# main_Sagb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_aboveCD/region_5ymean_alltypes_wrapper/")
# 
# 
# main_Sbgb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_belowCD/region_5ymean_alltypes_wrapper/")
# 
# 
# 
# XML_version <- paste0(version_num ,case_name,"_ssp",case) 

####

# main_GTM_mid_xml_path  <-"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/useful/"
# main_my_XML_path <- "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/new_XML/"
# # produce outputs in GCAM 7.0 release package 
# main_v7_XML_path <- "E/Docker_GCAM_v7_forest/gcam-master/input/gcamdata/xml/"
# 
# fig_save_path <- paste0(root,"E/new laptop2/PHD/my_2024_1_manuscript/Figure&table/figure/check_npp_rh_scaler_4in1_file/")

# Harmolandtype_area_main_path<-paste0(root,"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/")
# read from 2023 laptop  ##############################################################

# 2023 laptop
# root <- "C:/MengLuo/chapter 2_backup/"

# NAS
root <- "Z:/Meng/back_up_all/9_updates/"


main_Sagb_path <- paste0(root, "climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_aboveCD/region_5ymean_alltypes_wrapper/")


main_Sbgb_path <- paste0(root, "climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_belowCD/region_5ymean_alltypes_wrapper/")

XML_version <- paste0(version_num ,case_name,"_ssp",case) 


#####

main_GTM_mid_xml_path  <-"climate_FPC_GCAM/Data/GCAM data system_forestversion/useful/"
main_my_XML_path <- "climate_FPC_GCAM/Data/GCAM data system_forestversion/new_XML/"
# produce outputs in GCAM 7.0 release package 
main_v7_XML_path <- "XML_save/"

fig_save_path <- paste0(root,"my_2024_1_manuscript/Figure&table/figure/check_npp_rh_scaler_4in1_file/")

Harmolandtype_area_main_path<-paste0(root,"climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/")



shp_path <- paste0(root, "climate_FPC_GCAM/Code/boundary/gcam_boundaries_moirai_3p1_0p5arcmin_wgs84/gcam_boundaries_moirai_3p1_0p5arcmin_wgs84/main_outputs/region_boundaries_moirai_combined_3p1_0p5arcmin.shp")

data_sf <- st_read(shp_path)

```


## read GTM output txt file
separate each var and save in csv

# function section


```{r S2 function save_result }
save_csv_result <- function(result_DF, result_csv_name,row_names) {

full_save_path <- paste0(root,main_GTM_path, result_csv_name)
if (row_names == TRUE) {
write.csv(result_DF,full_save_path, row.names = TRUE)
} else {
write.csv(result_DF,full_save_path, row.names = FALSE)
}

}
```

# preprocessing for GCAM XML
## I am right here


```{r S2 automatically read the file}

# agb_files <- list.files(path = main_Sagb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)
# 
# 
# bgb_files <- list.files(path = main_Sbgb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)
# 
# print(agb_files)
# print(bgb_files)
```

```{r S3 read harmonized land type area in each subregion table }


in_forest_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_forest.csv"))%>%
  mutate(harm_type="Forest")
  
in_c3crop_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_c3crop.csv"))%>%
  mutate(harm_type="c3Crop")

in_c4crop_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_c4crop.csv"))%>%
  mutate(harm_type="c4Crop")

in_grass_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_grass.csv"))%>%
  mutate(harm_type="Grass")

in_Harmolandtype_area <-bind_rows(in_forest_area,in_c3crop_area,in_c4crop_area,in_grass_area)
  


```

```{r S4 read the file}

### diff SSPs
sub_case_names<-c("SSP126","SSP370","SSP585")


agb_file_SSP126_gfdl <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp126_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP370_gfdl <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp370_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP585_gfdl <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
## ukesm
agb_file_SSP126_ukesm <- paste0(main_Sagb_path, "classic_ukesm1-0-ll_w5e5_ssp126_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP370_ukesm <- paste0(main_Sagb_path, "classic_ukesm1-0-ll_w5e5_ssp370_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP585_ukesm <- paste0(main_Sagb_path, "classic_ukesm1-0-ll_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")


bgb_file_SSP126_gfdl <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp126_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP370_gfdl <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp370_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP585_gfdl <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
## ukesm
bgb_file_SSP126_ukesm <- paste0(main_Sbgb_path, "classic_ukesm1-0-ll_w5e5_ssp126_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP370_ukesm <- paste0(main_Sbgb_path, "classic_ukesm1-0-ll_w5e5_ssp370_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP585_ukesm <- paste0(main_Sbgb_path, "classic_ukesm1-0-ll_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")

agb_files_gfdl<-c(agb_file_SSP126_gfdl,agb_file_SSP370_gfdl,agb_file_SSP585_gfdl)
agb_files_ukesm<-c(agb_file_SSP126_ukesm,agb_file_SSP370_ukesm,agb_file_SSP585_ukesm)

bgb_files_gfdl<-c(bgb_file_SSP126_gfdl,bgb_file_SSP370_gfdl,bgb_file_SSP585_gfdl)
bgb_files_ukesm<-c(bgb_file_SSP126_ukesm,bgb_file_SSP370_ukesm,bgb_file_SSP585_ukesm)
##############################

```

```{r break label function}
generateQuantileLabels <- function(quantile_breaks) {
  sapply(1:(length(quantile_breaks) - 1), function(i) {
    paste(format(round(quantile_breaks[i], 3), nsmall = 3),
          "-",
          format(round(quantile_breaks[i + 1], 3), nsmall = 3),
          sep = "")
  })
}
## keep 2 decimal
generateQuantileLabels2 <- function(quantile_breaks) {
  sapply(1:(length(quantile_breaks) - 1), function(i) {
    paste(format(round(quantile_breaks[i], 2), nsmall = 2),
          "-",
          format(round(quantile_breaks[i + 1], 2), nsmall = 2),
          sep = "")
  })
}

## keep 1
generateQuantileLabels1 <- function(quantile_breaks) {
  sapply(1:(length(quantile_breaks) - 1), function(i) {
    paste(format(round(quantile_breaks[i], 1), nsmall = 1),
          "-",
          format(round(quantile_breaks[i + 1], 1), nsmall = 1),
          sep = "")
  })
}
## keep int
generateQuantileLabels_int <- function(quantile_breaks) {
  sapply(1:(length(quantile_breaks) - 1), function(i) {
    paste(format(round(quantile_breaks[i], 0)),
          "-",
          format(round(quantile_breaks[i + 1], 0)),
          sep = "")
  })
}

```

```{r S functions}

 
  
# Define a function to process the data
process_regional_data <- function(data, in_Harmolandtype_area) {
  
  # data <- aboveCD_foring_diff1
  
  data1<-  data %>%
      dplyr::select(-3) %>%
    filter(harm_type == "Forest") %>%
    group_by(child.nodes) %>%
    pivot_wider(names_from = "year",values_from = "scalar")%>%
    ungroup()%>%
    dplyr::select(-2) %>%
    left_join(in_Harmolandtype_area, by = c("out_reg_code", "out_lu_code", "harm_type")) %>%
      dplyr::select(-7, -6) %>%
      group_by(region, harm_type) %>%
      mutate(region_pft_area = sum(pft_area_total, na.rm = TRUE)) %>%
      mutate(region_pft_area_weight = pft_area_total / region_pft_area) %>%
      summarize(across(
        .cols = 4:20,
        .fns = ~ weighted.mean(.x, w = region_pft_area_weight, na.rm = TRUE)
      )) %>%
      ungroup() %>%
      pivot_longer(cols = 3:ncol(.),
                   names_to = "year",
                   values_to = "scalar") %>%
      mutate(year = as.numeric(year)) %>%
      na.omit()%>%
    pivot_wider(names_from = harm_type, values_from = scalar) %>%
    ungroup() %>%
  # rename(
  #   SSP1 = GCAM_SSP1,
  #   SSP2 = GCAM_SSP2,
  #   SSP3 = GCAM_SSP3,
  #   SSP4 = GCAM_SSP4,
  #   SSP5 = GCAM_SSP5
  # ) %>%
  left_join(data_sf, by = c("region" = "reg_nm"))
}

##########################

save_combined_plot <- function(plot, name_suffix,wid_size=17*0.7,hei_size=10*0.7) {
  file_base <- paste0(fig_save_path, "/",Fig_num_name, "_combined_", name_suffix, "_v", version_num)
  
  ggsave(paste0(file_base, ".svg"), plot = plot, width = wid_size, height = hei_size, units = "in")
  ggsave(paste0(file_base, ".pdf"), plot = plot, width = wid_size, height = hei_size, units = "in")
  ggsave(paste0(file_base, ".png"), plot = plot, width = wid_size, height = hei_size, units = "in", dpi = 300)
  ggsave(filename = paste0(file_base, ".tif"), plot = plot, width = wid_size, height = hei_size, units = "in", device = "tiff", dpi = 300)
}
#########################
# Function to create individual plots
create_regional_plot <- function(data, harm_type, x_label = "", y_label = "", title_suffix = "", ylim_range = c(-0.8, 0.6)) {
  ggplot(data %>% filter(harm_type == harm_type), aes(x = as.numeric(year), y = forcing_diff, group = region, color = region)) +
    geom_line() +
    labs(title = paste0(harm_type, title_suffix),
         x = x_label,
         y = y_label,
         color = "Region") +
    theme_minimal() +
    theme(
      panel.border = element_rect(color = "black", fill = NA, size = 1),
      legend.position = "none",
      plot.title = element_text(hjust = 0.5)
    ) +
    ylim(ylim_range)
}


```




```{r S5 plot and save agb scaler group map}

# 1: SSP126
# 2: SSP370
# 3: SSP585


##########################
# Initialize an empty list to store plots
pagb_list <- list()


  # data_idx<-1
  y_titles <- c("Agb carbon scalar difference", "", "")
  
  # Process the data for GFDL

  
  in_Sagb_file_gfdl1 <- agb_files_gfdl[1]
  in_Sagb_file_gfdl2 <- agb_files_gfdl[2]
  in_Sagb_file_gfdl3 <- agb_files_gfdl[3]
  
  in_Sagb_file_ukesm1 <- agb_files_ukesm[1]
  in_Sagb_file_ukesm2 <- agb_files_ukesm[2]
  in_Sagb_file_ukesm3 <- agb_files_ukesm[3]
  
    ###########################################
  
  
  # Process each dataset using the function
  
  in_Sagb_gfdl1<-read.csv(in_Sagb_file_gfdl1 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "gfdl")
  
  in_Sagb_gfdl2<-read.csv(in_Sagb_file_gfdl2 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "gfdl")
  
  in_Sagb_gfdl3<-read.csv(in_Sagb_file_gfdl3 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "gfdl")
  
  in_Sagb_ukesm3<-read.csv(in_Sagb_file_ukesm3 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "ukesm")
  
  in_Sagb_ukesm2<-read.csv(in_Sagb_file_ukesm2 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "ukesm")
  
  in_Sagb_ukesm1<-read.csv(in_Sagb_file_ukesm1 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "ukesm")
  
  aboveCD_foring_diff1<-in_Sagb_gfdl1%>%
  left_join(in_Sagb_ukesm1, by=c("region","child.nodes","above.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ukesm-gfdl)%>%
  select(-c("gfdl","ukesm"))
  
  aboveCD_foring_diff2<-in_Sagb_gfdl2%>%
  left_join(in_Sagb_ukesm2, by=c("region","child.nodes","above.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ukesm-gfdl)%>%
  select(-c("gfdl","ukesm"))
  
  aboveCD_foring_diff3<-in_Sagb_gfdl3%>%
  left_join(in_Sagb_ukesm3, by=c("region","child.nodes","above.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ukesm-gfdl)%>%
  select(-c("gfdl","ukesm"))
  
  
  
  
   check_aboveCD_foring_diff1 <-
    process_regional_data( aboveCD_foring_diff1, in_Harmolandtype_area)
   
   check_aboveCD_foring_diff2 <-
    process_regional_data( aboveCD_foring_diff2, in_Harmolandtype_area)
   
   check_aboveCD_foring_diff3 <-
    process_regional_data( aboveCD_foring_diff3, in_Harmolandtype_area)
   
   
   
   
   
   
   
   check_aboveCD_long_combine<-check_aboveCD_foring_diff1%>%
    rename(SSP126=Forest)%>%
    left_join(check_aboveCD_foring_diff2%>%
    rename(SSP370=Forest), by = c("region","year","key","reg_id","geometry"))%>%
    left_join(check_aboveCD_foring_diff3%>%
    rename(SSP585=Forest), by = c("region","year","key","reg_id","geometry"))
   
   
   
   
   
   
   
  
   
   
   
   
   
  ############################################################
   quantile_breaks_b <-
  quantile(
    c(check_aboveCD_long_combine$SSP126, check_aboveCD_long_combine$SSP370, check_aboveCD_long_combine$SSP585
      ),
    probs = seq(0, 1, by = 1 / 7),
    na.rm = TRUE
  )

# quantile_breaks_b[1] <- -0.50
quantile_breaks_b[2] <- -0.2
quantile_breaks_b[3] <- -0.1
quantile_breaks_b[4] <- 0
quantile_breaks_b[5] <- 0.10
quantile_breaks_b[6] <- 0.2
quantile_breaks_b[7] <- 0.3

  
  quantile_labels_b <- generateQuantileLabels1(quantile_breaks_b)
  
  
quantile_labels_b[1] <- "<-0.2"

quantile_labels_b[7] <- ">0.3"
color_values_FP_b <-
  c("#feb24c",
    "#fed976",
    "#ffffb2",
    "#d9ef8b",
    "#a6d96a",
    "#66bd63",
    "#1a9850")

assign_colors <- function(x, breaks, colors) {
  cut(x,
      breaks = breaks,
      include.lowest = TRUE,
      labels = FALSE) %>%
    {
      colors[.]
    }
}


assign_quantile_categories <- function(x, breaks) {
  cut(x,
      breaks = breaks,
      include.lowest = TRUE,
      labels = FALSE) %>%
    factor(levels = 1:length(breaks))
}
#################################################################################
#################################################################################
#################################################################################
#################################################################################
check_aboveCD_long_combine$quantile_cat_1 <-
  assign_quantile_categories(check_aboveCD_long_combine$SSP126, quantile_breaks_b)
check_aboveCD_long_combine$quantile_cat_2 <-
  assign_quantile_categories(check_aboveCD_long_combine$SSP370, quantile_breaks_b)
check_aboveCD_long_combine$quantile_cat_3 <-
  assign_quantile_categories(check_aboveCD_long_combine$SSP585, quantile_breaks_b)



#################################################################################
# First, find the max and min for each of the SSP columns
C_max_values_b1 <-
  sapply(check_aboveCD_long_combine[c("SSP126", "SSP370", "SSP585")], max, na.rm = TRUE)
C_min_values_b1 <-
  sapply(check_aboveCD_long_combine[c("SSP126", "SSP370", "SSP585")], min, na.rm = TRUE)



# Now find the overall max and min across all the SSP columns
C_overall_max_b <- max(C_max_values_b1)
C_overall_min_b <- min(C_min_values_b1)

# Print the max and min for each column
print(C_overall_max_b)
print(C_overall_min_b)

# Print the overall max and min
print(paste("Overall Max:", C_overall_max_b))
print(paste("Overall Min:", C_overall_min_b))





  
  plot_C_scalar <- function(data, fill_col, Title,num_label,h_value,show_legend = FALSE,y_title = "",if_ytitle=FALSE,ifxlabel=FALSE) {
    
    # data<-check_belowCD_long
    # fill_col<-"quantile_cat_1"
    # Title<-"Forest"
    # num_label<-"a"
    # h_value<-21
    # show_legend <- TRUE
    
    
  
  x_ticks <- seq(-180, 180, by = 90)  # Longitude range from -180 to 180 with 60-degree increments
  y_ticks <- seq(-60, 85, by = 45)    # Latitude range from -90 to 90 with 30-degree increments

  x_labels <- paste0(x_ticks, "째E")  # Append "째E" to each x tick label
  y_labels <- paste0(y_ticks, "째N")  # Append "째N" to each y tick label
  
  
 # p1<- 
   p<-ggplot(data) +
    geom_sf(aes(geometry = geometry, fill = !!sym(fill_col)), color = "grey25") +
    scale_fill_manual(
      values = color_values_FP_b,
      name = expression(""),
      # new add
      limits = c("1","2","3","4","5","6","7"),# make sure every legend level will be shown
      labels = quantile_labels_b
    ) +
    theme_base() +
    labs(
      y = y_title,
      x = '',
      title = paste0(Title)
    ) +
     scale_x_continuous(breaks = x_ticks, labels = x_labels) +
    scale_y_continuous(breaks = y_ticks, labels = y_labels) +
    theme(
      panel.grid = element_blank(),
      panel.background = element_rect(fill = "white", colour = NA),
      plot.background = element_rect(fill = "white", colour = NA),
      plot.title = element_text(hjust = 0.5, size = 15),
      axis.title.x = element_text(size = 15),
      axis.title.y = element_text(size = 15, face = "bold"),
      axis.text.x = element_text(size = 14.5),
      axis.text.y = element_text(size = 14.5),
      legend.text = element_text(size = 15),
      legend.title = element_text(size = 15),
      legend.position = ifelse(show_legend, "right", "none"),
      plot.margin = margin(t = 0, r = 0, b = 0, l = 0)
    ) +
    annotate(
      "text",
      x = Inf,
      y = Inf,
      label = paste0("(", num_label, ")"),
      hjust = h_value,
      vjust = 1.5,
      size = 4.5
    ) +
    guides(fill = guide_legend(keyheight = unit(1, "cm"), keywidth = unit(1, "cm"),
        reverse = TRUE  # Reverse the legend order
        ))
   
   
   if (!if_ytitle) {
    p <- p +
      theme(axis.text.y = element_blank(),
            axis.ticks.y = element_blank())
  }

  if (ifxlabel) {p<-p
    
  }else if (ifxlabel == FALSE) {
  p <- p +
      theme(axis.text.x = element_blank(),
            axis.ticks.x = element_blank())}
   return(p)
  }
  
  
   check_aboveCD_long_combine_2100<-check_aboveCD_long_combine%>%
    filter(year==2100)
write.csv( check_aboveCD_long_combine_2100,paste0(fig_save_path,"Fig24_check_aboveCD_long_combine_2100.csv"))



  
  p_C_126 <- plot_C_scalar(check_aboveCD_long_combine%>%
    filter(year==2100),"quantile_cat_1", "AGB carbon scalar difference","a",19.9*0.88,y_title= "SSP126",if_ytitle=TRUE,ifxlabel=FALSE)+
  theme(
    legend.margin = margin(t = 0, r = 15, b = 0, l = 0)  # Adjust the values to increase/decrease margin
  )
p_C_370 <- plot_C_scalar(check_aboveCD_long_combine%>%
    filter(year==2100),"quantile_cat_2", "","c",20.9*0.88,y_title= "SSP370",,if_ytitle=TRUE,ifxlabel=FALSE)+
  theme(
    legend.margin = margin(t = 0, r = 15, b = 0, l = 0)   # Adjust the values to increase/decrease margin
  )
p_C_585 <- plot_C_scalar(check_aboveCD_long_combine%>%
    filter(year==2100),"quantile_cat_3", "","e",19.9*0.88,y_title= "SSP585",if_ytitle=TRUE,ifxlabel=TRUE)+
  theme(
     legend.margin = margin(t = 0, r = 15, b = 0, l = 0)   # Adjust the values to increase/decrease margin
  )


P_C_legend <- plot_C_scalar(check_aboveCD_long_combine,"quantile_cat_3", "","d",21,show_legend = TRUE)+
  theme(
    legend.margin = margin(10, 10, 10, 10)#,  # Adjust the values to increase/decrease margin
  # Adjust margin
    # legend.text = element_text(size = 6),  # Adjust legend text size
    # legend.title = element_text(size = 6),  # Adjust legend title size
    # legend.key.size = unit(0.1, "lines")  # Adjust legend key size
  )

##############################################################################################################
##############################################################################################################  
##############################################################################################################
 

legend <- cowplot::get_legend(P_C_legend)

   
   



```



```{r S6 plot and save bgb scaler group map}



##########################
# Initialize an empty list to store plots
  pbgb_list <- list()


  # data_idx<-1
  y_titles <- c("BGB carbon scalar difference", "", "")
  
  in_Sbgb_file_gfdl1 <- bgb_files_gfdl[1]
  in_Sbgb_file_gfdl2 <- bgb_files_gfdl[2]
  in_Sbgb_file_gfdl3 <- bgb_files_gfdl[3]
  
  in_Sbgb_file_ukesm1 <- bgb_files_ukesm[1]
  in_Sbgb_file_ukesm2 <- bgb_files_ukesm[2]
  in_Sbgb_file_ukesm3 <- bgb_files_ukesm[3]
  
    ###########################################
  
  
  # Process each dataset using the function
  
  in_Sbgb_gfdl1<-read.csv(in_Sbgb_file_gfdl1 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "gfdl")
  
  in_Sbgb_gfdl2<-read.csv(in_Sbgb_file_gfdl2 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "gfdl")
  
  in_Sbgb_gfdl3<-read.csv(in_Sbgb_file_gfdl3 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "gfdl")
  
  in_Sbgb_ukesm3<-read.csv(in_Sbgb_file_ukesm3 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "ukesm")
  
  in_Sbgb_ukesm2<-read.csv(in_Sbgb_file_ukesm2 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "ukesm")
  
  in_Sbgb_ukesm1<-read.csv(in_Sbgb_file_ukesm1 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "ukesm")
  
  belowCD_foring_diff1<-in_Sbgb_gfdl1%>%
  left_join(in_Sbgb_ukesm1, by=c("region","child.nodes","below.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ukesm-gfdl)%>%
  select(-c("gfdl","ukesm"))
  
  belowCD_foring_diff2<-in_Sbgb_gfdl2%>%
  left_join(in_Sbgb_ukesm2, by=c("region","child.nodes","below.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ukesm-gfdl)%>%
  select(-c("gfdl","ukesm"))
  
  belowCD_foring_diff3<-in_Sbgb_gfdl3%>%
  left_join(in_Sbgb_ukesm3, by=c("region","child.nodes","below.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ukesm-gfdl)%>%
  select(-c("gfdl","ukesm"))
  
  
  
  
   check_belowCD_foring_diff1 <-
    process_regional_data( belowCD_foring_diff1, in_Harmolandtype_area)
   
   check_belowCD_foring_diff2 <-
    process_regional_data( belowCD_foring_diff2, in_Harmolandtype_area)
   
   check_belowCD_foring_diff3 <-
    process_regional_data( belowCD_foring_diff3, in_Harmolandtype_area)
   
   
   
   
    
   
   check_belowCD_long_combine<-check_belowCD_foring_diff1%>%
    rename(SSP126=Forest)%>%
    left_join(check_belowCD_foring_diff2%>%
    rename(SSP370=Forest), by = c("region","year","key","reg_id","geometry"))%>%
    left_join(check_belowCD_foring_diff3%>%
    rename(SSP585=Forest), by = c("region","year","key","reg_id","geometry"))
   
   
   
   
   
   check_belowCD_long_combine$quantile_cat_1 <-
  assign_quantile_categories(check_belowCD_long_combine$SSP126, quantile_breaks_b)
check_belowCD_long_combine$quantile_cat_2 <-
  assign_quantile_categories(check_belowCD_long_combine$SSP370, quantile_breaks_b)
check_belowCD_long_combine$quantile_cat_3 <-
  assign_quantile_categories(check_belowCD_long_combine$SSP585, quantile_breaks_b)
   
   
    check_belowCD_long_combine_2100<-check_belowCD_long_combine%>%
    filter(year==2100)
write.csv( check_belowCD_long_combine_2100,paste0(fig_save_path,"Fig24_check_belowCD_long_combine_2100.csv"))
   
   p_bC_126 <- plot_C_scalar(check_belowCD_long_combine%>%
    filter(year==2100),"quantile_cat_1", "BGB carbon scalar difference","b",19.9*0.88,if_ytitle=FALSE,ifxlabel=FALSE)#+
  # theme(
  #   legend.margin = margin(0, 15, 0, 0)  # Adjust the values to increase/decrease margin
  # )
p_bC_370 <- plot_C_scalar(check_belowCD_long_combine%>%
    filter(year==2100),"quantile_cat_2", "","d",19.9*0.88,if_ytitle=FALSE,ifxlabel=FALSE)#+
  # theme(
  #   legend.margin = margin(0, 15, 0, 0)  # Adjust the values to increase/decrease margin
  # )
p_bC_585 <- plot_C_scalar(check_belowCD_long_combine%>%
    filter(year==2100),"quantile_cat_3", "","f",25.8*0.88,if_ytitle=FALSE,ifxlabel=TRUE)#+
  # theme(
  #   legend.margin = margin(0, 15, 0, 0)  # Adjust the values to increase/decrease margin
  # )
   
   
  ############################################################
  #  quantile_breaks_b2 <-
  # quantile(
  #   c(check_belowCD_long_combine$SSP126, check_belowCD_long_combine$SSP370, check_belowCD_long_combine$SSP585
  #     ),
  #   probs = seq(0, 1, by = 1 / 7),
  #   na.rm = TRUE
  # )

   
   
  ############################################################
  
```

```{r save}


  combined_agb_plots <- wrap_plots(p_C_126,p_C_370,p_C_585, nrow = 3)
combined_bgb_plots <- wrap_plots(p_bC_126,p_bC_370,p_bC_585, nrow = 3)
# combined_agbbgb_plots <- wrap_plots(p_C_126,p_bC_126,p_C_370,p_bC_370,p_C_585,p_bC_585, nrow = 3)
##############################################
combined_global_bgb_plot <- plot_grid(
  combined_agb_plots, 
  combined_bgb_plots,
  legend,                 # Legend
  ncol = 3,                      # Two columns: one for plots, one for the legend
  rel_widths = c(0.7,0.61, 0.4)         # Relative widths, giving most space to the plots and less to the legend
)


 ggsave(paste0(fig_save_path, "/Fig24_forcings_diff_combined_Sagb_bgb_spatial_v",version_num,".svg"), plot = combined_global_bgb_plot , width = 15*0.81, height = 9*0.81, units = "in")


ggsave(paste0(fig_save_path, "/Fig24_forcings_diff_combined_Sagb_bgb_spatial_v",version_num,".pdf"), plot = combined_global_bgb_plot, width = 15*0.81, height = 9*0.81, units = "in")
ggsave(paste0(fig_save_path, "/Fig24_forcings_diff_combined_Sagb_bgb_spatial_v",version_num,".png"), plot = combined_global_bgb_plot, width = 15*0.81, height = 9*0.81, units = "in", dpi = 300)
ggsave(filename = paste0(fig_save_path,"/Fig24_forcings_diff_combined_Sagb_bgb_spatial_v", version_num, ".tif"),
     plot = combined_global_bgb_plot,
     width = 15*0.81,
     height = 9*0.81,
     units = "in",
     device = "tiff",
     dpi = 300)
  
  



  
  
```

