---
title: "GTM_4_dim_var_process"
author: "Meng Luo"
date: "2023-08-29"
output: html_document
    toc: true
    toc_float: true
---
# use the mature age's FP as the input for GCAM


#########################################################
## update of the this version
# add FULL_matrix_for_MFP_continue

# Content
## link to github
  S0 link to github
## Setting Up
  S1 needed R package and dir
 
  
  
  
  
# link to github
```{r S0 link to github , include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
```

# Setting Up
## Loading Needed R Packages and Setting Directory

```{r S1 needed R package and dir }
library(tidyverse)
library(tidyr)
#install.packages("rlang")
library(rlang)
library(dplyr)
library(gcamdata)
library('drake')
library(patchwork)
library(ggplot2)
library(cowplot)


## run this in console devtools::load_all()

Fig_num_name<-"Fig20_C_scalar"
version_num <-"5"
case_name<-"_climate_productivityC"
###############################################################################################
 
case<-"CC_components"




## end of need to modify 
# read from hard disk ##############################################################
# # Chen lab desktop
# # root<-"O:/"
# 
# # 2023 laptop
# root<-"D:/"
# 
# 
# main_Sagb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_aboveCD/region_5ymean_alltypes_wrapper/")
# 
# 
# main_Sbgb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_belowCD/region_5ymean_alltypes_wrapper/")
# 
# 
# 
# XML_version <- paste0(version_num ,case_name,"_ssp",case) 

####

# main_GTM_mid_xml_path  <-"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/useful/"
# main_my_XML_path <- "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/new_XML/"
# # produce outputs in GCAM 7.0 release package 
# main_v7_XML_path <- "E/Docker_GCAM_v7_forest/gcam-master/input/gcamdata/xml/"
# 
# fig_save_path <- paste0(root,"E/new laptop2/PHD/my_2024_1_manuscript/Figure&table/figure/check_npp_rh_scaler_4in1_file/")

# Harmolandtype_area_main_path<-paste0(root,"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/")
# read from 2023 laptop  ##############################################################

# 2023 laptop
# root <- "C:/MengLuo/chapter 2_backup/"

# NAS
root <- "Z:/Meng/back_up_all/9_updates/"


main_Sagb_path <- paste0(root, "climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_aboveCD/region_5ymean_alltypes_wrapper/")


main_Sbgb_path <- paste0(root, "climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_belowCD/region_5ymean_alltypes_wrapper/")

XML_version <- paste0(version_num ,case_name,"_ssp",case) 


#####

main_GTM_mid_xml_path  <-"climate_FPC_GCAM/Data/GCAM data system_forestversion/useful/"
main_my_XML_path <- "climate_FPC_GCAM/Data/GCAM data system_forestversion/new_XML/"
# produce outputs in GCAM 7.0 release package 
main_v7_XML_path <- "XML_save/"

fig_save_path <- paste0(root,"my_2024_1_manuscript/Figure&table/figure/check_npp_rh_scaler_4in1_file/")

Harmolandtype_area_main_path<-paste0(root,"climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/")

```


## read GTM output txt file
separate each var and save in csv

# function section


```{r S2 function save_result }
save_csv_result <- function(result_DF, result_csv_name,row_names) {

full_save_path <- paste0(root,main_GTM_path, result_csv_name)
if (row_names == TRUE) {
write.csv(result_DF,full_save_path, row.names = TRUE)
} else {
write.csv(result_DF,full_save_path, row.names = FALSE)
}

}
```

# preprocessing for GCAM XML
## I am right here


```{r S3 automatically read the file}

# agb_files <- list.files(path = main_Sagb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)
# 
# 
# bgb_files <- list.files(path = main_Sbgb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)
# 
# print(agb_files)
# print(bgb_files)
```

```{r S4 read the file}

forcing_choice<-1

if (forcing_choice==1){
forcing<-"gfdl-esm4"
forcing_short<-"gfdl"
}else{

forcing<-"ukesm1-0-ll"
forcing_short<-"ukesm"
}

### diff CC component
sub_case_names<-c("CO2","N deposition","precipi and temp")
  
agb_file_SSP585_default <- paste0(main_Sagb_path, "classic_",forcing,"_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP585_2015co2 <- paste0(main_Sagb_path, "classic_",forcing,"_w5e5_ssp585_2015soc-from-histsoc_2015co2_fullscalerc3c4_agb_v3.csv")
agb_file_SSP585_ndep <- paste0(main_Sagb_path, "classic_",forcing,"_w5e5_ssp585_2015soc-from-histsoc_ssp585ndep_fullscalerc3c4_agb_v3.csv")


bgb_file_SSP585_default <- paste0(main_Sbgb_path, "classic_",forcing,"_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP585_2015co2 <- paste0(main_Sbgb_path, "classic_",forcing,"_w5e5_ssp585_2015soc-from-histsoc_2015co2_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP585_ndep <- paste0(main_Sbgb_path, "classic_",forcing,"_w5e5_ssp585_2015soc-from-histsoc_ssp585ndep_fullscalerc3c4_bgb_v3.csv")

agb_files<-c(agb_file_SSP585_default,agb_file_SSP585_2015co2,agb_file_SSP585_ndep)
bgb_files<-c(bgb_file_SSP585_default,bgb_file_SSP585_2015co2,bgb_file_SSP585_ndep)

```


```{r S5 read harmonized land type area in each subregion table }


in_forest_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_forest.csv"))%>%
  mutate(harm_type="Forest")
  
in_c3crop_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_c3crop.csv"))%>%
  mutate(harm_type="c3Crop")

in_c4crop_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_c4crop.csv"))%>%
  mutate(harm_type="c4Crop")

in_grass_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_grass.csv"))%>%
  mutate(harm_type="Grass")

in_Harmolandtype_area <-bind_rows(in_forest_area,in_c3crop_area,in_c4crop_area,in_grass_area)
  


```

```{r S6 data_process_plot functions}
process_in_file <- function(file, harmolandtype_area) {
    # Read the CSV file
    in_Sagb <- read.csv(file, check.names = FALSE)
  
    # Process the data
    in_Sagb %>%
      dplyr::select(-3, -2) %>%
      filter(harm_type != "Other") %>%
      left_join(harmolandtype_area, by = c("out_reg_code", "out_lu_code", "harm_type")) %>%
      dplyr::select(-7, -6) %>%
      group_by(region, harm_type) %>%
      mutate(region_pft_area = sum(pft_area_total, na.rm = TRUE)) %>%
      mutate(region_pft_area_weight = pft_area_total / region_pft_area) %>%
      summarize(across(
        .cols = 4:22,
        .fns = ~ weighted.mean(.x, w = region_pft_area_weight, na.rm = TRUE)
      )) %>%
      ungroup() %>%
      pivot_longer(cols = 3:ncol(.),
                   names_to = "year",
                   values_to = "scalar") %>%
      mutate(year = as.numeric(year)) %>%
      na.omit()
}

process_global_data <- function(data) {
     # data<-in_Sagb_co2
  # write.csv(data,"data.csv")
   
  data %>%
    dplyr::select(-3) %>%
    filter(harm_type == "Forest") %>%
    group_by(child.nodes) %>%
    pivot_wider(names_from = "year",values_from = "scalar")%>%
    ungroup()%>%
    dplyr::select(-2) %>%
    left_join(in_Harmolandtype_area, by = c("out_reg_code", "out_lu_code", "harm_type")) %>%
    group_by(harm_type) %>%
    mutate(global_pft_area = sum(pft_area_total, na.rm = TRUE)) %>%
    mutate(global_pft_area_weight = pft_area_total / global_pft_area) %>%
    summarize(across(
    .cols = 7:23,
    .fns = list(
      mean = ~ weighted.mean(.x, w = global_pft_area_weight, na.rm = TRUE),
      sd = ~ sqrt(weighted.mean((.x - weighted.mean(.x, w = global_pft_area_weight, na.rm = TRUE))^2, w = global_pft_area_weight, na.rm = TRUE))
    )
  )) %>%
  ungroup() %>%
  pivot_longer(cols = ends_with("_mean") | ends_with("_sd"),
               names_to = "year_stat",
               values_to = "value") %>%
  separate(year_stat, into = c("year", "stat"), sep = "_", convert = TRUE) %>%
  pivot_wider(names_from = stat, values_from = value) %>%
  mutate(year = as.numeric(year)) %>%
  dplyr::select(harm_type, year, mean, sd) %>%
    na.omit()
}


    scenario_colors <- c("CO2" = "#B85800", "N_dep" = "#008C2F", "tempperci" = "#1B51F2")
#############################
 create_global_plot <- function(data,
                               y_var_m,
                               y_var_sd,
                               ylimits = c(0.82, 1.75),
                               if_title,
                               t_title,
                               if_xtitle = FALSE,
                               x_title,
                               if_ytitle = FALSE,
                               y_title,
                               ifxlabel = TRUE,
                               lab,
                               hj = 10,
                               scenario_colors = NULL) {
  
  
  


  # data <- check_aboveCD_long_gmean_combined
  # y_var_m <- "mean"
  # y_var_sd <- "sd"
  # ylimits <- c(0.82, 1.75)
  # if_title <- FALSE
  # t_title <- "AGB Carbon scalar"
  # if_xtitle <- TRUE
  # x_title <- "Year"
  # if_ytitle <- TRUE
  # y_title <- "Agb Carbon scalar"
  # ifxlabel <- FALSE
  # lab <- "(a)"
  # hj <- 10
  # scenario_colors <- NULL
  
  
  
  # Default color palette if none provided
  if (is.null(scenario_colors)) {
    
     # scenario_colors <- c("CO2" = "#65C927", "N_dep" = "#C76811", "tempperci" = "#2890E6")
     
    scenario_colors <- c("CO2" = "#B85800", "N_dep" = "#008C2F", "tempperci" = "#1B51F2")
     
     
  }
  
  p <- ggplot(data, aes(x = as.numeric(year), y = !!sym(y_var_m), group = scenario)) +
    geom_ribbon(aes(ymin = !!sym(y_var_m) - !!sym(y_var_sd) / 2, 
                    ymax = !!sym(y_var_m) + !!sym(y_var_sd) / 2, 
                    fill = scenario), color = NA, alpha = 0.2, show.legend = FALSE) +
    geom_line(aes(color = scenario), size = 1, show.legend = FALSE) +
    scale_color_manual(values = scenario_colors) +
    scale_fill_manual(values = scenario_colors) +
    labs(title = if (if_title) t_title else NULL,
         x = if (if_xtitle) x_title else NULL,
         y = if (if_ytitle) y_title else NULL,
         color = "Scenarios") +
    theme_minimal() +
    theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
          legend.position = "none",
          plot.title = element_text(hjust = 0.5, face = "bold")) +
    ylim(ylimits) +
    annotate("text",
             x = Inf,
             y = Inf,
             label = lab,
             hjust = hj,
             vjust = 1.5,
             size = 4)

  if (!if_ytitle) {
    p <- p +
      theme(axis.text.y = element_blank(),
            axis.ticks.y = element_blank())
  }

  if (ifxlabel) {p<-p
    
  }else if (ifxlabel == FALSE) {
  p <- p +
      theme(axis.text.x = element_blank(),
            axis.ticks.x = element_blank())}
  
  return(p)
}


##############################
# Function to save the regional combined plots for each CC component
# Define plot size

save_combined_plot <- function(plot, name_suffix,wid_size=15,hei_size=10) {
  file_base <- paste0(fig_save_path, "/",Fig_num_name, "_combined_", name_suffix, "_regions_v", version_num)
  
  ggsave(paste0(file_base, ".svg"), plot = plot, width = wid_size, height = hei_size, units = "in")
  ggsave(paste0(file_base, ".pdf"), plot = plot, width = wid_size, height = hei_size, units = "in")
  ggsave(paste0(file_base, ".png"), plot = plot, width = wid_size, height = hei_size, units = "in", dpi = 300)
  ggsave(filename = paste0(file_base, ".tif"), plot = plot, width = wid_size, height = hei_size, units = "in", device = "tiff", dpi = 300)
}
```




```{r S9 global plot & save}
pagb_list<- list()
pbgb_list<- list()
## AGB  ###################################################################################

in_Sagb_file_default <- agb_files[1]
in_Sagb_file_2015co2 <- agb_files[2]
in_Sagb_file_ndep <- agb_files[3]

in_Sagb_default1 <- read.csv(in_Sagb_file_default , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "default")
in_Sagb_2015co21 <- read.csv(in_Sagb_file_2015co2 , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "co22015")
in_Sagb_ndep1 <- read.csv(in_Sagb_file_ndep , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "ndep585")


in_Sagb_co2<-in_Sagb_default1%>%
  left_join(in_Sagb_2015co21, by=c("region","child.nodes","above.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = default-co22015)%>%
  dplyr::select(-c("default","co22015"))

in_Sagb_N_dep<-in_Sagb_default1%>%
  left_join(in_Sagb_ndep1, by=c("region","child.nodes","above.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ndep585-default)%>%
  dplyr::select(-c("default","ndep585"))

in_Sagb_tempperci<-in_Sagb_2015co21%>%
  mutate(scalar = co22015-1)%>%
  dplyr::select(-c("co22015"))




check_aboveCD_long_gmean_co2 <- process_global_data(in_Sagb_co2)
check_aboveCD_long_gmean_N_dep <- process_global_data(in_Sagb_N_dep)
check_aboveCD_long_gmean_tempperci <- process_global_data(in_Sagb_tempperci)

check_aboveCD_long_gmean_co2 <- rbind(check_aboveCD_long_gmean_co2, data.frame(harm_type = "Forest", year = 2015, mean = 0, sd = 0))
check_aboveCD_long_gmean_N_dep <- rbind(check_aboveCD_long_gmean_N_dep, data.frame(harm_type = "Forest", year = 2015, mean = 0, sd = 0))
check_aboveCD_long_gmean_tempperci <- rbind(check_aboveCD_long_gmean_tempperci, data.frame(harm_type = "Forest", year = 2015, mean = 0, sd = 0))

  
check_aboveCD_long_gmean_combined <- check_aboveCD_long_gmean_co2 %>%
  mutate(scenario = "CO2") %>%
  rbind(check_aboveCD_long_gmean_tempperci %>%
          mutate(scenario = "tempperci"))%>%
  rbind(check_aboveCD_long_gmean_N_dep %>%
          mutate(scenario = "N_dep"))



check_aboveCD_long_gmean_combined_2100<-check_aboveCD_long_gmean_combined%>%
    filter(year==2100)
  
  
  write.csv( check_aboveCD_long_gmean_combined_2100,paste0(fig_save_path,"Fig20_check_aboveCD_long_gmean_combined_2100",forcing_short,".csv"))

  
  write.csv( check_aboveCD_long_gmean_combined,paste0(fig_save_path,"Fig20_check_aboveCD_long_gmean_combined",forcing_short,".csv"))



  
pagb <- create_global_plot(
  check_aboveCD_long_gmean_combined,
  y_var_m = "mean",
  y_var_sd = "sd",
  ylimits = c(-0.285, 0.535),
  if_title = FALSE,
  t_title = "AGB carbon scalar difference",
  if_xtitle = TRUE,
  x_title = "Year",
  if_ytitle = TRUE,
  y_title = "AGB carbon scalar difference",
  ifxlabel = TRUE,
  lab = "(a)",
  hj = 16.6)


check_aboveCD_long_gmean_combined$scenario <- factor(
  check_aboveCD_long_gmean_combined$scenario,
  levels = c("CO2", "tempperci", "N_dep")  # Reorder as desired
)


p_global_legend <- ggplot(
  check_aboveCD_long_gmean_combined,
  aes(
    x = as.numeric(year),
    y = mean,
    group = scenario,
    color = scenario
  )
) +
  geom_ribbon(
    aes(
      ymin = mean - sd / 2,
      ymax = mean + sd / 2,
      fill = scenario
    ),
    color = NA,
    alpha = 0.2
  ) +
  geom_line(aes(color = scenario), size = 1) +
  scale_color_manual(
    values = scenario_colors,
    labels = c("CO2" = expression(CO[2]), "tempperci" = "Climate change", "N_dep" = "N deposition")
  ) +
  scale_fill_manual(
    values = scenario_colors,
     labels = c("CO2" = expression(CO[2]), "tempperci" = "Climate change", "N_dep" = "N deposition")
  ) +
  labs(
    title = "",
    x = "",
    y = "",
    color = "Climate Change Components"
  ) +
  theme_minimal() +
  theme(
    panel.border = element_rect(
      color = "black",
      fill = NA,
      size = 1
    ),
    plot.title = element_text(hjust = 0.5)
  ) +
  guides(color = guide_legend("Global Change\nComponents"),
         fill = guide_legend("Global Change\nComponents", override.aes = list(linetype = 1)))




global_legend <- cowplot::get_legend(p_global_legend)

## BGB #########################################################
in_Sbgb_file_default <- bgb_files[1]
in_Sbgb_file_2015co2 <- bgb_files[2]
in_Sbgb_file_ndep <- bgb_files[3]


in_Sbgb_default1 <- read.csv(in_Sbgb_file_default , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "default")
in_Sbgb_2015co21 <- read.csv(in_Sbgb_file_2015co2 , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "co22015")
in_Sbgb_ndep1 <- read.csv(in_Sbgb_file_ndep , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "ndep585")


in_Sbgb_co2<-in_Sbgb_default1%>%
  left_join(in_Sbgb_2015co21, by=c("region","child.nodes","below.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = default-co22015)%>%
  dplyr::select(-c("default","co22015"))

in_Sbgb_N_dep<-in_Sbgb_default1%>%
  left_join(in_Sbgb_ndep1, by=c("region","child.nodes","below.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ndep585-default)%>%
  dplyr::select(-c("default","ndep585"))

in_Sbgb_tempperci<-in_Sbgb_2015co21%>%
  mutate(scalar = co22015-1)%>%
  dplyr::select(-c("co22015"))


check_belowCD_long_gmean_co2 <- process_global_data(in_Sbgb_co2)
check_belowCD_long_gmean_N_dep <- process_global_data(in_Sbgb_N_dep)
check_belowCD_long_gmean_tempperci <- process_global_data(in_Sbgb_tempperci)

check_belowCD_long_gmean_co2 <- rbind(check_belowCD_long_gmean_co2, data.frame(harm_type = "Forest", year = 2015, mean = 0, sd = 0))
check_belowCD_long_gmean_N_dep <- rbind(check_belowCD_long_gmean_N_dep, data.frame(harm_type = "Forest", year = 2015, mean = 0, sd = 0))
check_belowCD_long_gmean_tempperci <- rbind(check_belowCD_long_gmean_tempperci, data.frame(harm_type = "Forest", year = 2015, mean = 0, sd = 0))

  
check_belowCD_long_gmean_combined <- check_belowCD_long_gmean_co2 %>%
  mutate(scenario = "CO2") %>%
  rbind(check_belowCD_long_gmean_tempperci %>%
          mutate(scenario = "tempperci"))%>%rbind(check_belowCD_long_gmean_N_dep %>%
          mutate(scenario = "N_dep"))


  ## save for check
  check_belowCD_long_gmean_combined_2100<-check_belowCD_long_gmean_combined%>%
    filter(year==2100)
  
  
  write.csv( check_belowCD_long_gmean_combined_2100,paste0(fig_save_path,"Fig20_check_belowCD_long_gmean_combined_2100",forcing_short,".csv"))
  
  write.csv( check_belowCD_long_gmean_combined,paste0(fig_save_path,"Fig20_check_belowCD_long_gmean_combined",forcing_short,".csv"))


  
  pbgb <- create_global_plot(
  check_belowCD_long_gmean_combined,
  y_var_m = "mean",
  y_var_sd = "sd",
  ylimits = c(-0.17, 0.09),
  if_title = FALSE,
  t_title = "BGB carbon scalar difference",
  if_xtitle = TRUE,
  x_title = "Year",
  if_ytitle = TRUE,
  y_title = "BGB carbon scalar difference",
  ifxlabel = TRUE,
  lab = "(b)",
  hj = 16.3)
  
  

combined_global_agbbgb_plot <- plot_grid(
  pagb,pbgb,  # Vertical stack of AGB and BGB plots
  global_legend,                 # Legend
  ncol = 3,                      # Two columns: one for plots, one for the legend
  rel_widths = c(1,1, 0.5)         # Relative widths, giving most space to the plots and less to the legend
)


save_combined_plot(combined_global_agbbgb_plot, paste0("Sagbbgb_global_CC_component",forcing_short),wid_size=20*0.5,hei_size=10*0.5)


```




