---
title: "GTM_4_dim_var_process"
author: "Meng Luo"
date: "2023-08-29"
output: html_document
    toc: true
    toc_float: true
---
# use the mature age's FP as the input for GCAM


#########################################################
## update of the this version
# add FULL_matrix_for_MFP_continue

# Content
## link to github
  S0 link to github
## Setting Up
  S1 needed R package and dir
 
  
  
  
  
# link to github
```{r S0 link to github , include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
```

# Setting Up
## Loading Needed R Packages and Setting Directory

```{r S1 needed R package and dir }
library(tidyverse)
library(tidyr)
#install.packages("rlang")
library(rlang)
library(dplyr)
library(gcamdata)
library('drake')
library(patchwork)
library(ggplot2)
library(cowplot)


## run this in console devtools::load_all()

Fig_num_name<-"Fig3_C_scalar"
version_num <-"4_C34_crops"
case_name<-"_climate_productivityC"
#################################################################################################
## need to modify 
# plot_case<-1 # diff SSPs
plot_case<-1 # diff CC component
 
cases<-c("3SSPs")

case<-cases[plot_case]


## end of need to modify 
# read from hard disk ##############################################################
# # Chen lab desktop
# # root<-"O:/"
# 
# # 2023 laptop
# root<-"D:/"
# 
# 
# main_Sagb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_aboveCD/region_5ymean_alltypes_wrapper/")
# 
# 
# main_Sbgb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_belowCD/region_5ymean_alltypes_wrapper/")
# 
# 
# 
# XML_version <- paste0(version_num ,case_name,"_ssp",case) 

####

# main_GTM_mid_xml_path  <-"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/useful/"
# main_my_XML_path <- "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/new_XML/"
# # produce outputs in GCAM 7.0 release package 
# main_v7_XML_path <- "E/Docker_GCAM_v7_forest/gcam-master/input/gcamdata/xml/"
# 
# fig_save_path <- paste0(root,"E/new laptop2/PHD/my_2024_1_manuscript/Figure&table/figure/check_npp_rh_scaler_4in1_file/")

# Harmolandtype_area_main_path<-paste0(root,"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/")
# read from 2023 laptop  ##############################################################

# 2023 laptop
# root <- "C:/MengLuo/chapter 2_backup/"

# NAS
root <- "Z:/Meng/back_up_all/9_updates/"

main_Sagb_path <- paste0(root, "climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_aboveCD/region_5ymean_alltypes_wrapper/")


main_Sbgb_path <- paste0(root, "climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_belowCD/region_5ymean_alltypes_wrapper/")

XML_version <- paste0(version_num ,case_name,"_ssp",case) 


#####

main_GTM_mid_xml_path  <-"climate_FPC_GCAM/Data/GCAM data system_forestversion/useful/"
main_my_XML_path <- "climate_FPC_GCAM/Data/GCAM data system_forestversion/new_XML/"
# produce outputs in GCAM 7.0 release package 
main_v7_XML_path <- "XML_save/"

fig_save_path <- paste0(root,"my_2024_1_manuscript/Figure&table/figure/check_npp_rh_scaler_4in1_file/")

Harmolandtype_area_main_path<-paste0(root,"climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/")

```


## read GTM output txt file
separate each var and save in csv

# function section


```{r S2 function save_result }
save_csv_result <- function(result_DF, result_csv_name,row_names) {

full_save_path <- paste0(root,main_GTM_path, result_csv_name)
if (row_names == TRUE) {
write.csv(result_DF,full_save_path, row.names = TRUE)
} else {
write.csv(result_DF,full_save_path, row.names = FALSE)
}

}
```

# preprocessing for GCAM XML
## I am right here


```{r S2 automatically read the file}

# agb_files <- list.files(path = main_Sagb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)
# 
# 
# bgb_files <- list.files(path = main_Sbgb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)
# 
# print(agb_files)
# print(bgb_files)
```

```{r S3 read harmonized land type area in each subregion table }


in_forest_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_forest.csv"))%>%
  mutate(harm_type="Forest")
  
in_c3crop_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_c3crop.csv"))%>%
  mutate(harm_type="c3Crop")

in_c4crop_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_c4crop.csv"))%>%
  mutate(harm_type="c4Crop")

in_grass_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_grass.csv"))%>%
  mutate(harm_type="Grass")

in_Harmolandtype_area <-bind_rows(in_forest_area,in_c3crop_area,in_c4crop_area,in_grass_area)
  


```

```{r S4 read the file}

### diff SSPs
sub_case_names<-c("SSP126","SSP370","SSP585")


agb_file_SSP126_gfdl <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp126_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP370_gfdl <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp370_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP585_gfdl <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
## ukesm
agb_file_SSP126_ukesm <- paste0(main_Sagb_path, "classic_ukesm1-0-ll_w5e5_ssp126_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP370_ukesm <- paste0(main_Sagb_path, "classic_ukesm1-0-ll_w5e5_ssp370_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP585_ukesm <- paste0(main_Sagb_path, "classic_ukesm1-0-ll_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")


bgb_file_SSP126_gfdl <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp126_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP370_gfdl <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp370_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP585_gfdl <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
## ukesm
bgb_file_SSP126_ukesm <- paste0(main_Sbgb_path, "classic_ukesm1-0-ll_w5e5_ssp126_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP370_ukesm <- paste0(main_Sbgb_path, "classic_ukesm1-0-ll_w5e5_ssp370_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP585_ukesm <- paste0(main_Sbgb_path, "classic_ukesm1-0-ll_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")

agb_files_gfdl<-c(agb_file_SSP126_gfdl,agb_file_SSP370_gfdl,agb_file_SSP585_gfdl)
agb_files_ukesm<-c(agb_file_SSP126_ukesm,agb_file_SSP370_ukesm,agb_file_SSP585_ukesm)

bgb_files_gfdl<-c(bgb_file_SSP126_gfdl,bgb_file_SSP370_gfdl,bgb_file_SSP585_gfdl)
bgb_files_ukesm<-c(bgb_file_SSP126_ukesm,bgb_file_SSP370_ukesm,bgb_file_SSP585_ukesm)
##############################

```

```{r S functions}
# Define a function to process the data
process_regional_data <- function(file_path, in_Harmolandtype_area) {
  data <- read.csv(file_path, check.names = FALSE)
  
  data %>%
    dplyr::select(-3, -2) %>%
    filter(harm_type != "Other") %>%
    left_join(in_Harmolandtype_area, by = c("out_reg_code", "out_lu_code", "harm_type")) %>%
    group_by(region, harm_type) %>%
    mutate(region_pft_area = sum(pft_area_total, na.rm = TRUE)) %>%
    mutate(region_pft_area_weight = pft_area_total / region_pft_area) %>%
    summarize(across(
      .cols = 6:20,
      .fns = ~ weighted.mean(.x, w = region_pft_area_weight, na.rm = TRUE)
    )) %>%
    ungroup() %>%
    pivot_longer(cols = 3:ncol(.),
                 names_to = "year",
                 values_to = "scalar") %>%
    mutate(year = as.numeric(year)) %>%
    na.omit()
}

##########################

save_combined_plot <- function(plot, name_suffix,wid_size=15,hei_size=10) {
  file_base <- paste0(fig_save_path, "/",Fig_num_name, "_combined_", name_suffix, "_v", version_num)
  
  ggsave(paste0(file_base, ".svg"), plot = plot, width = wid_size, height = hei_size, units = "in")
  ggsave(paste0(file_base, ".pdf"), plot = plot, width = wid_size, height = hei_size, units = "in")
  ggsave(paste0(file_base, ".png"), plot = plot, width = wid_size, height = hei_size, units = "in", dpi = 300)
  ggsave(filename = paste0(file_base, ".tif"), plot = plot, width = wid_size, height = hei_size, units = "in", device = "tiff", dpi = 300)
}
#########################
# Function to create individual plots
# create_regional_plot <- function(data, harm_type, x_label = "", y_label = "", title_suffix = "", ylim_range = c(-0.8, 0.6)) {
#   ggplot(data %>% filter(harm_type == harm_type), aes(x = as.numeric(year), y = forcing_diff, group = region, color = region)) +
#     geom_line() +
#     labs(title = paste0(harm_type, title_suffix),
#          x = x_label,
#          y = y_label,
#          color = "Region") +
#     theme_minimal() +
#     theme(
#       panel.border = element_rect(color = "black", fill = NA, size = 1),
#       legend.position = "none",
#       plot.title = element_text(hjust = 0.5)
#     ) +
#     ylim(ylim_range)
# }

############################



 # Function to process agb files
process_global_file <- function(data, harmolandtype_area) {
  
    data %>%
    dplyr::select(-3) %>%
    filter(harm_type != "Other") %>%
    group_by(child.nodes) %>%
    pivot_wider(names_from = "year",values_from = "scalar")%>%
    ungroup()%>%
    dplyr::select(-2) %>%
    left_join(in_Harmolandtype_area, by = c("out_reg_code", "out_lu_code", "harm_type")) %>%
    group_by(harm_type) %>%
    mutate(global_pft_area = sum(pft_area_total, na.rm = TRUE)) %>%
    mutate(global_pft_area_weight = pft_area_total / global_pft_area) %>%
    summarize(across(
    .cols = 7:23,
    .fns = list(
      mean = ~ weighted.mean(.x, w = global_pft_area_weight, na.rm = TRUE),
      sd = ~ sqrt(weighted.mean((.x - weighted.mean(.x, w = global_pft_area_weight, na.rm = TRUE))^2, w = global_pft_area_weight, na.rm = TRUE))
    )
  )) %>%
  ungroup() %>%
  pivot_longer(cols = ends_with("_mean") | ends_with("_sd"),
               names_to = "year_stat",
               values_to = "value") %>%
  separate(year_stat, into = c("year", "stat"), sep = "_", convert = TRUE) %>%
  pivot_wider(names_from = stat, values_from = value) %>%
  mutate(year = as.numeric(year)) %>%
  dplyr::select(harm_type, year, mean, sd) %>%
    na.omit()
}
```




```{r S5 plot and save agb scaler group map}



##########################
# Initialize an empty list to store plots
pagb_list <- list()
agbfignum <- c("(a)","(b)","(c)")
y_titles<-c("AGB carbon scalar difference","","")
ahjusts<-c(10,10.01,10.25)


for (data_idx in c(1, 2, 3)) {
  # data_idx<-1
  
  
  # Process the data for GFDL
  in_Sagb_file_gfdl <- agb_files_gfdl[data_idx]
  in_Sagb_file_ukesm <- agb_files_ukesm[data_idx]
  
  
  
    ###########################################
  
  
  # Process each dataset using the function
  
  in_Sagb_gfdl<-read.csv(in_Sagb_file_gfdl , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "gfdl")
  
  in_Sagb_ukesm<-read.csv(in_Sagb_file_ukesm , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "ukesm")
  
  aboveCD_global_foring_diff<-in_Sagb_gfdl%>%
  left_join(in_Sagb_ukesm, by=c("region","child.nodes","above.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ukesm-gfdl)%>%
  dplyr::select(-c("gfdl","ukesm"))
  
  
  
  
   check_aboveCD_global_foring_diff <-
    process_global_file(aboveCD_global_foring_diff, in_Harmolandtype_area)%>%
    # replace c3Crop with C3crop, c4Crop with C4crop
    mutate(harm_type = gsub("c3Crop", "C3 crops", harm_type))%>%
    mutate(harm_type = gsub("c4Crop", "C4 crops", harm_type))
   
   check_aboveCD_global_foring_diff <- rbind(check_aboveCD_global_foring_diff, data.frame(harm_type = "Forest",  year = 2015, mean = 0, sd = 0),data.frame(harm_type = "Grass",  year = 2015, mean = 0, sd = 0),data.frame(harm_type = "C3 crops",  year = 2015, mean = 0, sd = 0),data.frame(harm_type = "C4 crops",  year = 2015, mean = 0, sd = 0))
  
  #############
  pagb_list[[data_idx]] <- ggplot(check_aboveCD_global_foring_diff, aes(x = as.numeric(year), y = mean, group = harm_type, color = harm_type))+
    geom_ribbon(aes(ymin = mean - sd/2, ymax = mean + sd/2, fill = harm_type), color = NA, alpha = 0.2, show.legend = FALSE) +
    geom_line(aes(color = harm_type), size = 1, show.legend = FALSE) +
  labs(title = sub_case_names[data_idx],
       x = "",
       y = y_titles[data_idx],
       color = "Harmonized Types") +
  theme_minimal() +
  theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.text.x = element_blank(),  # Removes x-axis tick labels
        axis.ticks.x = element_blank()  # Removes x-axis ticks
        )    + ylim(c(-0.3, 0.3))+
    annotate(
      "text",
      x = Inf,
      y = Inf,
      label = agbfignum[data_idx],
      hjust = ahjusts[data_idx],
      vjust = 1.5,
      size = 4
    )
  
 if (data_idx > 1) {
  pagb_list[[data_idx]] <- pagb_list[[data_idx]] +
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
}
   
}




p_global_legend <- ggplot(check_aboveCD_global_foring_diff, aes(x = as.numeric(year), y = mean, group = harm_type, color = harm_type))+
    geom_ribbon(aes(ymin = mean - sd/2, ymax = mean + sd/2, fill = harm_type), color = NA, alpha = 0.2) +
    geom_line(aes(color = harm_type), size = 1) +
  labs(title = sub_case_names[data_idx],
       x = "",
       y = y_titles[data_idx],
       color = "Harmonized Types") +
  theme_minimal() +
  theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
        plot.title = element_text(hjust = 0.5))  +
  guides(color = guide_legend("Harmonized Types"), fill = guide_legend("Harmonized Types", override.aes = list(linetype = 1)))


global_legend <- cowplot::get_legend(p_global_legend)

combined_agb_plots <- wrap_plots(pagb_list, nrow = 1)

```

```{r S6 plot and save bgb scaler group map}



##########################
# Initialize an empty list to store plots
pbgb_list <- list()
y_titles<-c("BGB carbon scalar difference","","")
 

bgbfignum <- c("(d)","(e)","(f)")
bhjusts<-c(10,10,12.7)

for (data_idx in c(1, 2, 3)) {
  # data_idx<-1
  
  
  
  # Process the data for GFDL
  in_Sbgb_file_gfdl <- bgb_files_gfdl[data_idx]
  in_Sbgb_file_ukesm <- bgb_files_ukesm[data_idx]
  
  
  
    ###########################################
  
  
  # Process each dataset using the function
  
  in_Sbgb_gfdl<-read.csv(in_Sbgb_file_gfdl , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "gfdl")
  
  in_Sbgb_ukesm<-read.csv(in_Sbgb_file_ukesm , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "ukesm")
  
  belowCD_global_foring_diff<-in_Sbgb_gfdl%>%
  left_join(in_Sbgb_ukesm, by=c("region","child.nodes","below.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ukesm-gfdl)%>%
  dplyr::select(-c("gfdl","ukesm"))
  
  
  
  
   check_belowCD_global_foring_diff <-
    process_global_file(belowCD_global_foring_diff, in_Harmolandtype_area)%>%
    # replace c3Crop with C3crop, c4Crop with C4crop
    mutate(harm_type = gsub("c3Crop", "C3 crops", harm_type))%>%
    mutate(harm_type = gsub("c4Crop", "C4 crops", harm_type))
  
  
  check_belowCD_global_foring_diff <- rbind(check_belowCD_global_foring_diff, data.frame(harm_type = "Forest",  year = 2015, mean = 0, sd = 0),data.frame(harm_type = "Grass",  year = 2015, mean = 0, sd = 0),data.frame(harm_type = "C3 crops",  year = 2015, mean = 0, sd = 0),data.frame(harm_type = "C4 crops",  year = 2015, mean = 0, sd = 0))
  
  
  pbgb_list[[data_idx]] <- ggplot(check_belowCD_global_foring_diff, aes(x = as.numeric(year), y = mean, group = harm_type, color = harm_type))+
    geom_ribbon(aes(ymin = mean - sd/2, ymax = mean + sd/2, fill = harm_type), color = NA, alpha = 0.2, show.legend = FALSE) +
    geom_line(aes(color = harm_type), size = 1, show.legend = FALSE) +
  labs(title = NULL,
       x = "Year",
       y = y_titles[data_idx],
       color = "Harmonized Types") +
  theme_minimal() +
  theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
        plot.title = element_text(hjust = 0.5))  + ylim(c(0.87, 1.06)) +
    annotate(
      "text",
      x = Inf,
      y = Inf,
      label = bgbfignum[data_idx],
      hjust = bhjusts[data_idx],
      vjust = 1.5,
      size = 4
    )+ ylim(c(-0.15, 0.15))
  
  # Conditionally remove y-axis labels and ticks when data_idx > 1
if (data_idx > 1) {
  pbgb_list[[data_idx]] <- pbgb_list[[data_idx]] +
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
}
  
}

combined_bgb_plots <- wrap_plots(pbgb_list, nrow = 1)

```
######

```{r agb bgb global combined save}
agb_bgb_list<-c(pagb_list,pbgb_list)
combined_global_agbbgb_plots <- wrap_plots(agb_bgb_list, nrow = 2)  # Combine AGB plots into a single row


combined_global_agbbgb_plot <- plot_grid(
  combined_global_agbbgb_plots,  # Vertical stack of AGB and BGB plots
  global_legend,                 # Legend
  ncol = 2,                      # Two columns: one for plots, one for the legend
  rel_widths = c(1, 0.2)         # Relative widths, giving most space to the plots and less to the legend
)


 save_combined_plot(combined_global_agbbgb_plot, "Sagbbgb_global_3SSPs_forcing",wid_size=18*0.5,hei_size=10*0.5)
 
```
