---
title: "GTM_4_dim_var_process"
author: "Meng Luo"
date: "2023-08-29"
output: html_document
    toc: true
    toc_float: true
---
# use the mature age's FP as the input for GCAM


#########################################################
## update of the this version
# add FULL_matrix_for_MFP_continue

# Content
## link to github
  S0 link to github
## Setting Up
  S1 needed R package and dir
  S2 function save_result
## functions
  S3 GCAM XML generation prepare
  S4 read new AGB scaler
## pre-processing for GCAM XML
  S5 update ag cost for crop bio and forest
  S6_1 update forest and pasture productivity change
  S6_2 update crop productivity change
  S6_3 update bio productivity change
## old code and draft below this line
  S7 old code, include = FALSE
  
  
  
# link to github
```{r S0 link to github , include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
```

# Setting Up
## Loading Needed R Packages and Setting Directory

```{r S1 needed R package and dir }
library(tidyverse)
library(tidyr)
#install.packages("rlang")
library(rlang)
library(dplyr)
library(gcamdata)
library('drake')
## run this in console devtools::load_all()

#################################################################################################
## need to modify 

## hard disk ############################################### 
## computer
# root<-"O:/E/new laptop2/PHD/phd_dissertation/"

## newlaptop
# root<-"D:/E/new laptop2/PHD/phd_dissertation/"
# root2<-"D:/"
# produce outputs in GCAM 7.0 release package
# main_v7_XML_path <- "E/GCAMv7Forestry-master_VS/GCAMv7Forestry-master/input/gcamdata/xml/"
## 2023 laptop###############################################
# root <- "C:/MengLuo/chapter 2_backup/"
# root2<-"C:/MengLuo/chapter 2_backup/"

## desktop NAS #########################################
root <- "Z:/Meng/Chapter 3/"

root2 <- "Z:/Meng/Chapter 3/"
#Z:\Meng\Chapter 3\GCAMv7Forestry-master
# produce outputs in GCAM 7.0 forest breakout folder
main_v7_XML_path <- "GCAMv7Forestry-master/input/gcamdata/xml/"



## ssp1
# scenario<-"ssp126_2015soc-from-histsoc_default" #  n for SSPn e.g. 1 for SSP1
# climate_model<-"gfdl-esm4"#"ukesm1-0-ll" #"gfdl-esm4"
# biome_model<-"classic"

## ssp3
scenario<-"ssp370_2015soc-from-histsoc_default" #  n for SSPn e.g. 1 for SSP1
climate_model<-"gfdl-esm4" #"gfdl-esm4"# "ukesm1-0-ll"
biome_model<-"classic"

# ssp5
# scenario<-"ssp585_2015soc-from-histsoc_default" # _default, _ssp585ndep, _2015co2 n for SSPn e.g. 1 for SSP1
# climate_model<-"ukesm1-0-ll"#"ukesm1-0-ll" #"gfdl-esm4"
# biome_model<-"classic"


version_num <-"1"
case_name<-"_climate_productivityC"




## end of need to modify 
#################################################################################################

# Z:\Meng\Chapter 3\ISIMIP_GTM_GCAM\Data\ISIMIP_3b_process\GCAM_subregion_mean\aboveCD

main_producticity_path <- paste0(root, "ISIMIP_GTM_GCAM/Data/ISIMIP_3b_process/GCAM_subregion_mean/aboveCD/region_5ymean_alltypes_wrapper/")

XML_version <- paste0(version_num ,case_name,"_",biome_model,"_",climate_model,"_",scenario) 

## end need to modify 
#########################

main_GTM_mid_xml_path  <-"ISIMIP_GTM_GCAM/Data/GCAM data system_forestversion/useful/"
main_my_XML_path <- "ISIMIP_GTM_GCAM/Data/GCAM data system_forestversion/new_XML/"


# choose aggregation methods #####################
## SSP1 and SSP5

# L2052_AgProdChange_hi_file <-  paste0(root,main_GTM_mid_xml_path, "L2052.AgProdChange_irr_high.csv")
# L2052_AgProdChange_irr <- read.csv(L2052_AgProdChange_hi_file, skip = 2)
# # Define file names
# v7_crop_XML_file <- paste0(root2, main_v7_XML_path, "ag_prodchange_crop_subregion_irr_hi_", as.character(XML_version), ".xml")
# GTM_crop_XML_file <- paste0(root, main_my_XML_path, "ag_prodchange_crop_subregion_irr_hi_", as.character(XML_version), ".xml")


# ## SSP3 
L2052_AgProdChange_lo_file <-  paste0(root,main_GTM_mid_xml_path, "L2052.AgProdChange_irr_low.csv")
L2052_AgProdChange_irr <- read.csv(L2052_AgProdChange_lo_file, skip = 2)
# Define file names
v7_crop_XML_file <- paste0(root, main_v7_XML_path, "ag_prodchange_crop_subregion_irr_lo_", as.character(XML_version), ".xml")
GTM_crop_XML_file <- paste0(root, main_my_XML_path, "ag_prodchange_crop_subregion_irr_lo_", as.character(XML_version), ".xml")

## end need to modify 
#########################
```

## read GTM output txt file
separate each var and save in csv
# function section
```{r S2 function save_result }
save_csv_result <- function(result_DF, result_csv_name,row_names) {

full_save_path <- paste0(root,main_GTM_path, result_csv_name)
if (row_names == TRUE) {
write.csv(result_DF,full_save_path, row.names = TRUE)
} else {
write.csv(result_DF,full_save_path, row.names = FALSE)
}

}
```

# preprocessing for GCAM XML
## I am right here

```{r S3 GCAM XML generation prepare}


all_region <- c("Africa_Eastern",
"Africa_Northern",
"Africa_Southern",
"Africa_Western",
"Argentina",
"Australia_NZ",
"Brazil",
"Canada",
"Central America and Caribbean",
"Central Asia",
"China",
"Colombia",
"EU-12",
"EU-15",
"Europe_Eastern",
"Europe_Non_EU",
"European Free Trade Association",
"India",
"Indonesia",
"Japan",
"Mexico",
"Middle East",
"Pakistan",
"Russia",
"South Africa",
"South America_Northern",
"South America_Southern",
"South Asia",
"South Korea",
"Southeast Asia",
"Taiwan",
"USA"
)

```

```{r S4 read new AGB scaler }


in_Sagb_file<-paste0(main_producticity_path,biome_model,"_",climate_model,"_w5e5_",scenario,"_fullscalerc3c4_agb_chapter3.csv")
in_Sagb <-read.csv(in_Sagb_file,check.names = FALSE)

in_Sagb_long<-in_Sagb%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "agb_scaler")%>%
  dplyr::select(region, child.nodes,landtype,subregion,broad_type,harm_type, year,agb_scaler)%>%
  mutate(year=as.numeric(year))

in_Sagb_long1<-in_Sagb%>%
  mutate("2015" = 1)%>%
  pivot_longer(cols = 10:27,names_to = "year",values_to = "agb_scaler")%>%
  dplyr::select(region, child.nodes,landtype,subregion,broad_type,harm_type, year,agb_scaler)%>%
  mutate(year=as.numeric(year))%>%
  arrange(region, child.nodes,landtype,subregion,broad_type,harm_type, year)
  

check<-in_Sagb_long%>%
  filter(landtype=="FodderGrass")


in_Sagb_file2<-paste0(main_producticity_path,biome_model,"_",climate_model,"_w5e5_",scenario,"_regional_scale_fullscaler_yieldc3c4.csv")
in_Sagb2 <-read.csv(in_Sagb_file2,check.names = FALSE)

in_Sagb_long2<-in_Sagb2%>%
  dplyr::select(-c("AgProdChange","year","out_reg_code","out_lu_code"))%>%
  mutate("2015" = 1)%>%
  pivot_longer(cols = 8:25,names_to = "year",values_to = "agb_scaler")%>%
  # rename(AgProductionTechnology = child.nodes)%>%
  # in_Sagb_long2<-in_Sagb_long2%>%
  dplyr::select(region, AgProductionTechnology,landtype,subregion,harm_type, year,agb_scaler)%>%
  distinct()%>%
  mutate(year=as.numeric(year))%>%
  arrange(region, AgProductionTechnology,year)



in_Sagb_file3<-paste0(main_producticity_path,biome_model,"_", climate_model,"_w5e5_",scenario,"_regional_scale_fullscaler_bio_yieldc3c4.csv")
in_Sagb3 <-read.csv(in_Sagb_file3,check.names = FALSE)

in_Sagb_long3<-in_Sagb3%>%
  dplyr::select(-c("AgProdChange","year","out_reg_code","out_lu_code"))%>%
  mutate("2015" = 1)%>%
  pivot_longer(cols = 8:25,names_to = "year",values_to = "agb_scaler")%>%
  # rename(AgProductionTechnology = child.nodes)%>%
  # in_Sagb_long2<-in_Sagb_long2%>%
  dplyr::select(region, AgProductionTechnology,landtype,subregion,harm_type, year,agb_scaler)%>%
  distinct()%>%
  mutate(year=as.numeric(year))%>%
  arrange(region, AgProductionTechnology,year)
  

```


## generate ag cost XML
```{r S5 update ag cost for crop bio and forest }

# read L2052.AgCost_For
L2052.AgCost_For_path <- paste0(root,main_GTM_mid_xml_path,"L2052.AgCost_For.csv")
L2062.AgCost_ag_path <- paste0(root,main_GTM_mid_xml_path,"L2062.AgCost_ag_irr_mgmt_adj.csv")
L2062.AgCost_bio_path <- paste0(root,main_GTM_mid_xml_path,"L2062.AgCost_bio_irr_mgmt_adj.csv")

L2052.AgCost_For <- read.csv(L2052.AgCost_For_path, skip = 1)
L2062.AgCost_ag <- read.csv(L2062.AgCost_ag_path, skip = 2)
L2062.AgCost_bio <- read.csv(L2062.AgCost_bio_path, skip = 2)


in_Sagb_file2<-paste0(main_producticity_path,biome_model,"_", climate_model,"_w5e5_",scenario,"_regional_scale_fullscaler_yieldc3c4.csv")
in_Sagb2 <-read.csv(in_Sagb_file2,check.names = FALSE)

# Function to process AgCost data
process_AgCost_data <- function(data, in_Sagb_long) {
  # Filter data for years before and starting from 2020
  data_before_2020 <- data %>%
    filter(year <= 2020)
  
  data_new <- data %>%
    filter(year >= 2020) %>%
    mutate(subregion = sub(".*_(.*)$", "\\1", AgSupplySubsector)) %>%
    left_join(in_Sagb_long, by = c("region", "subregion", "year", "AgSupplySector" = "broad_type")) %>%
    mutate(nonLandVariableCost = nonLandVariableCost / agb_scaler) %>%
    dplyr::select(1:6) %>%
    rbind(data_before_2020) %>%
    arrange(region, AgSupplySector, AgSupplySubsector, year)
  
  return(data_new)
}


process_AgCost_ag_data <- function(data, in_Sagb_long) {
  # Filter data for years before and starting from 2020
  
  # data<-L2062.AgCost_bio
  # in_Sagb_long<-in_Sagb_long3
  # 
  # check<-in_Sagb_long%>%
  #   filter(AgProductionTechnology=="Soybean_CaspianNE_IRR_lo")
  # 
  data_before_2020 <- data %>%
    filter(year <= 2020)
  
  data_new <- data %>%
    filter(year >= 2020) %>%
    mutate(subregion = sub(".*_(.*)$", "\\1", AgSupplySubsector)) %>%
    # mutate(landtype = sub("_.*", "", AgSupplySubsector)) %>%
    left_join(in_Sagb_long, by = c("region", "subregion", "year", "AgProductionTechnology")) %>%
    mutate(nonLandVariableCost = nonLandVariableCost / agb_scaler) %>%
    dplyr::select(1:6) %>%
    rbind(data_before_2020) %>%
    arrange(region, AgSupplySector, AgSupplySubsector, year)
  
  return(data_new)
}
# Apply the function to the specific datasets
L2052.AgCost_For_new <- process_AgCost_data(L2052.AgCost_For,  in_Sagb_long)
L2062.AgCost_bio_new <- process_AgCost_ag_data(L2062.AgCost_bio,  in_Sagb_long3)

L2062.AgCost_ag_new <- process_AgCost_ag_data(L2062.AgCost_ag,  in_Sagb_long2)




# library(dplyr)

# Function to create XML path
create_xml_path <- function(root, main_path, type, version) {
  paste0(root, main_path, 'ag_cost_IRR_MGMT_', type, '_', as.character(version), '.xml')
}

# Function to process XML creation and data addition
process_xml <- function(xml_path, data, data_tag) {
  
  # xml_path<-my_for_XML_path
  # data<-L2052.AgCost_For_new
  # data_tag<-"AgCost"
 
  xml_filename <- create_xml(xml_path) %>%
    add_xml_data(data, data_tag)

  
  xml_filename %>%
    gcamdata::run_xml_conversion()
  
  return(xml_filename)
}



# Process for forest managed
my_for_XML_path <- create_xml_path(root, main_my_XML_path, "for", XML_version)
v7_for_XML_path <- create_xml_path(root2, main_v7_XML_path, "for", XML_version)

process_xml(my_for_XML_path, L2052.AgCost_For_new, "AgCost")
process_xml(v7_for_XML_path, L2052.AgCost_For_new, "AgCost")

# Process for agriculture managed
my_ag_XML_path <- create_xml_path(root, main_my_XML_path, "ag", XML_version)
v7_ag_XML_path <- create_xml_path(root2, main_v7_XML_path, "ag", XML_version)

process_xml(my_ag_XML_path, L2062.AgCost_ag_new, "AgCost")
process_xml(v7_ag_XML_path, L2062.AgCost_ag_new, "AgCost")

# Process for biomass managed
my_ag_XML_path <- create_xml_path(root, main_my_XML_path, "bio", XML_version)
v7_ag_XML_path <- create_xml_path(root2, main_v7_XML_path, "bio", XML_version)

process_xml(my_ag_XML_path, L2062.AgCost_bio_new, "AgCost")
process_xml(v7_ag_XML_path, L2062.AgCost_bio_new, "AgCost")


```


## generate forest productivity XML
```{r S6_1 update forest and pasture productivity change}

# read ag product change file's template


# read L2052_AgProdChange_ag_irr_ref (ag_prd_change template)
L2052_AgProdChange_file <-  paste0(root,main_GTM_mid_xml_path, "L2052.AgProdChange_ag_irr_ref.csv") 
L2052_AgProdChange_ag_irr_ref <- read.csv(L2052_AgProdChange_file, skip = 1)
####################################################################

# Function to read CSV files
read_csv_file <- function(file_path) {
  read.csv(file_path, skip = 1)
}

# Function to prepare GCAM PFC template
prepare_gcam_pfc_template <- function(data, sector) {
  data %>%
    mutate(AgSupplySector = sector,
           AgSupplySubsector = LandLeaf,
           AgProductionTechnology = LandLeaf) %>%
    dplyr::select(region, AgSupplySector, AgSupplySubsector, AgProductionTechnology, year)
}

# Function to expand years and add subregion
expand_years_and_subregion <- function(data) {
  data %>%
    complete(year = seq(2020, 2100, 5), 
             nesting(region, AgSupplySector, AgSupplySubsector, AgProductionTechnology)) %>%
    filter(year >= 2020) %>%
    mutate(subregion = sub(".*_(.*)$", "\\1", AgSupplySubsector))
}

# Function to replace AgProdChange with GTM's value
replace_agprodchange_with_gtm <- function(expanded_data, gtm_data, sector) {
  expanded_data %>%
    left_join(gtm_data %>% mutate(year = as.integer(year)), by = c("region", "subregion", "year")) %>%
    mutate(AgProdChange = case_when(
      GCAM_subregion_ag_prodc >= 2 ~ 2,
      GCAM_subregion_ag_prodc < -2 ~ -2,
      TRUE ~ GCAM_subregion_ag_prodc
    )) %>%
    dplyr::select(-GCAM_subregion_ag_prodc) %>%
    dplyr::select(region, AgSupplySector, AgSupplySubsector, AgProductionTechnology, year, AgProdChange)
}

# Define file paths
L223_LN3_MgdAllocation_noncrop_file <- paste0(root, main_GTM_mid_xml_path, "L2231.LN3_MgdAllocation_noncrop.csv")
L222_LN2_MgdAllocation_file <- paste0(root, main_GTM_mid_xml_path, "L222.LN2_MgdAllocation.csv")

# Read CSV files
L223_LN3_MgdAllocation_noncrop <- read_csv_file(L223_LN3_MgdAllocation_noncrop_file)
L222_LN2_MgdAllocation <- read_csv_file(L222_LN2_MgdAllocation_file)

# Prepare GCAM PFC templates
L223_LN3_MgdAllocation_forest <- prepare_gcam_pfc_template(L223_LN3_MgdAllocation_noncrop, "Forest")
L222_LN2_MgdAllocation_pasture <- prepare_gcam_pfc_template(L222_LN2_MgdAllocation, "Pasture")

# Expand years and add subregions
expanded_dataframe_forest <- expand_years_and_subregion(L223_LN3_MgdAllocation_forest)
expanded_dataframe_pasture <- expand_years_and_subregion(L222_LN2_MgdAllocation_pasture)

# Select necessary columns for GTM data
in_Sagb_long_needed_forest <- in_Sagb_long1 %>%
  mutate(GCAM_subregion_ag_prodc = (agb_scaler/lag(agb_scaler))^(1/5) - 1) %>%
  filter(landtype == "Forest") %>%
  filter(year >= 2020) %>%
  dplyr::select(region, subregion, year, landtype, GCAM_subregion_ag_prodc)

in_Sagb_long_needed_pasture <- in_Sagb_long1 %>%
  mutate(GCAM_subregion_ag_prodc = (agb_scaler/lag(agb_scaler))^(1/5) - 1) %>%
  filter(landtype == "Pasture") %>%
  filter(year >= 2020) %>%
  dplyr::select(region, subregion, year, landtype, GCAM_subregion_ag_prodc)

# Replace AgProdChange with ISIMIP's value
L2052.AgProdChange_ag_forest_new <- replace_agprodchange_with_gtm(expanded_dataframe_forest, in_Sagb_long_needed_forest, "Forest")
L2052.AgProdChange_ag_pasture_new <- replace_agprodchange_with_gtm(expanded_dataframe_pasture, in_Sagb_long_needed_pasture, "Pasture")

# Define file names
v7_FP_XML_file <- paste0(root2, main_v7_XML_path, "ag_prodchange_forest_subregion_", as.character(XML_version), ".xml")
v7_pasture_XML_file <- paste0(root2, main_v7_XML_path, "ag_prodchange_pasture_subregion_", as.character(XML_version), ".xml")
GTM_FP_XML_file <- paste0(root, main_my_XML_path, "ag_prodchange_forest_subregion_", as.character(XML_version), ".xml")
GTM_pasture_XML_file <- paste0(root, main_my_XML_path, "ag_prodchange_pasture_subregion_", as.character(XML_version), ".xml")

# Save data in XML format
create_xml(v7_FP_XML_file) %>% add_xml_data(L2052.AgProdChange_ag_forest_new, "AgProdChange") -> ag_prodchange_MGMT_forest.xml
create_xml(v7_pasture_XML_file) %>% add_xml_data(L2052.AgProdChange_ag_pasture_new, "AgProdChange") -> ag_prodchange_MGMT_pasture.xml
create_xml(GTM_FP_XML_file) %>% add_xml_data(L2052.AgProdChange_ag_forest_new, "AgProdChange") -> ag_prodchange_MGMT_forest2.xml
create_xml(GTM_pasture_XML_file) %>% add_xml_data(L2052.AgProdChange_ag_pasture_new, "AgProdChange") -> ag_prodchange_MGMT_pasture2.xml

# Run XML conversion
ag_prodchange_MGMT_forest.xml %>% gcamdata::run_xml_conversion()
ag_prodchange_MGMT_pasture.xml %>% gcamdata::run_xml_conversion()
ag_prodchange_MGMT_forest2.xml %>% gcamdata::run_xml_conversion()
ag_prodchange_MGMT_pasture2.xml %>% gcamdata::run_xml_conversion()



```


```{r S6_2 update crop productivity change}
####################################################################
######## important !!!!!!!!!########################################
####################################################################
####################################################################
####################################################################

# SSP1, SSP5: L2052.AgProdChange_irr_high
# SSP3: L2052.AgProdChange_irr_low
# please find the file read code in S1
####################################################################
######## important !!!!!!!!!########################################
####################################################################





#######################################################
#######################################################  
#######################################################

# Select necessary columns for ISIMIP data
in_Sagb_long_needed_crop <- in_Sagb_long2 %>%
  group_by(region, AgProductionTechnology)%>%
  mutate(GCAM_subregion_ag_prodc = (agb_scaler/lag(agb_scaler))^(1/5)) %>%
  ungroup()%>%
  filter(harm_type %in% c("c3Crop","c4Crop","Grass"))%>%
  dplyr::select(region, year, AgProductionTechnology, GCAM_subregion_ag_prodc)%>%
  filter(year>=2020)

check<-in_Sagb_long_needed_crop%>%
  filter(is.na(AgProductionTechnology))

L2052_AgProdChange_irr_new<-L2052_AgProdChange_irr%>%
  # mutate(subregion = sub(".*_(.*)$", "\\1", AgSupplySubsector))%>%
  left_join(in_Sagb_long_needed_crop, by=c("region",  "year", "AgProductionTechnology"))%>%
  mutate(AgProdChange = GCAM_subregion_ag_prodc*(1+AgProdChange)-1)%>%
  dplyr::select(-GCAM_subregion_ag_prodc)

# Replace AgProdChange with ISIMIP's value
check2<-L2052_AgProdChange_irr_new%>%
  filter(AgSupplySector== "FodderGrass")




# Save data in XML format
create_xml(v7_crop_XML_file) %>% add_xml_data(L2052_AgProdChange_irr_new, "AgProdChange") -> ag_prodchange_MGMT_crop.xml

create_xml(GTM_crop_XML_file) %>% add_xml_data(L2052_AgProdChange_irr_new, "AgProdChange") -> ag_prodchange_MGMT_crop2.xml


# Run XML conversion
ag_prodchange_MGMT_crop.xml %>% gcamdata::run_xml_conversion()
ag_prodchange_MGMT_crop2.xml %>% gcamdata::run_xml_conversion()




```

```{r S6_3 update bio productivity change}

# read ag product change file's template

####################################################################


# read L2052_AgProdChange_ag_irr_ref (ag_prd_change template)


# in_Sagb_file2<-paste0(main_producticity_path,biome_model,"_", climate_model,"_w5e5_",scenario,"_fullscaler_yieldc3c4.csv")
# in_Sagb2 <-read.csv(in_Sagb_file2,check.names = FALSE)



L2052_AgProdChange_bio_ref_file <-  paste0(root,main_GTM_mid_xml_path, "L2052.AgProdChange_bio_irr_ref.csv") 
L2052_AgProdChange_bio_irr_ref <- read.csv(L2052_AgProdChange_bio_ref_file, skip = 1)


in_Sagb_long<-in_Sagb%>%
  rename(AgProductionTechnology=child.nodes)%>%
  dplyr::select(-c("above.ground.carbon.density","out_reg_code","out_lu_code"))%>%
  mutate("2015" = 1)%>%
  pivot_longer(cols = 7:24,names_to = "year",values_to = "agb_scaler")%>%
  # rename(AgProductionTechnology = child.nodes)%>%
  dplyr::select(region, AgProductionTechnology,landtype,subregion,harm_type, year,agb_scaler)%>%
  mutate(year=as.numeric(year))%>%
  arrange(region, AgProductionTechnology,year)
  
##############################################

# Select necessary columns for GTM data
in_Sagb_long_needed_bio <- in_Sagb_long %>%
  group_by(region, AgProductionTechnology)%>%
  mutate(GCAM_subregion_ag_prodc = (agb_scaler/lag(agb_scaler))^(1/5)) %>%
  ungroup()%>%
  filter(harm_type %in% c("c4Crop","c3Crop","Forest"))%>%
  dplyr::select(region, year, AgProductionTechnology, GCAM_subregion_ag_prodc)%>%
  filter(year>=2020)

check<-in_Sagb_long_needed_bio%>%
  filter(is.na(AgProductionTechnology))

L2052_AgProdChange_bio_irr_ref_new<-L2052_AgProdChange_bio_irr_ref%>%
  # mutate(subregion = sub(".*_(.*)$", "\\1", AgSupplySubsector))%>%
  left_join(in_Sagb_long_needed_bio, by=c("region",  "year", "AgProductionTechnology"))%>%
  mutate(AgProdChange = GCAM_subregion_ag_prodc*(1+AgProdChange)-1)%>%
  dplyr::select(-GCAM_subregion_ag_prodc)

# Replace AgProdChange with ISIMIP's value


# Define file names
v7_bio_XML_file <- paste0(root2, main_v7_XML_path, "ag_prodchange_bio_subregion_irr_ref_", as.character(XML_version), ".xml")

GTM_bio_XML_file <- paste0(root, main_my_XML_path, "ag_prodchange_bio_subregion_irr_ref_", as.character(XML_version), ".xml")


# Save data in XML format
create_xml(v7_bio_XML_file) %>% add_xml_data(L2052_AgProdChange_bio_irr_ref_new, "AgProdChange") -> ag_prodchange_MGMT_bio.xml

create_xml(GTM_bio_XML_file) %>% add_xml_data(L2052_AgProdChange_bio_irr_ref_new, "AgProdChange") -> ag_prodchange_MGMT_bio2.xml


# Run XML conversion
ag_prodchange_MGMT_bio.xml %>% gcamdata::run_xml_conversion()
ag_prodchange_MGMT_bio2.xml %>% gcamdata::run_xml_conversion()




```
# old code and draft below this line
```{r S7 old code, include = FALSE}
#############################################################
# ## forest
# 
# # read L2231.LN3_MgdAllocation_noncrop (to get subregion with managed forest)
# L223_LN3_MgdAllocation_noncrop_file <-  paste0(root,main_GTM_mid_xml_path, "L2231.LN3_MgdAllocation_noncrop.csv")
# L223_LN3_MgdAllocation_noncrop <- read.csv(L223_LN3_MgdAllocation_noncrop_file, skip = 1)
# 
# # make new GCAM PFC template with all managed forest region
# L223_LN3_MgdAllocation_forest <- L223_LN3_MgdAllocation_noncrop %>%
#   # all type in this file belongs to managed forest
#   mutate(AgSupplySector = "Forest")%>%
#   mutate(AgSupplySubsector = LandLeaf)%>%
#   mutate(AgProductionTechnology = LandLeaf)  %>% 
#   dplyr::select(region, AgSupplySector,AgSupplySubsector,AgProductionTechnology,year)
# 
# 
# # expand the hist year to future 
# expanded_dataframe_forest <- L223_LN3_MgdAllocation_forest %>%
#    complete(year = seq(2020, 2100, 5), 
#            nesting(region,AgSupplySector, AgSupplySubsector, AgProductionTechnology))%>%
#   filter(year >= 2020) %>%
#    mutate(subregion = sub(".*_(.*)$", "\\1", AgSupplySubsector))
#  
# # fill AgProdChange with the GTM based FPC
# 
# # select needed col
# in_Sagb_long_needed_forest <- in_Sagb_long %>%
#   mutate(GCAM_subregion_ag_prodc = agb_scaler^(1/5) - 1)%>%
#   filter(landtype=="Forest")%>%
#   dplyr::select(region, subregion,year,landtype,GCAM_subregion_ag_prodc)
# 
# 
#   
# ## replace the FP with GTM's value
# L2052.AgProdChange_ag_forest_new <- expanded_dataframe_forest%>%
#   # join GTM csv with GCAM L2052.AgProdChange_ag_irr_ref by region name
#   left_join( in_Sagb_long_needed_forest %>%
#       mutate(year = as.integer(year)), by = c("region" , "subregion","year")) %>%
#   # mutate AgProdChange that same as the value in GCAM_5_year_productivity_change_percent
#   # add a range control, allow change from -2~2
#   mutate(AgProdChange = case_when(
#     GCAM_subregion_ag_prodc >= 2 ~ 2,
#     GCAM_subregion_ag_prodc < -2 ~ -2,
#     TRUE ~ GCAM_subregion_ag_prodc
#   ))%>%
#   # drop GCAM_5_year_productivity_change_percent
#   select(-GCAM_subregion_ag_prodc)%>%
#   select(region, AgSupplySector,AgSupplySubsector,AgProductionTechnology,year,AgProdChange)
# 
# 
# # save in GCAM 7.0 forest breakout version
# v7_FP_XML_file <- paste0(root,main_v7_XML_path,"ag_prodchange_forest_subregion_",as.character(XML_version),".xml")
# 
# create_xml(v7_FP_XML_file) %>%
#   add_xml_data(L2052.AgProdChange_ag_forest_new, "AgProdChange")->
#   ag_prodchange_MGMT_forest.xml
#     
# ag_prodchange_MGMT_forest.xml %>% gcamdata::run_xml_conversion()
#     
# # save in GCAM_para_update_to_GTMs       
# GTM_FP_XML_file <- paste0(root,main_my_XML_path,"ag_prodchange_forest_subregion_",as.character(XML_version),".xml")
#  
# create_xml(GTM_FP_XML_file) %>%
# add_xml_data(L2052.AgProdChange_ag_forest_new, "AgProdChange")->
#   ag_prodchange_MGMT_forest2.xml
#     
# ag_prodchange_MGMT_forest2.xml %>% gcamdata::run_xml_conversion()
#     
#    
# # save csv outputs
# # FP_CSV_file <-paste0(root,main_GTM_mid_xml_path,"ag_prodchange_",scenario,"_IRR_MGMT_all_forest_subregion_v7_GTM_",as.character(XML_version),".csv")
# # write.csv(L2052.AgProdChange_ag_irr_ref_new2,FP_CSV_file)
# 
# 
# 
# ##########################################################################################################################
# 
# ## pasture ###############################################################################################################
# 
# ##########################################################################################################################
# L222_LN2_MgdAllocation_file <-  paste0(root,main_GTM_mid_xml_path, "L222.LN2_MgdAllocation.csv")
# L222_LN2_MgdAllocation <- read.csv(L222_LN2_MgdAllocation_file, skip = 1)
# ############################################
# 
# # make new GCAM PFC template with all managed forest region
# L222_LN2_MgdAllocation_pasture <- L222_LN2_MgdAllocation %>%
#   mutate(AgSupplySector = str_extract(LandLeaf, "^[^_]+"))%>%
#   filter(AgSupplySector %in% c("Pasture") )%>%
#   mutate(AgSupplySubsector = LandLeaf)%>%
#   mutate(AgProductionTechnology = LandLeaf)  %>% 
#   dplyr::select(region, AgSupplySector,AgSupplySubsector,AgProductionTechnology,year)
# 
# # expand the hist year to future 
# expanded_dataframe_pasture <- L222_LN2_MgdAllocation_pasture %>%
#    complete(year = seq(2020, 2100, 5), 
#            nesting(region,AgSupplySector, AgSupplySubsector, AgProductionTechnology))%>%
#   filter(year >= 2020) %>%
#    mutate(subregion = sub(".*_(.*)$", "\\1", AgSupplySubsector))
#   
# # fill AgProdChange with the new data from ISIMIP
# 
# # select needed col
# in_Sagb_long_needed_pasture <- in_Sagb_long %>%
#   mutate(GCAM_subregion_ag_prodc = agb_scaler^(1/5) - 1)%>%
#   filter(landtype=="Pasture")%>%
#   dplyr::select(region, subregion,year,landtype,GCAM_subregion_ag_prodc)
# 
# 
# 
#   
# ## replace the FP with GTM's value
# L2052.AgProdChange_ag_pasture_new <- expanded_dataframe_pasture%>%
#   # join GTM csv with GCAM L2052.AgProdChange_ag_irr_ref by region name
#   left_join( in_Sagb_long_needed %>%
#       mutate(year = as.integer(year)), by = c("region" , "subregion","year")) %>%
#   # mutate AgProdChange that same as the value in GCAM_5_year_productivity_change_percent
#   # add a range control, allow change from -2~2
#   mutate(AgProdChange = case_when(
#     GCAM_subregion_ag_prodc >= 2 ~ 2,
#     GCAM_subregion_ag_prodc < -2 ~ -2,
#     TRUE ~ GCAM_subregion_ag_prodc
#   ))%>%
#   # drop GCAM_5_year_productivity_change_percent
#   select(-GCAM_subregion_ag_prodc)%>%
#   select(region, AgSupplySector,AgSupplySubsector,AgProductionTechnology,year,AgProdChange)
# 
# # save in GCAM 7.0
# v7_pasture_XML_file <- paste0(root,main_v7_XML_path,"ag_prodchange_pasture_subregion_",as.character(XML_version),".xml")
# 
# create_xml(v7_pasture_XML_file) %>%
#   add_xml_data(L2052.AgProdChange_ag_pasture_new, "AgProdChange")->
#   ag_prodchange_MGMT_pasture.xml
#     
# ag_prodchange_MGMT_pasture.xml %>% gcamdata::run_xml_conversion()
#     
# # save in GCAM_para_update_to_GTMs       
# GTM_pasture_XML_file <- paste0(root,main_my_XML_path,"ag_prodchange_pasture_subregion_",as.character(XML_version),".xml")
#  
# create_xml(GTM_pasture_XML_file) %>%
# add_xml_data(L2052.AgProdChange_ag_pasture_new, "AgProdChange")->
#   ag_prodchange_MGMT_pasture2.xml
#     
# ag_prodchange_MGMT_pasture2.xml %>% gcamdata::run_xml_conversion()
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
