---
title: "GTM_4_dim_var_process"
author: "Meng Luo"
date: "2023-08-29"
output: html_document
    toc: true
    toc_float: true
---
# use the mature age's FP as the input for GCAM


#########################################################
## update of the this version
# add FULL_matrix_for_MFP_continue

# Content
## link to github
  S0 link to github
## Setting Up
  S1 needed R package and dir
 
  
  
  
  
# link to github
```{r S0 link to github , include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
```

# Setting Up
## Loading Needed R Packages and Setting Directory

```{r S1 needed R package and dir }
library(tidyverse)
library(tidyr)
#install.packages("rlang")
library(rlang)
library(dplyr)
# devtools::install_github("JGCRI/gcamdata")
library(gcamdata)
library('drake')
library(patchwork)
library(ggplot2)
library(cowplot)


## run this in console devtools::load_all()


version_num <-"4"
case_name<-"_climate_productivityC"
#################################################################################################
## need to modify 
# plot_case<-1 # diff SSPs
plot_case<-1 # diff CC component
 
cases<-c("3SSPs")

case<-cases[plot_case]


## end of need to modify 
# read from hard disk ##############################################################
# # Chen lab desktop
# # root<-"O:/"
# 
# # 2023 laptop
# root<-"D:/"
# 
# 
# main_Sagb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_aboveCD/region_5ymean_alltypes_wrapper/")
# 
# 
# main_Sbgb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_belowCD/region_5ymean_alltypes_wrapper/")
# 
# 
# 
# XML_version <- paste0(version_num ,case_name,"_ssp",case) 

####

# main_GTM_mid_xml_path  <-"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/useful/"
# main_my_XML_path <- "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/new_XML/"
# # produce outputs in GCAM 7.0 release package 
# main_v7_XML_path <- "E/Docker_GCAM_v7_forest/gcam-master/input/gcamdata/xml/"
# 
# fig_save_path <- paste0(root,"E/new laptop2/PHD/my_2024_1_manuscript/Figure&table/figure/check_npp_rh_scaler_4in1_file/")

# Harmolandtype_area_main_path<-paste0(root,"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/")
# read from 2023 laptop  ##############################################################

# 2023 laptop
# root <- "C:/MengLuo/chapter 2_backup/"

# NAS
root <- "Z:/Meng/back_up_all/9_updates/"

########################################################################################
main_Sagb_path <- paste0(root, "climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_aboveCD/region_5ymean_alltypes_wrapper/")


main_Sbgb_path <- paste0(root, "climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_belowCD/region_5ymean_alltypes_wrapper/")

XML_version <- paste0(version_num ,case_name,"_ssp",case) 


#####

main_GTM_mid_xml_path  <-"climate_FPC_GCAM/Data/GCAM data system_forestversion/useful/"
main_my_XML_path <- "climate_FPC_GCAM/Data/GCAM data system_forestversion/new_XML/"
# produce outputs in GCAM 7.0 release package 
main_v7_XML_path <- "XML_save/"

fig_save_path <- paste0(root,"my_2024_1_manuscript/Figure&table/figure/check_npp_rh_scaler_4in1_file/")

Harmolandtype_area_main_path<-paste0(root,"climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/")

```


## read GTM output txt file
separate each var and save in csv

# function section


```{r S2 function save_result }
save_csv_result <- function(result_DF, result_csv_name,row_names) {

full_save_path <- paste0(root,main_GTM_path, result_csv_name)
if (row_names == TRUE) {
write.csv(result_DF,full_save_path, row.names = TRUE)
} else {
write.csv(result_DF,full_save_path, row.names = FALSE)
}

}
```

# preprocessing for GCAM XML
## I am right here


```{r S2 automatically read the file}

# agb_files <- list.files(path = main_Sagb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)
# 
# 
# bgb_files <- list.files(path = main_Sbgb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)
# 
# print(agb_files)
# print(bgb_files)
```

```{r S2_2 read the file}

forcing <- 1 # gfdl
# forcing <- 2 # ukesm


### diff SSPs
sub_case_names<-c("SSP126","SSP370","SSP585")

if (forcing == 1){
  
forcing_name<-"gfdl_"

## gfdl ####################################
agb_file_SSP126_gfdl <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp126_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP370_gfdl <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp370_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP585_gfdl <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")


bgb_file_SSP126_gfdl <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp126_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP370_gfdl <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp370_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP585_gfdl <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")

agb_files<-c(agb_file_SSP126_gfdl,agb_file_SSP370_gfdl,agb_file_SSP585_gfdl)
bgb_files<-c(bgb_file_SSP126_gfdl,bgb_file_SSP370_gfdl,bgb_file_SSP585_gfdl)
##############################
} else {
  
forcing_name<-"ukesm_"
  
agb_file_SSP126_ukesm <- paste0(main_Sagb_path, "classic_ukesm1-0-ll_w5e5_ssp126_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP370_ukesm <- paste0(main_Sagb_path, "classic_ukesm1-0-ll_w5e5_ssp370_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP585_ukesm <- paste0(main_Sagb_path, "classic_ukesm1-0-ll_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")


bgb_file_SSP126_ukesm <- paste0(main_Sbgb_path, "classic_ukesm1-0-ll_w5e5_ssp126_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP370_ukesm <- paste0(main_Sbgb_path, "classic_ukesm1-0-ll_w5e5_ssp370_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP585_ukesm <- paste0(main_Sbgb_path, "classic_ukesm1-0-ll_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")

agb_files<-c(agb_file_SSP126_ukesm,agb_file_SSP370_ukesm,agb_file_SSP585_ukesm)
bgb_files<-c(bgb_file_SSP126_ukesm,bgb_file_SSP370_ukesm,bgb_file_SSP585_ukesm)
}

```


```{r S3 read harmonized land type area in each subregion table }


in_forest_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_forest.csv"))%>%
  mutate(harm_type="Forest")
  
in_c3crop_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_c3crop.csv"))%>%
  mutate(harm_type="c3Crop")

in_c4crop_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_c4crop.csv"))%>%
  mutate(harm_type="c4Crop")

in_grass_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_grass.csv"))%>%
  mutate(harm_type="Grass")

in_Harmolandtype_area <-bind_rows(in_forest_area,in_c3crop_area,in_c4crop_area,in_grass_area)
  


```



```{r S4 plot and save agb scaler group map}



##########################
# Initialize an empty list to store plots
pagb_list <- list()
agbfignum <- c("(a)","(b)","(c)")
y_titles<-c("Agb Carbon Scalar","","")
ahjusts<-c(10,10.01,10.25)
# data_idx<-1
for (data_idx in c(1,2,3)) {
  
  
  in_Sagb_file <- agb_files[data_idx]
  in_Sagb <- read.csv(in_Sagb_file, check.names = FALSE)

  agb_file_name <- basename(in_Sagb_file)
  desired_name_part <- sub("_fullscaler.*", "", agb_file_name)

  check_belowCD_long <- in_Sagb %>%
    dplyr::select(-3, -2) %>%
    filter(harm_type != "Other") %>%
    left_join(in_Harmolandtype_area, by = c("out_reg_code", "out_lu_code", "harm_type")) %>%
    group_by(region, harm_type) %>%
    mutate(region_pft_area = sum(pft_area_total, na.rm = TRUE)) %>%
    mutate(region_pft_area_weight = pft_area_total / region_pft_area) %>%
    summarize(across(
      .cols = 6:22,
      .fns = ~ weighted.mean(.x, w = region_pft_area_weight, na.rm = TRUE)
    )) %>%
    ungroup() %>%
    pivot_longer(cols = 3:ncol(.),
                 names_to = "year",
                 values_to = "scaler") %>%
    mutate(year = as.numeric(year)) %>%
    na.omit()
  
  
  write.csv(check_belowCD_long,paste0(fig_save_path,"check_aboveCD_long_",agb_file_name,".csv"))
##############################  
  

# This way, you get both the weighted mean and standard deviation in your summarized output.
check_belowCD_long_gmean <- in_Sagb %>%
  dplyr::select(-3, -2) %>%
  filter(harm_type != "Other") %>%
  left_join(in_Harmolandtype_area, by = c("out_reg_code", "out_lu_code", "harm_type")) %>%
  group_by(harm_type) %>%
  mutate(global_pft_area = sum(pft_area_total, na.rm = TRUE)) %>%
  mutate(global_pft_area_weight = pft_area_total / global_pft_area) %>%
  summarize(across(
    .cols = 7:23,
    .fns = list(
      mean = ~ weighted.mean(.x, w = global_pft_area_weight, na.rm = TRUE),
      sd = ~ sqrt(weighted.mean((.x - weighted.mean(.x, w = global_pft_area_weight, na.rm = TRUE))^2, w = global_pft_area_weight, na.rm = TRUE))
    )
  )) %>%
  ungroup() %>%
  pivot_longer(cols = ends_with("_mean") | ends_with("_sd"),
               names_to = "year_stat",
               values_to = "value") %>%
  separate(year_stat, into = c("year", "stat"), sep = "_", convert = TRUE) %>%
  pivot_wider(names_from = stat, values_from = value) %>%
  mutate(year = as.numeric(year)) %>%
  select(harm_type, year, mean, sd)%>%
    # replace c3Crop with C3crop, c4Crop with C4crop
    mutate(harm_type = gsub("c3Crop", "C3crop", harm_type))%>%
    mutate(harm_type = gsub("c4Crop", "C4crop", harm_type))

  
  
  # write.csv(check_belowCD_long_gmean,"check_belowCD_long_gmean.csv")
  
  
  pagb_list[[data_idx]] <- ggplot(check_belowCD_long_gmean, aes(x = as.numeric(year), y = mean, group = harm_type, color = harm_type))+
    geom_ribbon(aes(ymin = mean - sd/2, ymax = mean + sd/2, fill = harm_type), color = NA, alpha = 0.2, show.legend = FALSE) +
    geom_line(aes(color = harm_type), size = 1, show.legend = FALSE) +
  labs(title = sub_case_names[data_idx],
       x = "",
       y = y_titles[data_idx],
       color = "Harmonized Types") +
  theme_minimal() +
  theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.text.x = element_blank(),  # Removes x-axis tick labels
        axis.ticks.x = element_blank()  # Removes x-axis ticks
        )   + ylim(c(0.82, 1.75))+
    annotate(
      "text",
      x = Inf,
      y = Inf,
      label = agbfignum[data_idx],
      hjust = ahjusts[data_idx],
      vjust = 1.5,
      size = 4
    )
  
 if (data_idx > 1) {
  pagb_list[[data_idx]] <- pagb_list[[data_idx]] +
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
}
 
}

p_global_legend <- ggplot(check_belowCD_long_gmean, aes(x = as.numeric(year), y = mean, group = harm_type, color = harm_type))+
    geom_ribbon(aes(ymin = mean - sd/2, ymax = mean + sd/2, fill = harm_type), color = NA, alpha = 0.2) +
    geom_line(aes(color = harm_type), size = 1) +
  labs(title = sub_case_names[data_idx],
       x = "",
       y = y_titles[data_idx],
       color = "Harmonized Types") +
  theme_minimal() +
  theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
        plot.title = element_text(hjust = 0.5))  +
  guides(color = guide_legend("Harmonized Types"), fill = guide_legend("Harmonized Types", override.aes = list(linetype = 1)))
  
  



global_legend <- cowplot::get_legend(p_global_legend)

combined_agb_plots <- wrap_plots(pagb_list, nrow = 1)



```

```{r S6 plot and save bgb scaler group map}



##########################
# Initialize an empty list to store plots
pbgb_list <- list()
y_titles<-c("Bgb Carbon Scalar","","")
 

bgbfignum <- c("(d)","(e)","(f)")
bhjusts<-c(10,10,12.7)

for (data_idx in c(1,2,3)) {
 
  
  in_Sbgb_file <- bgb_files[data_idx]
  in_Sbgb <- read.csv(in_Sbgb_file, check.names = FALSE)

  bgb_file_name <- basename(in_Sbgb_file)
  desired_name_part <- sub("_fullscaler.*", "", bgb_file_name)

  check_belowCD_long <- in_Sbgb %>%
    dplyr::select(-3, -2) %>%
    filter(harm_type != "Other") %>%
    left_join(in_Harmolandtype_area, by = c("out_reg_code", "out_lu_code", "harm_type")) %>%
    group_by(region, harm_type) %>%
    mutate(region_pft_area = sum(pft_area_total, na.rm = TRUE)) %>%
    mutate(region_pft_area_weight = pft_area_total / region_pft_area) %>%
    summarize(across(
      .cols = 6:22,
      .fns = ~ weighted.mean(.x, w = region_pft_area_weight, na.rm = TRUE)
    )) %>%
    ungroup() %>%
    pivot_longer(cols = 3:ncol(.),
                 names_to = "year",
                 values_to = "scaler") %>%
    mutate(year = as.numeric(year)) %>%
    na.omit()

  
  write.csv(check_belowCD_long,paste0(fig_save_path,"check_belowCD_long_",agb_file_name,".csv"))
  
  ######################
  check_belowCD_long_gmean <- in_Sbgb %>%
  dplyr::select(-3, -2) %>%
  filter(harm_type != "Other") %>%
  left_join(in_Harmolandtype_area, by = c("out_reg_code", "out_lu_code", "harm_type")) %>%
  group_by(harm_type) %>%
  mutate(global_pft_area = sum(pft_area_total, na.rm = TRUE)) %>%
  mutate(global_pft_area_weight = pft_area_total / global_pft_area) %>%
  summarize(across(
    .cols = 7:23,
    .fns = list(
      mean = ~ weighted.mean(.x, w = global_pft_area_weight, na.rm = TRUE),
      sd = ~ sqrt(weighted.mean((.x - weighted.mean(.x, w = global_pft_area_weight, na.rm = TRUE))^2, w = global_pft_area_weight, na.rm = TRUE))
    )
  )) %>%
  ungroup() %>%
  pivot_longer(cols = ends_with("_mean") | ends_with("_sd"),
               names_to = "year_stat",
               values_to = "value") %>%
  separate(year_stat, into = c("year", "stat"), sep = "_", convert = TRUE) %>%
  pivot_wider(names_from = stat, values_from = value) %>%
  mutate(year = as.numeric(year)) %>%
  select(harm_type, year, mean, sd)%>%
    # replace c3Crop with C3crop, c4Crop with C4crop
    mutate(harm_type = gsub("c3Crop", "C3crop", harm_type))%>%
    mutate(harm_type = gsub("c4Crop", "C4crop", harm_type))

  
  
  # write.csv(check_belowCD_long_gmean,"check_belowCD_long_gmean.csv")
  
  
  pbgb_list[[data_idx]] <- ggplot(check_belowCD_long_gmean, aes(x = as.numeric(year), y = mean, group = harm_type, color = harm_type))+
    geom_ribbon(aes(ymin = mean - sd/2, ymax = mean + sd/2, fill = harm_type), color = NA, alpha = 0.2, show.legend = FALSE) +
    geom_line(aes(color = harm_type), size = 1, show.legend = FALSE) +
  labs(title = NULL,
       x = "Year",
       y = y_titles[data_idx],
       color = "Harmonized Types") +
  theme_minimal() +
  theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
        plot.title = element_text(hjust = 0.5))  + ylim(c(0.87, 1.06)) +
    annotate(
      "text",
      x = Inf,
      y = Inf,
      label = bgbfignum[data_idx],
      hjust = bhjusts[data_idx],
      vjust = 1.5,
      size = 4
    )
  
  # Conditionally remove y-axis labels and ticks when data_idx > 1
if (data_idx > 1) {
  pbgb_list[[data_idx]] <- pbgb_list[[data_idx]] +
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
}
  
}


p_global_legend <- ggplot(check_belowCD_long_gmean, aes(x = as.numeric(year), y = mean, group = harm_type, color = harm_type))+
    geom_ribbon(aes(ymin = mean - sd/2, ymax = mean + sd/2, fill = harm_type), color = NA, alpha = 0.2) +
    geom_line(aes(color = harm_type), size = 1) +
  labs(title = sub_case_names[data_idx],
       x = "",
       y = y_titles[data_idx],
       color = "Harmonized Types") +
  theme_minimal() +
  theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
        plot.title = element_text(hjust = 0.5))  +
  guides(color = guide_legend("Harmonized Types"), fill = guide_legend("Harmonized Types", override.aes = list(linetype = 1)))

global_legend <- cowplot::get_legend(p_global_legend)

combined_bgb_plots <- wrap_plots(pbgb_list, nrow = 1)


```


```{r agb bgb global combined save}
agb_bgb_list<-c(pagb_list,pbgb_list)
combined_global_agbbgb_plots <- wrap_plots(agb_bgb_list, nrow = 2)  # Combine AGB plots into a single row


combined_global_agbbgb_plot <- plot_grid(
  combined_global_agbbgb_plots,  # Vertical stack of AGB and BGB plots
  global_legend,                 # Legend
  ncol = 2,                      # Two columns: one for plots, one for the legend
  rel_widths = c(1, 0.2)         # Relative widths, giving most space to the plots and less to the legend
)

ggsave(paste0(fig_save_path, "/Fig1_C_scalar_", case, "_Sagbbgb_global_",forcing_name,version_num,".svg"), plot = combined_global_agbbgb_plot, width = 18*0.5, height = 10*0.5, units = "in")
ggsave(paste0(fig_save_path, "/Fig1_C_scalar_", case, "_Sagbbgb_global_",forcing_name,version_num,".pdf"), plot = combined_global_agbbgb_plot, width = 18*0.5, height = 10*0.5, units = "in")
ggsave(paste0(fig_save_path, "/Fig1_C_scalar_", case, "_Sagbbgb_global_",forcing_name,version_num,".png"), plot = combined_global_agbbgb_plot, width = 18*0.5, height = 10*0.5, units = "in", dpi = 300)
ggsave(paste0(fig_save_path, "/Fig1_C_scalar_", case, "_Sagbbgb_global_",forcing_name,version_num,".tif"), plot = combined_global_agbbgb_plot, width = 18*0.5, height = 10*0.5, units = "in", device = "tiff", dpi = 300)


```

