---
title: "GTM_4_dim_var_process"
author: "Meng Luo"
date: "2023-08-29"
output: html_document
    toc: true
    toc_float: true
---
# use the mature age's FP as the input for GCAM


#########################################################
## update of the this version
# add FULL_matrix_for_MFP_continue

# Content
## link to github
  S0 link to github
## Setting Up
  S1 needed R package and dir
 
  
  
  
  
# link to github
```{r S0 link to github , include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
```

# Setting Up
## Loading Needed R Packages and Setting Directory

```{r S1 needed R package and dir }
#install.packages("drake")
library('drake')
#install.packages("cowplot")
library(cowplot)
############
require(devtools)
#Please use this in console if needed: install_github('JGCRI/rgcam', build_vignettes=TRUE, force =TRUE)
library (rgcam)
library(tidyverse)
library(tidyr)

library(rlang)
library(dplyr)
# install.packages("patchwork")
library(patchwork)
# install.packages("sf")
library(sf)
# install.packages("svglite")
library(svglite)
library(cowplot)
library(gridExtra)
library(ggthemes)
library(stringr)
library(ggplot2)
library(RColorBrewer)


## run this in console devtools::load_all()

Fig_num_name<-"Fig23_C_scalar"
version_num <-"7"
case_name<-"_climate_productivityC"
#################################################################################################
## need to modify 
# plot_case<-1 # diff SSPs


case<-"CC_components"


## end of need to modify 
# read from hard disk ##############################################################
# # Chen lab desktop
# # root<-"O:/"
# 
# # 2023 laptop
# root<-"D:/"
# 
# 
# main_Sagb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_aboveCD/region_5ymean_alltypes_wrapper/")
# 
# 
# main_Sbgb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_belowCD/region_5ymean_alltypes_wrapper/")
# 
# 
# 
# XML_version <- paste0(version_num ,case_name,"_ssp",case) 

####

# main_GTM_mid_xml_path  <-"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/useful/"
# main_my_XML_path <- "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/new_XML/"
# # produce outputs in GCAM 7.0 release package 
# main_v7_XML_path <- "E/Docker_GCAM_v7_forest/gcam-master/input/gcamdata/xml/"
# 
# fig_save_path <- paste0(root,"E/new laptop2/PHD/my_2024_1_manuscript/Figure&table/figure/check_npp_rh_scaler_4in1_file/")

# Harmolandtype_area_main_path<-paste0(root,"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/")
# read from 2023 laptop  ##############################################################

# 2023 laptop
# root <- "C:/MengLuo/chapter 2_backup/"

# NAS
root <- "Z:/Meng/back_up_all/9_updates/"

########################################################################################


main_Sagb_path <- paste0(root, "climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_aboveCD/region_5ymean_alltypes_wrapper/")


main_Sbgb_path <- paste0(root, "climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_belowCD/region_5ymean_alltypes_wrapper/")

XML_version <- paste0(version_num ,case_name,"_ssp",case) 


#####

main_GTM_mid_xml_path  <-"climate_FPC_GCAM/Data/GCAM data system_forestversion/useful/"
main_my_XML_path <- "climate_FPC_GCAM/Data/GCAM data system_forestversion/new_XML/"
# produce outputs in GCAM 7.0 release package 
main_v7_XML_path <- "XML_save/"

fig_save_path <- paste0(root,"my_2024_1_manuscript/Figure&table/figure/check_npp_rh_scaler_4in1_file/")

Harmolandtype_area_main_path<-paste0(root,"climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/")



shp_path <- paste0(root, "climate_FPC_GCAM/Code/boundary/gcam_boundaries_moirai_3p1_0p5arcmin_wgs84/gcam_boundaries_moirai_3p1_0p5arcmin_wgs84/main_outputs/region_boundaries_moirai_combined_3p1_0p5arcmin.shp")

data_sf <- st_read(shp_path)
```


## read GTM output txt file
separate each var and save in csv

# function section


```{r S2 function save_result }
save_csv_result <- function(result_DF, result_csv_name,row_names) {

full_save_path <- paste0(root,main_GTM_path, result_csv_name)
if (row_names == TRUE) {
write.csv(result_DF,full_save_path, row.names = TRUE)
} else {
write.csv(result_DF,full_save_path, row.names = FALSE)
}

}
```

# preprocessing for GCAM XML
## I am right here


```{r S3 automatically read the file}

# agb_files <- list.files(path = main_Sagb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)
# 
# 
# bgb_files <- list.files(path = main_Sbgb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)
# 
# print(agb_files)
# print(bgb_files)
```

```{r S4 read the file}


forcing_choice<-2

if (forcing_choice==1){
forcing<-"gfdl-esm4"
forcing_short<-"gfdl"
}else{

forcing<-"ukesm1-0-ll"
forcing_short<-"ukesm"
}


### diff CC component
sub_case_names<-c("CO2","N deposition","precipi and temp")
  
agb_file_SSP585_default <- paste0(main_Sagb_path, "classic_",forcing,"_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP585_2015co2 <- paste0(main_Sagb_path, "classic_",forcing,"_w5e5_ssp585_2015soc-from-histsoc_2015co2_fullscalerc3c4_agb_v3.csv")
agb_file_SSP585_ndep <- paste0(main_Sagb_path, "classic_",forcing,"_w5e5_ssp585_2015soc-from-histsoc_ssp585ndep_fullscalerc3c4_agb_v3.csv")


bgb_file_SSP585_default <- paste0(main_Sbgb_path, "classic_",forcing,"_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP585_2015co2 <- paste0(main_Sbgb_path, "classic_",forcing,"_w5e5_ssp585_2015soc-from-histsoc_2015co2_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP585_ndep <- paste0(main_Sbgb_path, "classic_",forcing,"_w5e5_ssp585_2015soc-from-histsoc_ssp585ndep_fullscalerc3c4_bgb_v3.csv")

agb_files<-c(agb_file_SSP585_default,agb_file_SSP585_2015co2,agb_file_SSP585_ndep)
bgb_files<-c(bgb_file_SSP585_default,bgb_file_SSP585_2015co2,bgb_file_SSP585_ndep)


```


```{r S5 read harmonized land type area in each subregion table }


in_forest_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_forest.csv"))%>%
  mutate(harm_type="Forest")
  
in_c3crop_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_c3crop.csv"))%>%
  mutate(harm_type="c3Crop")

in_c4crop_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_c4crop.csv"))%>%
  mutate(harm_type="c4Crop")

in_grass_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_grass.csv"))%>%
  mutate(harm_type="Grass")

in_Harmolandtype_area <-bind_rows(in_forest_area,in_c3crop_area,in_c4crop_area,in_grass_area)
  


```


```{r break label function}
## keep 3 decimal
generateQuantileLabels <- function(quantile_breaks) {
  sapply(1:(length(quantile_breaks) - 1), function(i) {
    paste(format(round(quantile_breaks[i], 3), nsmall = 3),
          "-",
          format(round(quantile_breaks[i + 1], 3), nsmall = 3),
          sep = "")
  })
}
## keep 2 decimal
generateQuantileLabels2 <- function(quantile_breaks) {
  sapply(1:(length(quantile_breaks) - 1), function(i) {
    paste(format(round(quantile_breaks[i], 2), nsmall = 2),
          "-",
          format(round(quantile_breaks[i + 1], 2), nsmall = 2),
          sep = "")
  })
}
## keep 1
generateQuantileLabels1 <- function(quantile_breaks) {
  sapply(1:(length(quantile_breaks) - 1), function(i) {
    paste(format(round(quantile_breaks[i], 1), nsmall = 1),
          "-",
          format(round(quantile_breaks[i + 1], 1), nsmall = 1),
          sep = "")
  })
}


## keep int
generateQuantileLabels_int <- function(quantile_breaks) {
  sapply(1:(length(quantile_breaks) - 1), function(i) {
    paste(format(round(quantile_breaks[i], 0)),
          "-",
          format(round(quantile_breaks[i + 1], 0)),
          sep = "")
  })
}

```

```{r S6 data_process_plot functions}
process_in_file <- function(data, harmolandtype_area) {
    # Read the CSV file
    # in_Sagb_co2->data
    # Process the data
    data %>%
      dplyr::select(-3) %>%
    filter(harm_type == "Forest") %>%
    group_by(child.nodes) %>%
    pivot_wider(names_from = "year",values_from = "scalar")%>%
    ungroup()%>%
    dplyr::select(-2) %>%
    left_join(in_Harmolandtype_area, by = c("out_reg_code", "out_lu_code", "harm_type")) %>%
      dplyr::select(-7, -6) %>%
      group_by(region, harm_type) %>%
      mutate(region_pft_area = sum(pft_area_total, na.rm = TRUE)) %>%
      mutate(region_pft_area_weight = pft_area_total / region_pft_area) %>%
      summarize(across(
        .cols = 4:20,
        .fns = ~ weighted.mean(.x, w = region_pft_area_weight, na.rm = TRUE)
      )) %>%
      ungroup() %>%
      pivot_longer(cols = 3:ncol(.),
                   names_to = "year",
                   values_to = "scalar") %>%
      mutate(year = as.numeric(year)) %>%
      na.omit()%>%
    pivot_wider(names_from = harm_type, values_from = scalar) %>%
    ungroup() %>%
  # rename(
  #   SSP1 = GCAM_SSP1,
  #   SSP2 = GCAM_SSP2,
  #   SSP3 = GCAM_SSP3,
  #   SSP4 = GCAM_SSP4,
  #   SSP5 = GCAM_SSP5
  # ) %>%
  left_join(data_sf, by = c("region" = "reg_nm"))
}
###########################################
# Function to create individual plots
create_plot <- function(data,y_var, harm_type, x_label = "", y_label = "", title, ylim_range = c(-0.4, 0.8)) {
  ggplot(data %>% filter(harm_type == harm_type), aes(x = as.numeric(year), y = !!sym(y_var),group = region, color = region)) +
    geom_line() +
    labs(title = title,
         x = x_label,
         y = y_label,
         color = "Region") +
    theme_minimal() +
    theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
          legend.position = "none",
          plot.title = element_text(hjust = 0.5)) +
    ylim(ylim_range)
}
###############################################
# Function to save the regional combined plots for each CC component
# Define plot size

save_combined_plot <- function(plot, name_suffix,wid_size=17*0.7,hei_size=10*0.7) {
  file_base <- paste0(fig_save_path, "/",Fig_num_name, "_combined_",forcing_short,"_", name_suffix, "_regions_v", version_num)
  
  ggsave(paste0(file_base, ".svg"), plot = plot, width = wid_size, height = hei_size, units = "in")
  ggsave(paste0(file_base, ".pdf"), plot = plot, width = wid_size, height = hei_size, units = "in")
  ggsave(paste0(file_base, ".png"), plot = plot, width = wid_size, height = hei_size, units = "in", dpi = 300)
  ggsave(filename = paste0(file_base, ".tif"), plot = plot, width = wid_size, height = hei_size, units = "in", device = "tiff", dpi = 300)
}

```

```{r S7 plot and save regional agb scaler group map}



##########################
# Initialize empty lists to store plots and processed data
pagb_list <- list()
check_belowCD_long_gmean_list <- list()

# For each dataset (this loop can be uncommented and used if needed)
# for (data_idx in c(1,2,3)) {
  y_titles <- c("Agb Carbon Scalars", "", "")
  

# Define file paths and process each agb file
in_Sagb_file_default <- agb_files[1]
in_Sagb_file_2015co2 <- agb_files[2]
in_Sagb_file_ndep <- agb_files[3]

in_Sagb_default1 <- read.csv(in_Sagb_file_default , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "default")
in_Sagb_2015co21 <- read.csv(in_Sagb_file_2015co2 , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "co22015")
in_Sagb_ndep1 <- read.csv(in_Sagb_file_ndep , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "ndep585")


in_Sagb_co2<-in_Sagb_default1%>%
  left_join(in_Sagb_2015co21, by=c("region","child.nodes","above.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = default-co22015)%>%
  dplyr::select(-c("default","co22015"))

in_Sagb_N_dep<-in_Sagb_default1%>%
  left_join(in_Sagb_ndep1, by=c("region","child.nodes","above.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ndep585-default)%>%
  dplyr::select(-c("default","ndep585"))

in_Sagb_tempperci<-in_Sagb_2015co21%>%
  mutate(scalar = co22015-1)%>%
  dplyr::select(-c("co22015"))





##################


check_aboveCD_long_co2 <- process_in_file(in_Sagb_co2, in_Harmolandtype_area) 

check_aboveCD_long_N_dep <- process_in_file(in_Sagb_N_dep, in_Harmolandtype_area) 

check_aboveCD_long_tempperci <- process_in_file(in_Sagb_tempperci, in_Harmolandtype_area) 




check_aboveCD_long_combine<-check_aboveCD_long_co2%>%
    rename(CO2=Forest)%>%
    left_join(check_aboveCD_long_N_dep%>%
    rename(N_dep=Forest), by = c("region","year","key","reg_id","geometry"))%>%
    left_join(check_aboveCD_long_tempperci%>%
    rename(tempperci=Forest), by = c("region","year","key","reg_id","geometry"))
  

########################

quantile_breaks_b <-
  quantile(
    c(check_aboveCD_long_combine$CO2, check_aboveCD_long_combine$N_dep, check_aboveCD_long_combine$tempperci
      # ,check_belowCD_long_combine$CO2, check_belowCD_long_combine$N_dep, check_belowCD_long_combine$tempperci
      ),
    probs = seq(0, 1, by = 1 / 7),
    na.rm = TRUE
  )

# quantile_breaks_b[1] <- -0.45
quantile_breaks_b[2] <- -0.2
quantile_breaks_b[3] <- -0.1
quantile_breaks_b[4] <- 0
quantile_breaks_b[5] <- 0.1
quantile_breaks_b[6] <- 0.2
quantile_breaks_b[7] <- 0.3

  
  quantile_labels_b <- generateQuantileLabels1(quantile_breaks_b)
quantile_labels_b[1] <- "<-0.2"

quantile_labels_b[7] <- ">0.3"
color_values_FP_b <-
  c("#feb24c",
    "#fed976",
    "#ffffb2",
    "#d9ef8b",
    "#a6d96a",
    "#66bd63",
    "#1a9850")
# reversed_color_values_b <- rev(color_values_FP_b)

assign_colors <- function(x, breaks, colors) {
  cut(x,
      breaks = breaks,
      include.lowest = TRUE,
      labels = FALSE) %>%
    {
      colors[.]
    }
}


assign_quantile_categories <- function(x, breaks) {
  cut(x,
      breaks = breaks,
      include.lowest = TRUE,
      labels = FALSE) %>%
    factor(levels = 1:length(breaks))
}
#################################################################################
#################################################################################
#################################################################################
#################################################################################
check_aboveCD_long_combine$quantile_cat_1 <-
  assign_quantile_categories(check_aboveCD_long_combine$CO2, quantile_breaks_b)
check_aboveCD_long_combine$quantile_cat_2 <-
  assign_quantile_categories(check_aboveCD_long_combine$N_dep, quantile_breaks_b)
check_aboveCD_long_combine$quantile_cat_3 <-
  assign_quantile_categories(check_aboveCD_long_combine$tempperci, quantile_breaks_b)









#################################################################################
# First, find the max and min for each of the SSP columns
C_max_values_b1 <-
  sapply(check_aboveCD_long_combine[c("CO2", "N_dep", "tempperci")], max, na.rm = TRUE)
C_min_values_b1 <-
  sapply(check_aboveCD_long_combine[c("CO2", "N_dep", "tempperci")], min, na.rm = TRUE)



# Now find the overall max and min across all the SSP columns
C_overall_max_b <- max(C_max_values_b1)
C_overall_min_b <- min(C_min_values_b1)

# Print the max and min for each column
print(C_overall_max_b)
print(C_overall_min_b)

# Print the overall max and min
print(paste("Overall Max:", C_overall_max_b))
print(paste("Overall Min:", C_overall_min_b))





  
   
  plot_C_scalar <- function(data, fill_col, Title,num_label,h_value,show_legend = FALSE,y_title = "",if_ytitle=FALSE,ifxlabel=FALSE) {
    
    # data<-check_belowCD_long
    # fill_col<-"quantile_cat_1"
    # Title<-"Forest"
    # num_label<-"a"
    # h_value<-21
    # show_legend <- TRUE
    
    
  
  x_ticks <- seq(-180, 180, by = 90)  # Longitude range from -180 to 180 with 60-degree increments
  y_ticks <- seq(-60, 85, by = 45)    # Latitude range from -90 to 90 with 30-degree increments

  x_labels <- paste0(x_ticks, "°E")  # Append "°E" to each x tick label
  y_labels <- paste0(y_ticks, "°N")  # Append "°N" to each y tick label
  
  
 # p1<- 
   p<-ggplot(data) +
    geom_sf(aes(geometry = geometry, fill = !!sym(fill_col)), color = "grey25") +
    scale_fill_manual(
      values = color_values_FP_b,
      name = expression("Carbon scalar difference"),
      # new add
      limits = c("1","2","3","4","5","6","7"),# make sure every legend level will be shown
      labels = quantile_labels_b
    ) +
    theme_base() +
    labs(
      y = y_title,
      x = '',
      title = paste0(Title)
    ) +
     scale_x_continuous(breaks = x_ticks, labels = x_labels) +
    scale_y_continuous(breaks = y_ticks, labels = y_labels) +
    theme(
      panel.grid = element_blank(),
      panel.background = element_rect(fill = "white", colour = NA),
      plot.background = element_rect(fill = "white", colour = NA),
      plot.title = element_text(hjust = 0.5, size = 15),
      axis.title.x = element_text(size = 15),
      axis.title.y = element_text(size = 15, face = "bold"),
      axis.text.x = element_text(size = 14.5),
      axis.text.y = element_text(size = 14.5),
      legend.text = element_text(size = 15),
      legend.title = element_text(size = 15),
      legend.position = ifelse(show_legend, "right", "none"),
      plot.margin = margin(t = 0, r = 0, b = 0, l = 0)
    ) +
    annotate(
      "text",
      x = Inf,
      y = Inf,
      label = paste0("(", num_label, ")"),
      hjust = h_value,
      vjust = 1.5,
      size = 4.5
    ) +
    guides(fill = guide_legend(keyheight = unit(1, "cm"), keywidth = unit(1, "cm"),        
                               reverse = TRUE  # Reverse the legend order
                               ))
   
   
   if (!if_ytitle) {
    p <- p +
      theme(axis.text.y = element_blank(),
            axis.ticks.y = element_blank())
  }

  if (ifxlabel) {p<-p
    
  }else if (ifxlabel == FALSE) {
  p <- p +
      theme(axis.text.x = element_blank(),
            axis.ticks.x = element_blank())}
   return(p)
  }
  ###############################################
  #CO2
  plot_C_scalar_CO2 <- function(data, fill_col, Title,num_label,h_value,show_legend = FALSE,y_title = "",if_ytitle=FALSE,ifxlabel=FALSE) {
    
    # data<-check_belowCD_long
    # fill_col<-"quantile_cat_1"
    # Title<-"Forest"
    # num_label<-"a"
    # h_value<-21
    # show_legend <- TRUE
    
    
  
  x_ticks <- seq(-180, 180, by = 90)  # Longitude range from -180 to 180 with 60-degree increments
  y_ticks <- seq(-60, 85, by = 45)    # Latitude range from -90 to 90 with 30-degree increments

  x_labels <- paste0(x_ticks, "°E")  # Append "°E" to each x tick label
  y_labels <- paste0(y_ticks, "°N")  # Append "°N" to each y tick label
  
  
 # p1<- 
   p<-ggplot(data) +
    geom_sf(aes(geometry = geometry, fill = !!sym(fill_col)), color = "grey25") +
    scale_fill_manual(
      values = color_values_FP_b,
      name = expression("Carbon scalar difference"),
      # new add
      limits = c("1","2","3","4","5","6","7"),# make sure every legend level will be shown
      labels = quantile_labels_b
    ) +
    theme_base() +
    labs(
      y = expression(bold(CO[2])),
      x = '',
      title = paste0(Title)
    ) +
     scale_x_continuous(breaks = x_ticks, labels = x_labels) +
    scale_y_continuous(breaks = y_ticks, labels = y_labels) +
    theme(
      panel.grid = element_blank(),
      panel.background = element_rect(fill = "white", colour = NA),
      plot.background = element_rect(fill = "white", colour = NA),
      plot.title = element_text(hjust = 0.5, size = 15),
      axis.title.x = element_text(size = 15),
      axis.title.y = element_text(size = 15, face = "bold"),
      axis.text.x = element_text(size = 14.5),
      axis.text.y = element_text(size = 14.5),
      legend.text = element_text(size = 15),
      legend.title = element_text(size = 15),
      legend.position = ifelse(show_legend, "right", "none"),
      plot.margin = margin(t = 0, r = 0, b = 0, l = 0)
    ) +
    annotate(
      "text",
      x = Inf,
      y = Inf,
      label = paste0("(", num_label, ")"),
      hjust = h_value,
      vjust = 1.5,
      size = 4.5
    ) +
    guides(fill = guide_legend(keyheight = unit(1, "cm"), keywidth = unit(1, "cm"),        
                               reverse = TRUE  # Reverse the legend order
                               ))
   
   
   if (!if_ytitle) {
    p <- p +
      theme(axis.text.y = element_blank(),
            axis.ticks.y = element_blank())
  }

  if (ifxlabel) {p<-p
    
  }else if (ifxlabel == FALSE) {
  p <- p +
      theme(axis.text.x = element_blank(),
            axis.ticks.x = element_blank())}
   return(p)
}

######################################################
  
  check_aboveCD_long_combine_2100<-check_aboveCD_long_combine%>%
    filter(year==2100)
write.csv( check_aboveCD_long_combine_2100,paste0(fig_save_path,"Fig23_check_aboveCD_long_combine",forcing_short,"_2100.csv"))

saveRDS(check_aboveCD_long_combine_2100, file = paste0(fig_save_path,"Fig23_check_aboveCD_long_combine",forcing_short,"_2100.rds"))

p_C_CO2 <- plot_C_scalar_CO2(check_aboveCD_long_combine%>%
    filter(year==2100),"quantile_cat_1", "Scalar difference","a",19.9*0.88,y_title= "CO2",if_ytitle=TRUE,ifxlabel=FALSE)+
  theme(
    legend.margin = margin(t = 0, r = 15, b = 0, l = 0)  # Adjust the values to increase/decrease margin
  )
p_C_tp <- plot_C_scalar(check_aboveCD_long_combine%>%
    filter(year==2100),"quantile_cat_3", "","c",20.9*0.88,y_title= "Climate change",,if_ytitle=TRUE,ifxlabel=FALSE)+
  theme(
    legend.margin = margin(t = 0, r = 15, b = 0, l = 0)   # Adjust the values to increase/decrease margin
  )
p_C_N <- plot_C_scalar(check_aboveCD_long_combine%>%
    filter(year==2100),"quantile_cat_2", "","e",19.9*0.88,y_title= "N deposition",if_ytitle=TRUE,ifxlabel=TRUE)+
  theme(
     legend.margin = margin(t = 0, r = 15, b = 0, l = 0)   # Adjust the values to increase/decrease margin
  )


P_C_legend <- plot_C_scalar(check_aboveCD_long_combine,"quantile_cat_3", "","e",19.9,y_title= "Temp & Prec",if_ytitle=TRUE,ifxlabel=TRUE,show_legend = TRUE)+
  theme(
    legend.margin = margin(10, 10, 10, 10),  # Adjust the values to increase/decrease margin
    legend.title = element_blank()
  # Adjust margin
    # legend.text = element_text(size = 6),  # Adjust legend text size
    # legend.title = element_text(size = 6),  # Adjust legend title size
    # legend.key.size = unit(0.1, "lines")  # Adjust legend key size
  )

##############################################################################################################
##############################################################################################################  
##############################################################################################################
 

legend <- cowplot::get_legend(P_C_legend)




 
```


```{r S8 plot and save regional bgb scaler group map}



##########################
# Initialize empty lists to store plots and processed data
pbgb_list <- list()
check_belowCD_long_gmean_list <- list()

# For each dataset (this loop can be uncommented and used if needed)
# for (data_idx in c(1,2,3)) {
  
  
  # Define file paths and process each agb file
in_Sbgb_file_default <- bgb_files[1]
in_Sbgb_file_2015co2 <- bgb_files[2]
in_Sbgb_file_ndep <- bgb_files[3]

in_Sbgb_default1 <- read.csv(in_Sbgb_file_default , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "default")
in_Sbgb_2015co21 <- read.csv(in_Sbgb_file_2015co2 , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "co22015")
in_Sbgb_ndep1 <- read.csv(in_Sbgb_file_ndep , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "ndep585")


in_Sbgb_co2<-in_Sbgb_default1%>%
  left_join(in_Sbgb_2015co21, by=c("region","child.nodes","below.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = default-co22015)%>%
  dplyr::select(-c("default","co22015"))

in_Sbgb_N_dep<-in_Sbgb_default1%>%
  left_join(in_Sbgb_ndep1, by=c("region","child.nodes","below.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ndep585-default)%>%
  dplyr::select(-c("default","ndep585"))

in_Sbgb_tempperci<-in_Sbgb_2015co21%>%
  mutate(scalar = co22015-1)%>%
  dplyr::select(-c("co22015"))





##################


check_belowCD_long_co2 <- process_in_file(in_Sbgb_co2, in_Harmolandtype_area) 

check_belowCD_long_N_dep <- process_in_file(in_Sbgb_N_dep, in_Harmolandtype_area) 

check_belowCD_long_tempperci <- process_in_file(in_Sbgb_tempperci, in_Harmolandtype_area) 




check_belowCD_long_combine<-check_belowCD_long_co2%>%
    rename(CO2=Forest)%>%
    left_join(check_belowCD_long_N_dep%>%
    rename(N_dep=Forest), by = c("region","year","key","reg_id","geometry"))%>%
    left_join(check_belowCD_long_tempperci%>%
    rename(tempperci=Forest), by = c("region","year","key","reg_id","geometry"))

########################


  check_belowCD_long_combine$quantile_cat_1 <-
  assign_quantile_categories(check_belowCD_long_combine$CO2, quantile_breaks_b)
check_belowCD_long_combine$quantile_cat_2 <-
  assign_quantile_categories(check_belowCD_long_combine$N_dep, quantile_breaks_b)
check_belowCD_long_combine$quantile_cat_3 <-
  assign_quantile_categories(check_belowCD_long_combine$tempperci, quantile_breaks_b)


 check_belowCD_long_combine_2100<-check_belowCD_long_combine%>%
    filter(year==2100)
write.csv( check_belowCD_long_combine_2100,paste0(fig_save_path,"Fig23_check_belowCD_long_combine",forcing_short,"2100.csv"))
  
saveRDS(check_belowCD_long_combine_2100, file = paste0(fig_save_path,"Fig23_check_belowCD_long_combine",forcing_short,"_2100.rds"))

p_bC_CO2 <- plot_C_scalar(check_belowCD_long_combine%>%
    filter(year==2100),"quantile_cat_1", "Scalar difference","b",19.9*0.88,if_ytitle=FALSE,ifxlabel=FALSE)#+
  # theme(
  #   legend.margin = margin(0, 15, 0, 0)  # Adjust the values to increase/decrease margin
  # )
p_bC_tp <- plot_C_scalar(check_belowCD_long_combine%>%
    filter(year==2100),"quantile_cat_3", "","d",19.9*0.88,if_ytitle=FALSE,ifxlabel=FALSE)#+
  # theme(
  #   legend.margin = margin(0, 15, 0, 0)  # Adjust the values to increase/decrease margin
  # )
p_bC_N <- plot_C_scalar(check_belowCD_long_combine%>%
    filter(year==2100),"quantile_cat_2", "","f",25.9*0.88,if_ytitle=FALSE,ifxlabel=TRUE)#+
  # theme(
  #   legend.margin = margin(0, 15, 0, 0)  # Adjust the values to increase/decrease margin
  # )


  
  



```

```{r save plot}


combined_agb_plots <- wrap_plots(p_C_CO2,p_C_tp,p_C_N, nrow = 3)
combined_bgb_plots <- wrap_plots(p_bC_CO2,p_bC_tp,p_bC_N, nrow = 3)
# combined_agbbgb_plots <- wrap_plots(p_C_126,p_bC_126,p_C_370,p_bC_370,p_C_585,p_bC_585, nrow = 3)
##############################################
combined_global_bgb_plot <- plot_grid(
  combined_agb_plots, 
  combined_bgb_plots,
  legend,                 # Legend
  ncol = 3,                      # Two columns: one for plots, one for the legend
  rel_widths = c(0.7,0.61, 0.4)         # Relative widths, giving most space to the plots and less to the legend
)


 ggsave(paste0(fig_save_path, "/Fig23_CC_components_Sagb_bgb_spatial_",forcing_short,"_v",version_num,".svg"), plot = combined_global_bgb_plot , width = 15*0.81, height = 9*0.81, units = "in")


ggsave(paste0(fig_save_path, "/Fig23_CC_components_Sagb_bgb_spatial_",forcing_short,"_v",version_num,".pdf"), plot = combined_global_bgb_plot, width = 15*0.81, height = 9*0.81, units = "in")
ggsave(paste0(fig_save_path, "/Fig23_CC_components_Sagb_bgb_spatial_",forcing_short,"_v",version_num,".png"), plot = combined_global_bgb_plot, width = 15*0.81, height = 9*0.81, units = "in", dpi = 300)
ggsave(filename = paste0(fig_save_path,"/Fig23_CC_components_Sagb_bgb_spatial_",forcing_short,"_v", version_num, ".tif"),
     plot = combined_global_bgb_plot,
     width = 15*0.81,
     height = 9*0.81,
     units = "in",
     device = "tiff",
     dpi = 300)




```






