---
title: "GTM_4_dim_var_process"
author: "Meng Luo"
date: "2023-08-29"
output: html_document
    toc: true
    toc_float: true
---
# use the mature age's FP as the input for GCAM


#########################################################
## update of the this version
# add FULL_matrix_for_MFP_continue

# Content
## link to github
  S0 link to github
## Setting Up
  S1 needed R package and dir
 
  
  
  
  
# link to github
```{r S0 link to github , include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
```

# Setting Up
## Loading Needed R Packages and Setting Directory

```{r S1 needed R package and dir }
library(tidyverse)
library(tidyr)
#install.packages("rlang")
library(rlang)
library(dplyr)
library(gcamdata)
library('drake')
library(patchwork)
library(ggplot2)
library(cowplot)


## run this in console devtools::load_all()

Fig_num_name<-"Fig21_C_scalar"
version_num <-"7"
case_name<-"_climate_productivityC"
#################################################################################################
## need to modify 
# plot_case<-1 # diff SSPs
plot_case<-1 # diff CC component
 
cases<-c("3SSPs")

case<-cases[plot_case]


## end of need to modify 
# read from hard disk ##############################################################
# # Chen lab desktop
# # root<-"O:/"
# 
# # 2023 laptop
# root<-"D:/"
# 
# 
# main_Sagb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_aboveCD/region_5ymean_alltypes_wrapper/")
# 
# 
# main_Sbgb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_belowCD/region_5ymean_alltypes_wrapper/")
# 
# 
# 
# XML_version <- paste0(version_num ,case_name,"_ssp",case) 

####

# main_GTM_mid_xml_path  <-"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/useful/"
# main_my_XML_path <- "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/new_XML/"
# # produce outputs in GCAM 7.0 release package 
# main_v7_XML_path <- "E/Docker_GCAM_v7_forest/gcam-master/input/gcamdata/xml/"
# 
# fig_save_path <- paste0(root,"E/new laptop2/PHD/my_2024_1_manuscript/Figure&table/figure/check_npp_rh_scaler_4in1_file/")

# Harmolandtype_area_main_path<-paste0(root,"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/")
# read from 2023 laptop  ##############################################################

# 2023 laptop
# root <- "C:/MengLuo/chapter 2_backup/"

# NAS
root <- "Z:/Meng/back_up_all/9_updates/"

main_Sagb_path <- paste0(root, "climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_aboveCD/region_5ymean_alltypes_wrapper/")


main_Sbgb_path <- paste0(root, "climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_belowCD/region_5ymean_alltypes_wrapper/")

XML_version <- paste0(version_num ,case_name,"_ssp",case) 


#####

main_GTM_mid_xml_path  <-"climate_FPC_GCAM/Data/GCAM data system_forestversion/useful/"
main_my_XML_path <- "climate_FPC_GCAM/Data/GCAM data system_forestversion/new_XML/"
# produce outputs in GCAM 7.0 release package 
main_v7_XML_path <- "XML_save/"

fig_save_path <- paste0(root,"my_2024_1_manuscript/Figure&table/figure/check_npp_rh_scaler_4in1_file/")

Harmolandtype_area_main_path<-paste0(root,"climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/")

```


## read GTM output txt file
separate each var and save in csv

# function section


```{r S2 function save_result }
save_csv_result <- function(result_DF, result_csv_name,row_names) {

full_save_path <- paste0(root,main_GTM_path, result_csv_name)
if (row_names == TRUE) {
write.csv(result_DF,full_save_path, row.names = TRUE)
} else {
write.csv(result_DF,full_save_path, row.names = FALSE)
}

}
```

# preprocessing for GCAM XML
## I am right here


```{r S2 automatically read the file}

# agb_files <- list.files(path = main_Sagb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)
# 
# 
# bgb_files <- list.files(path = main_Sbgb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)
# 
# print(agb_files)
# print(bgb_files)
```

```{r S3 read harmonized land type area in each subregion table }


in_forest_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_forest.csv"))%>%
  mutate(harm_type="Forest")
  
in_c3crop_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_c3crop.csv"))%>%
  mutate(harm_type="c3Crop")

in_c4crop_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_c4crop.csv"))%>%
  mutate(harm_type="c4Crop")

in_grass_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_grass.csv"))%>%
  mutate(harm_type="Grass")

in_Harmolandtype_area <-bind_rows(in_forest_area,in_c3crop_area,in_c4crop_area,in_grass_area)
  


```

```{r S4 read the file}

### diff SSPs
sub_case_names<-c("SSP126","SSP370","SSP585")


agb_file_SSP126_gfdl <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp126_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP370_gfdl <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp370_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP585_gfdl <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
## ukesm
agb_file_SSP126_ukesm <- paste0(main_Sagb_path, "classic_ukesm1-0-ll_w5e5_ssp126_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP370_ukesm <- paste0(main_Sagb_path, "classic_ukesm1-0-ll_w5e5_ssp370_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP585_ukesm <- paste0(main_Sagb_path, "classic_ukesm1-0-ll_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")


bgb_file_SSP126_gfdl <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp126_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP370_gfdl <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp370_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP585_gfdl <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
## ukesm
bgb_file_SSP126_ukesm <- paste0(main_Sbgb_path, "classic_ukesm1-0-ll_w5e5_ssp126_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP370_ukesm <- paste0(main_Sbgb_path, "classic_ukesm1-0-ll_w5e5_ssp370_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP585_ukesm <- paste0(main_Sbgb_path, "classic_ukesm1-0-ll_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")

agb_files_gfdl<-c(agb_file_SSP126_gfdl,agb_file_SSP370_gfdl,agb_file_SSP585_gfdl)
agb_files_ukesm<-c(agb_file_SSP126_ukesm,agb_file_SSP370_ukesm,agb_file_SSP585_ukesm)

bgb_files_gfdl<-c(bgb_file_SSP126_gfdl,bgb_file_SSP370_gfdl,bgb_file_SSP585_gfdl)
bgb_files_ukesm<-c(bgb_file_SSP126_ukesm,bgb_file_SSP370_ukesm,bgb_file_SSP585_ukesm)
##############################

```

```{r S functions}

##########################

save_combined_plot <- function(plot, name_suffix,wid_size=15,hei_size=10) {
  file_base <- paste0(fig_save_path, "/",Fig_num_name, "_combined_", name_suffix, "_v", version_num)
  
  ggsave(paste0(file_base, ".svg"), plot = plot, width = wid_size, height = hei_size, units = "in")
  ggsave(paste0(file_base, ".pdf"), plot = plot, width = wid_size, height = hei_size, units = "in")
  ggsave(paste0(file_base, ".png"), plot = plot, width = wid_size, height = hei_size, units = "in", dpi = 300)
  ggsave(filename = paste0(file_base, ".tif"), plot = plot, width = wid_size, height = hei_size, units = "in", device = "tiff", dpi = 300)
}
#########################
scenario_colors <- c("SSP126" = "#4daf4a", "SSP370" = "#377eb8", "SSP585" = "#e41a1c")

create_global_plot <- function(data,
                               y_var_m,
                               y_var_sd,
                               ylimits = c(0.82, 1.75),
                               if_title,
                               t_title,
                               if_xtitle = FALSE,
                               x_title,
                               if_ytitle = FALSE,
                               y_title,
                               ifxlabel = TRUE,
                               lab,
                               hj = 10,
                               scenario_colors = NULL) {
  
  
  


  # data <- check_aboveCD_long_gmean_combined
  # y_var_m <- "mean"
  # y_var_sd <- "sd"
  # ylimits <- c(0.82, 1.75)
  # if_title <- FALSE
  # t_title <- "AGB Carbon scalar"
  # if_xtitle <- TRUE
  # x_title <- "Year"
  # if_ytitle <- TRUE
  # y_title <- "Agb Carbon scalar"
  # ifxlabel <- FALSE
  # lab <- "(a)"
  # hj <- 10
  # scenario_colors <- NULL
  
  
  
  # Default color palette if none provided
  if (is.null(scenario_colors)) {
    # scenario_colors <- c("SSP126" = "#009E73", "SSP370" = "#D55E00", "SSP585" = "#0072B2") ##984ea3
    scenario_colors <- c("SSP126" = "#4daf4a", "SSP370" = "#377eb8", "SSP585" = "#e41a1c") ##984ea3
  }
  
  p <- ggplot(data, aes(x = as.numeric(year), y = !!sym(y_var_m), group = scenario)) +
    geom_ribbon(aes(ymin = !!sym(y_var_m) - !!sym(y_var_sd) / 2, 
                    ymax = !!sym(y_var_m) + !!sym(y_var_sd) / 2, 
                    fill = scenario), color = NA, alpha = 0.2, show.legend = FALSE) +
    geom_line(aes(color = scenario), size = 1, show.legend = FALSE) +
    scale_color_manual(values = scenario_colors) +
    scale_fill_manual(values = scenario_colors) +
    labs(title = if (if_title) t_title else NULL,
         x = if (if_xtitle) x_title else NULL,
         y = if (if_ytitle) y_title else NULL,
         color = "Scenarios") +
    theme_minimal() +
    theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
          legend.position = "none",
          plot.title = element_text(hjust = 0.5, face = "bold")) +
    ylim(ylimits) +
    annotate("text",
             x = Inf,
             y = Inf,
             label = lab,
             hjust = hj,
             vjust = 1.5,
             size = 4)

  if (!if_ytitle) {
    p <- p +
      theme(axis.text.y = element_blank(),
            axis.ticks.y = element_blank())
  }

  if (ifxlabel) {p<-p
    
  }else if (ifxlabel == FALSE) {
  p <- p +
      theme(axis.text.x = element_blank(),
            axis.ticks.x = element_blank())}
  
  return(p)
}


############################



 # Function to process agb files
process_global_file <- function(data, harmolandtype_area) {
  
    data %>%
    dplyr::select(-3) %>%
    filter(harm_type == "Forest") %>%
    group_by(child.nodes) %>%
    pivot_wider(names_from = "year",values_from = "scalar")%>%
    ungroup()%>%
    dplyr::select(-2) %>%
    left_join(in_Harmolandtype_area, by = c("out_reg_code", "out_lu_code", "harm_type")) %>%
    group_by(harm_type) %>%
    mutate(global_pft_area = sum(pft_area_total, na.rm = TRUE)) %>%
    mutate(global_pft_area_weight = pft_area_total / global_pft_area) %>%
    summarize(across(
    .cols = 7:23,
    .fns = list(
      mean = ~ weighted.mean(.x, w = global_pft_area_weight, na.rm = TRUE),
      sd = ~ sqrt(weighted.mean((.x - weighted.mean(.x, w = global_pft_area_weight, na.rm = TRUE))^2, w = global_pft_area_weight, na.rm = TRUE))
    )
  )) %>%
  ungroup() %>%
  pivot_longer(cols = ends_with("_mean") | ends_with("_sd"),
               names_to = "year_stat",
               values_to = "value") %>%
  separate(year_stat, into = c("year", "stat"), sep = "_", convert = TRUE) %>%
  pivot_wider(names_from = stat, values_from = value) %>%
  mutate(year = as.numeric(year)) %>%
  dplyr::select(harm_type, year, mean, sd) %>%
    na.omit()
}
```




```{r S5 plot and save agb scaler group map}



##########################
# Initialize an empty list to store plots
pagb_list <- list()




 in_Sagb_file_gfdl1 <- agb_files_gfdl[1]
  in_Sagb_file_gfdl2 <- agb_files_gfdl[2]
  in_Sagb_file_gfdl3 <- agb_files_gfdl[3]
  
  in_Sagb_file_ukesm1 <- agb_files_ukesm[1]
  in_Sagb_file_ukesm2 <- agb_files_ukesm[2]
  in_Sagb_file_ukesm3 <- agb_files_ukesm[3]
  
    ###########################################
  
  
  # Process each dataset using the function
  
  in_Sagb_gfdl1<-read.csv(in_Sagb_file_gfdl1 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "gfdl")
  
  in_Sagb_gfdl2<-read.csv(in_Sagb_file_gfdl2 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "gfdl")
  
  in_Sagb_gfdl3<-read.csv(in_Sagb_file_gfdl3 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "gfdl")
  
  in_Sagb_ukesm3<-read.csv(in_Sagb_file_ukesm3 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "ukesm")
  
  in_Sagb_ukesm2<-read.csv(in_Sagb_file_ukesm2 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "ukesm")
  
  in_Sagb_ukesm1<-read.csv(in_Sagb_file_ukesm1 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "ukesm")
  
  aboveCD_foring_diff1<-in_Sagb_gfdl1%>%
  left_join(in_Sagb_ukesm1, by=c("region","child.nodes","above.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ukesm-gfdl)%>%
  dplyr::select(-c("gfdl","ukesm"))
  
  aboveCD_foring_diff2<-in_Sagb_gfdl2%>%
  left_join(in_Sagb_ukesm2, by=c("region","child.nodes","above.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ukesm-gfdl)%>%
  dplyr::select(-c("gfdl","ukesm"))
  
  aboveCD_foring_diff3<-in_Sagb_gfdl3%>%
  left_join(in_Sagb_ukesm3, by=c("region","child.nodes","above.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ukesm-gfdl)%>%
  dplyr::select(-c("gfdl","ukesm"))
  
  
  
  
   check_aboveCD_foring_diff1 <-
    process_global_file( aboveCD_foring_diff1, in_Harmolandtype_area)
   
   check_aboveCD_foring_diff2 <-
    process_global_file( aboveCD_foring_diff2, in_Harmolandtype_area)
   
   check_aboveCD_foring_diff3 <-
    process_global_file( aboveCD_foring_diff3, in_Harmolandtype_area)
   
   
    check_aboveCD_foring_diff1 <- rbind(check_aboveCD_foring_diff1, data.frame(harm_type = "Forest", year = 2015, mean = 0, sd = 0))
check_aboveCD_foring_diff2 <- rbind(check_aboveCD_foring_diff2, data.frame(harm_type = "Forest", year = 2015, mean = 0, sd = 0))
check_aboveCD_foring_diff3 <- rbind(check_aboveCD_foring_diff3, data.frame(harm_type = "Forest", year = 2015, mean = 0, sd = 0))

   
   
   check_aboveCD_long_gmean_combined <- check_aboveCD_foring_diff1 %>%
  mutate(scenario = "SSP126") %>%
  rbind(check_aboveCD_foring_diff2 %>%
          mutate(scenario = "SSP370")) %>%
  rbind(check_aboveCD_foring_diff3 %>%
          mutate(scenario = "SSP585"))
   
   
     
write.csv( check_aboveCD_long_gmean_combined,paste0(fig_save_path,"Fig21_check_aboveCD_long_gmean_combined.csv"))

check_aboveCD_long_gmean_combined_2100<-check_aboveCD_long_gmean_combined%>%
    filter(year==2100)


#############
pagb <- create_global_plot(
  check_aboveCD_long_gmean_combined,
  y_var_m = "mean",
  y_var_sd = "sd",
  ylimits = c(-0.26, 0.20),
  if_title = FALSE,
  t_title = "AGC scalar",
  if_xtitle = TRUE,
  x_title = "Year",
  if_ytitle = TRUE,
  y_title = "Vegetation carbon scalar difference",
  ifxlabel = TRUE,
  lab = "(a)",
  hj = 16.6)




p_global_legend <- ggplot(
  check_aboveCD_long_gmean_combined,
  aes(
    x = as.numeric(year),
    y = mean,
    group = scenario,
    color = scenario
  )
) +
  geom_ribbon(
    aes(
      ymin = mean - sd / 2,
      ymax = mean + sd / 2,
      fill = scenario
    ),
    color = NA,
    alpha = 0.2
  ) +
  geom_line(aes(color = scenario), size = 1) +
  scale_color_manual(values = scenario_colors) +
  scale_fill_manual(values = scenario_colors) +
  labs(
    title = "",
    x = "",
    y = "",
    color = "Scenario"
  ) +
  theme_minimal() +
  theme(
    panel.border = element_rect(
      color = "black",
      fill = NA,
      size = 1
    ),
    plot.title = element_text(hjust = 0.5)
  )  +
  guides(color = guide_legend("Scenario"),
         fill = guide_legend("Scenario", override.aes = list(linetype = 1)))





global_legend <- cowplot::get_legend(p_global_legend)


```

```{r S6 plot and save bgb scaler group map}



##########################
# Initialize an empty list to store plots
pbgb_list <- list()

  in_Sbgb_file_gfdl1 <- bgb_files_gfdl[1]
  in_Sbgb_file_gfdl2 <- bgb_files_gfdl[2]
  in_Sbgb_file_gfdl3 <- bgb_files_gfdl[3]
  
  in_Sbgb_file_ukesm1 <- bgb_files_ukesm[1]
  in_Sbgb_file_ukesm2 <- bgb_files_ukesm[2]
  in_Sbgb_file_ukesm3 <- bgb_files_ukesm[3]
  
    ###########################################
  
  
  # Process each dataset using the function
  
  in_Sbgb_gfdl1<-read.csv(in_Sbgb_file_gfdl1 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "gfdl")
  
  in_Sbgb_gfdl2<-read.csv(in_Sbgb_file_gfdl2 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "gfdl")
  
  in_Sbgb_gfdl3<-read.csv(in_Sbgb_file_gfdl3 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "gfdl")
  
  in_Sbgb_ukesm3<-read.csv(in_Sbgb_file_ukesm3 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "ukesm")
  
  in_Sbgb_ukesm2<-read.csv(in_Sbgb_file_ukesm2 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "ukesm")
  
  in_Sbgb_ukesm1<-read.csv(in_Sbgb_file_ukesm1 , check.names = FALSE)%>%
    pivot_longer(cols = 10:26,names_to = "year",values_to = "ukesm")
  
  belowCD_foring_diff1<-in_Sbgb_gfdl1%>%
  left_join(in_Sbgb_ukesm1, by=c("region","child.nodes","below.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ukesm-gfdl)%>%
  dplyr::select(-c("gfdl","ukesm"))
  
  belowCD_foring_diff2<-in_Sbgb_gfdl2%>%
  left_join(in_Sbgb_ukesm2, by=c("region","child.nodes","below.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ukesm-gfdl)%>%
  dplyr::select(-c("gfdl","ukesm"))
  
  belowCD_foring_diff3<-in_Sbgb_gfdl3%>%
  left_join(in_Sbgb_ukesm3, by=c("region","child.nodes","below.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ukesm-gfdl)%>%
  dplyr::select(-c("gfdl","ukesm"))
  
  
  
  
   check_belowCD_foring_diff1 <-
    process_global_file( belowCD_foring_diff1, in_Harmolandtype_area)
   
   check_belowCD_foring_diff2 <-
    process_global_file( belowCD_foring_diff2, in_Harmolandtype_area)
   
   check_belowCD_foring_diff3 <-
    process_global_file( belowCD_foring_diff3, in_Harmolandtype_area)
   
   
   check_belowCD_foring_diff1 <- rbind(check_belowCD_foring_diff1, data.frame(harm_type = "Forest", year = 2015, mean = 0, sd = 0))
check_belowCD_foring_diff2 <- rbind(check_belowCD_foring_diff2, data.frame(harm_type = "Forest", year = 2015, mean = 0, sd = 0))
check_belowCD_foring_diff3 <- rbind(check_belowCD_foring_diff3, data.frame(harm_type = "Forest", year = 2015, mean = 0, sd = 0))


   
   check_belowCD_long_gmean_combined <- check_belowCD_foring_diff1 %>%
  mutate(scenario = "SSP126") %>%
  rbind(check_belowCD_foring_diff2 %>%
          mutate(scenario = "SSP370")) %>%
  rbind(check_belowCD_foring_diff3 %>%
          mutate(scenario = "SSP585"))
   
   write.csv( check_belowCD_long_gmean_combined,paste0(fig_save_path,"Fig21_check_belowCD_long_gmean_combined.csv"))

check_belowCD_long_gmean_combined_2100<-check_belowCD_long_gmean_combined%>%
    filter(year==2100)


#############
pbgb <- create_global_plot(
  check_belowCD_long_gmean_combined,
  y_var_m = "mean",
  y_var_sd = "sd",
  ylimits = c(-0.13, 0.07),
  if_title = FALSE,
  t_title = "BGC scalar",
  if_xtitle = TRUE,
  x_title = "Year",
  if_ytitle = TRUE,
  y_title = "Soil carbon scalar difference",
  ifxlabel = TRUE,
  lab = "(b)",
  hj = 16.3)
 


```
######

```{r agb bgb global combined save}


combined_global_agbbgb_plot <- plot_grid(
  pagb,pbgb,  # Vertical stack of AGB and BGB plots
  global_legend,                 # Legend
  ncol = 3,                      # Two columns: one for plots, one for the legend
  rel_widths = c(1,1, 0.2)            # Relative widths, giving most space to the plots and less to the legend
)


 save_combined_plot(combined_global_agbbgb_plot, "Sagbbgb_global_3SSPs_forcing",wid_size=18*0.5,hei_size=10*0.5)
 
```
