---
title: "GTM_4_dim_var_process"
author: "Meng Luo"
date: "2023-08-29"
output: html_document
    toc: true
    toc_float: true
---
# use the mature age's FP as the input for GCAM


#########################################################
## update of the this version
# add FULL_matrix_for_MFP_continue

# Content
## link to github
  S0 link to github
## Setting Up
  S1 needed R package and dir
 
  
  
  
  
# link to github
```{r S0 link to github , include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
```

# Setting Up
## Loading Needed R Packages and Setting Directory

```{r S1 needed R package and dir }
library(tidyverse)
library(tidyr)
#install.packages("rlang")
library(rlang)
library(dplyr)
library(gcamdata)
library('drake')
library(patchwork)
library(ggplot2)
library(cowplot)


## run this in console devtools::load_all()

Fig_num_name<-"Fig2_C_scalar"
version_num <-"4"
case_name<-"_climate_productivityC"
#################################################################################################
## need to modify 
# plot_case<-1 # diff SSPs
plot_case<-2 # diff CC component
 
cases<-c("3SSPs","CC_components")

case<-cases[plot_case]


## end of need to modify 
# read from hard disk ##############################################################
# # Chen lab desktop
# # root<-"O:/"
# 
# # 2023 laptop
# root<-"D:/"
# 
# 
# main_Sagb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_aboveCD/region_5ymean_alltypes_wrapper/")
# 
# 
# main_Sbgb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_belowCD/region_5ymean_alltypes_wrapper/")
# 
# 
# 
# XML_version <- paste0(version_num ,case_name,"_ssp",case) 

####

# main_GTM_mid_xml_path  <-"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/useful/"
# main_my_XML_path <- "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/new_XML/"
# # produce outputs in GCAM 7.0 release package 
# main_v7_XML_path <- "E/Docker_GCAM_v7_forest/gcam-master/input/gcamdata/xml/"
# 
# fig_save_path <- paste0(root,"E/new laptop2/PHD/my_2024_1_manuscript/Figure&table/figure/check_npp_rh_scaler_4in1_file/")

# Harmolandtype_area_main_path<-paste0(root,"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/")
# read from 2023 laptop  ##############################################################

# 2023 laptop
# root <- "C:/MengLuo/chapter 2_backup/"

# NAS
root <- "Z:/Meng/back_up_all/9_updates/"


main_Sagb_path <- paste0(root, "climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_aboveCD/region_5ymean_alltypes_wrapper/")


main_Sbgb_path <- paste0(root, "climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_belowCD/region_5ymean_alltypes_wrapper/")

XML_version <- paste0(version_num ,case_name,"_ssp",case) 


#####

main_GTM_mid_xml_path  <-"climate_FPC_GCAM/Data/GCAM data system_forestversion/useful/"
main_my_XML_path <- "climate_FPC_GCAM/Data/GCAM data system_forestversion/new_XML/"
# produce outputs in GCAM 7.0 release package 
main_v7_XML_path <- "XML_save/"

fig_save_path <- paste0(root,"my_2024_1_manuscript/Figure&table/figure/check_npp_rh_scaler_4in1_file/")

Harmolandtype_area_main_path<-paste0(root,"climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/")

```


## read GTM output txt file
separate each var and save in csv

# function section


```{r S2 function save_result }
save_csv_result <- function(result_DF, result_csv_name,row_names) {

full_save_path <- paste0(root,main_GTM_path, result_csv_name)
if (row_names == TRUE) {
write.csv(result_DF,full_save_path, row.names = TRUE)
} else {
write.csv(result_DF,full_save_path, row.names = FALSE)
}

}
```

# preprocessing for GCAM XML
## I am right here


```{r S3 automatically read the file}

# agb_files <- list.files(path = main_Sagb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)
# 
# 
# bgb_files <- list.files(path = main_Sbgb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)
# 
# print(agb_files)
# print(bgb_files)
```

```{r S4 read the file}



if (plot_case == 1){
### diff SSPs
sub_case_names<-c("SSP126","SSP370","SSP585")


agb_file_SSP126_gfdl <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp126_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP370_gfdl <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp370_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP585_gfdl <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")


bgb_file_SSP126_gfdl <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp126_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP370_gfdl <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp370_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP585_gfdl <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")

agb_files<-c(agb_file_SSP126_gfdl,agb_file_SSP370_gfdl,agb_file_SSP585_gfdl)
bgb_files<-c(bgb_file_SSP126_gfdl,bgb_file_SSP370_gfdl,bgb_file_SSP585_gfdl)
##############################
} else if(plot_case==2){
### diff CC component
sub_case_names<-c("CO2","N deposition","precipi and temp")
  
agb_file_SSP585_default <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_agb_v3.csv")
agb_file_SSP585_2015co2 <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_2015co2_fullscalerc3c4_agb_v3.csv")
agb_file_SSP585_ndep <- paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_ssp585ndep_fullscalerc3c4_agb_v3.csv")


bgb_file_SSP585_default <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_default_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP585_2015co2 <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_2015co2_fullscalerc3c4_bgb_v3.csv")
bgb_file_SSP585_ndep <- paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_ssp585ndep_fullscalerc3c4_bgb_v3.csv")

agb_files<-c(agb_file_SSP585_default,agb_file_SSP585_2015co2,agb_file_SSP585_ndep)
bgb_files<-c(bgb_file_SSP585_default,bgb_file_SSP585_2015co2,bgb_file_SSP585_ndep)
}

```


```{r S5 read harmonized land type area in each subregion table }


in_forest_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_forest.csv"))%>%
  mutate(harm_type="Forest")
  
in_c3crop_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_c3crop.csv"))%>%
  mutate(harm_type="c3Crop")

in_c4crop_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_c4crop.csv"))%>%
  mutate(harm_type="c4Crop")

in_grass_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_grass.csv"))%>%
  mutate(harm_type="Grass")

in_Harmolandtype_area <-bind_rows(in_forest_area,in_c3crop_area,in_c4crop_area,in_grass_area)
  


```

```{r S6 data_process_plot functions}
process_in_file <- function(file, harmolandtype_area) {
    # Read the CSV file
    in_Sagb <- read.csv(file, check.names = FALSE)
  
    # Process the data
    in_Sagb %>%
      dplyr::select(-3, -2) %>%
      filter(harm_type != "Other") %>%
      left_join(harmolandtype_area, by = c("out_reg_code", "out_lu_code", "harm_type")) %>%
      dplyr::select(-7, -6) %>%
      group_by(region, harm_type) %>%
      mutate(region_pft_area = sum(pft_area_total, na.rm = TRUE)) %>%
      mutate(region_pft_area_weight = pft_area_total / region_pft_area) %>%
      summarize(across(
        .cols = 4:22,
        .fns = ~ weighted.mean(.x, w = region_pft_area_weight, na.rm = TRUE)
      )) %>%
      ungroup() %>%
      pivot_longer(cols = 3:ncol(.),
                   names_to = "year",
                   values_to = "scalar") %>%
      mutate(year = as.numeric(year)) %>%
      na.omit()
}

process_global_data <- function(data) {
     # data<-in_Sagb_co2
  # write.csv(data,"data.csv")
   
  data %>%
    dplyr::select(-3) %>%
    filter(harm_type != "Other") %>%
    group_by(child.nodes) %>%
    pivot_wider(names_from = "year",values_from = "scalar")%>%
    ungroup()%>%
    dplyr::select(-2) %>%
    left_join(in_Harmolandtype_area, by = c("out_reg_code", "out_lu_code", "harm_type")) %>%
    group_by(harm_type) %>%
    mutate(global_pft_area = sum(pft_area_total, na.rm = TRUE)) %>%
    mutate(global_pft_area_weight = pft_area_total / global_pft_area) %>%
    summarize(across(
    .cols = 7:23,
    .fns = list(
      mean = ~ weighted.mean(.x, w = global_pft_area_weight, na.rm = TRUE),
      sd = ~ sqrt(weighted.mean((.x - weighted.mean(.x, w = global_pft_area_weight, na.rm = TRUE))^2, w = global_pft_area_weight, na.rm = TRUE))
    )
  )) %>%
  ungroup() %>%
  pivot_longer(cols = ends_with("_mean") | ends_with("_sd"),
               names_to = "year_stat",
               values_to = "value") %>%
  separate(year_stat, into = c("year", "stat"), sep = "_", convert = TRUE) %>%
  pivot_wider(names_from = stat, values_from = value) %>%
  mutate(year = as.numeric(year)) %>%
  select(harm_type, year, mean, sd) %>%
    na.omit()
}


      
#############################
  create_global_plot <- function(data,
                                 y_var_m,
                                 y_var_sd,
                                 ylimits = c(-0.2, 0.75),
                                 if_title,
                                 t_title,
                                 if_xtitle = FALSE,
                                 x_title,
                                 if_ytitle= FALSE,
                                 y_title,
                                 ifagb = TRUE,
                                 lab,
                                 hj=10
  ) {
    
    # data<-check_belowCD_long_gmean_combined
    # y_var_m <-"co2"
    #   y_var_sd <-"co2_sd"
    #   ylimits <- c(-0.2, 0.75)
    #   if_title <-TRUE
    #   t_title<-"CO2"
    #   if_xtitle <- TRUE
    # x_title <- "Year"
    #   if_ytitle <- TRUE
    # y_title <- "Agb Carbon scalar"
    #   ifagb <- FALSE
    # lab <- "(a)"
    #   hj<-10
    # 
  
 p<- ggplot(data, aes(x = as.numeric(year), y = !!sym(y_var_m), group = harm_type, color = harm_type)) +
   geom_ribbon(aes(ymin = !!sym(y_var_m) - !!sym(y_var_sd)/2,  ymax = !!sym(y_var_m) + !!sym(y_var_sd)/2, fill = harm_type), color = NA, alpha = 0.2, show.legend = FALSE) +
    geom_line(aes(color = harm_type), size = 1, show.legend = FALSE) +
    labs(title = if (if_title) t_title else NULL,
       x = if (if_xtitle) x_title else NULL,
         y =if (if_ytitle) y_title else NULL,
         color = "Harmonized Types") +
    theme_minimal() +
    theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
          legend.position = "none",
          plot.title = element_text(hjust = 0.5, face = "bold")) +
    ylim(ylimits)+
    annotate(
      "text",
      x = Inf,
      y = Inf,
      label =lab,
      hjust = hj,
      vjust = 1.5,
      size = 4
    )
  
    
 if (!if_ytitle) {
  p <- p +
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
 }
  
  if (ifagb == TRUE) {
  p <- p +
    theme(axis.text.x = element_blank(),
          axis.ticks.x = element_blank())
}else if (ifagb == FALSE) {p<-p}
 

  }
##############################
# Function to save the regional combined plots for each CC component
# Define plot size

save_combined_plot <- function(plot, name_suffix,wid_size=15,hei_size=10) {
  file_base <- paste0(fig_save_path, "/",Fig_num_name, "_combined_", name_suffix, "_regions_v", version_num)
  
  ggsave(paste0(file_base, ".svg"), plot = plot, width = wid_size, height = hei_size, units = "in")
  ggsave(paste0(file_base, ".pdf"), plot = plot, width = wid_size, height = hei_size, units = "in")
  ggsave(paste0(file_base, ".png"), plot = plot, width = wid_size, height = hei_size, units = "in", dpi = 300)
  ggsave(filename = paste0(file_base, ".tif"), plot = plot, width = wid_size, height = hei_size, units = "in", device = "tiff", dpi = 300)
}
```

```{r S7 plot and save regional agb scaler group map}

#lab=agbfignum[data_idx],hj=bhjusts[data_idx]

##########################
# Initialize empty lists to store plots and processed data
# pagb_list <- list()
# 
# agbfignum <- c("(a)","(b)","(c)")
# 
# ahjusts<-c(10,10.01,10.25)
# y_titles <- c("Agb Carbon Scalars", "", "")
  


```

```{r S8 plot and save regional agb scaler group map}



##########################
# Initialize empty lists to store plots and processed data
# pbgb_list <- list()
# check_belowCD_long_gmean_list <- list()
# bgbfignum <- c("(d)","(e)","(f)")
# bhjusts<-c(10,10,12.7)
# For each dataset (this loop can be uncommented and used if needed)
# for (data_idx in c(1,2,3)) {


```



```{r S9 global plot & save}
pagb_list<- list()
pbgb_list<- list()
## AGB  ###################################################################################

in_Sagb_file_default <- agb_files[1]
in_Sagb_file_2015co2 <- agb_files[2]
in_Sagb_file_ndep <- agb_files[3]

in_Sagb_default1 <- read.csv(in_Sagb_file_default , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "default")
in_Sagb_2015co21 <- read.csv(in_Sagb_file_2015co2 , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "co22015")
in_Sagb_ndep1 <- read.csv(in_Sagb_file_ndep , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "ndep585")


in_Sagb_co2<-in_Sagb_default1%>%
  left_join(in_Sagb_2015co21, by=c("region","child.nodes","above.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = default-co22015)%>%
  select(-c("default","co22015"))

in_Sagb_N_dep<-in_Sagb_default1%>%
  left_join(in_Sagb_ndep1, by=c("region","child.nodes","above.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ndep585-default)%>%
  select(-c("default","ndep585"))

in_Sagb_tempperci<-in_Sagb_2015co21%>%
  mutate(scalar = co22015-1)%>%
  select(-c("co22015"))




check_aboveCD_long_gmean_co2 <- process_global_data(in_Sagb_co2)%>%
  rename(co2 = mean,
         co2_sd = sd)
check_aboveCD_long_gmean_N_dep <- process_global_data(in_Sagb_N_dep)%>%
  rename(N_dep = mean,
         N_dep_sd = sd)
check_aboveCD_long_gmean_tempperci <- process_global_data(in_Sagb_tempperci)%>%
  rename(tempperci = mean,
         tempperci_sd = sd)

  
  check_aboveCD_long_gmean_combined<-check_aboveCD_long_gmean_co2%>%
  left_join(check_aboveCD_long_gmean_N_dep,by=c("harm_type","year"))%>%
  left_join(check_aboveCD_long_gmean_tempperci,by=c("harm_type","year"))%>%
    # replace c3Crop with C3crop, c4Crop with C4crop
    mutate(harm_type = gsub("c3Crop", "C3crop", harm_type))%>%
    mutate(harm_type = gsub("c4Crop", "C4crop", harm_type))
  
  
  ## save for check
  check_aboveCD_long_gmean_combined_2100<-check_aboveCD_long_gmean_combined%>%
    filter(year==2100)
  
  
  write.csv( check_aboveCD_long_gmean_combined_2100,paste0(fig_save_path,"Fig2_check_aboveCD_long_gmean_combined_2100.csv"))
 
    
ax_title<-c("","","")
y_agb_titles<-c("Agb Carbon Scalar","","")
a_ylimits<-c(-0.27, 0.75)

pagb_list[[1]] <- create_global_plot(
  check_aboveCD_long_gmean_combined,
  y_var_m = "co2",
  y_var_sd = "co2_sd",
  ylimits = a_ylimits,
  if_title = TRUE,
  t_title = "CO2",
  if_xtitle = FALSE,
  x_title = ax_title[1],
  if_ytitle = TRUE,
  y_title = y_agb_titles[1],
  ifagb = TRUE,
  lab = "(a)",
  hj = 10.3
)

pagb_list[[2]] <- create_global_plot(
  check_aboveCD_long_gmean_combined,
  y_var_m = "tempperci",
  y_var_sd = "tempperci_sd",
  ylimits = a_ylimits,
  if_title = TRUE,
  t_title = "temp&perci",
  if_xtitle = FALSE,
  x_title = ax_title[2],
  if_ytitle = FALSE,
  y_title = y_agb_titles[2],
  ifagb = TRUE,
  lab = "(b)",
  hj = 10.3
)
   
 pagb_list[[3]] <- create_global_plot(
  check_aboveCD_long_gmean_combined,
  y_var_m = "N_dep",
  y_var_sd = "N_dep_sd",
  ylimits = a_ylimits,
  if_title = TRUE,
  t_title = "N deposition",
  if_xtitle = FALSE,
  x_title = ax_title[3],
  if_ytitle = FALSE,
  y_title = y_agb_titles[3],
  ifagb = TRUE,
  lab = "(c)",
  hj = 11
)  


# pagb_list[[1]] <- create_global_plot(check_aboveCD_long_gmean_combined, "co2",y_agb_titles, 1)
# pagb_list[[3]] <- create_global_plot(check_aboveCD_long_gmean_combined, "tempperci",y_agb_titles,3)
# pagb_list[[2]] <- create_global_plot(check_aboveCD_long_gmean_combined, "N_dep",y_agb_titles, 2)


combined_agb_plots <- wrap_plots(pagb_list, nrow = 1)

## BGB #########################################################
in_Sbgb_file_default <- bgb_files[1]
in_Sbgb_file_2015co2 <- bgb_files[2]
in_Sbgb_file_ndep <- bgb_files[3]


in_Sbgb_default1 <- read.csv(in_Sbgb_file_default , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "default")
in_Sbgb_2015co21 <- read.csv(in_Sbgb_file_2015co2 , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "co22015")
in_Sbgb_ndep1 <- read.csv(in_Sbgb_file_ndep , check.names = FALSE)%>%
  pivot_longer(cols = 10:26,names_to = "year",values_to = "ndep585")


in_Sbgb_co2<-in_Sbgb_default1%>%
  left_join(in_Sbgb_2015co21, by=c("region","child.nodes","below.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = default-co22015)%>%
  select(-c("default","co22015"))

in_Sbgb_N_dep<-in_Sbgb_default1%>%
  left_join(in_Sbgb_ndep1, by=c("region","child.nodes","below.ground.carbon.density","landtype","subregion","broad_type","harm_type","out_reg_code","out_lu_code","year"))%>%
  mutate(scalar = ndep585-default)%>%
  select(-c("default","ndep585"))

in_Sbgb_tempperci<-in_Sbgb_2015co21%>%
  mutate(scalar = co22015-1)%>%
  select(-c("co22015"))




check_belowCD_long_gmean_co2 <- process_global_data(in_Sbgb_co2)%>%
  rename(co2 = mean,
         co2_sd = sd)
check_belowCD_long_gmean_N_dep <- process_global_data(in_Sbgb_N_dep)%>%
  rename(N_dep = mean,
         N_dep_sd = sd)
check_belowCD_long_gmean_tempperci <- process_global_data(in_Sbgb_tempperci)%>%
  rename(tempperci = mean,
         tempperci_sd = sd)

  
  check_belowCD_long_gmean_combined<-check_belowCD_long_gmean_co2%>%
  left_join(check_belowCD_long_gmean_N_dep,by=c("harm_type","year"))%>%
  left_join(check_belowCD_long_gmean_tempperci,by=c("harm_type","year"))%>%
    # replace c3Crop with C3crop, c4Crop with C4crop
    mutate(harm_type = gsub("c3Crop", "C3crop", harm_type))%>%
    mutate(harm_type = gsub("c4Crop", "C4crop", harm_type))
 
    ## save for check
  check_belowCD_long_gmean_combined_2100<-check_belowCD_long_gmean_combined%>%
    filter(year==2100)
  
  
  write.csv( check_belowCD_long_gmean_combined_2100,paste0(fig_save_path,"Fig2_check_belowCD_long_gmean_combined_2100.csv"))

bx_title<-c("Year","Year","Year")
y_bgb_titles<-c("Bgb Carbon Scalars","","")
b_ylimits<-c(-0.1, 0.1)

pbgb_list[[1]] <- create_global_plot(
  check_belowCD_long_gmean_combined,
  y_var_m = "co2",
  y_var_sd = "co2_sd",
  ylimits = b_ylimits,
  if_title = FALSE,
  t_title = "CO2",
  if_xtitle = TRUE,
  x_title = bx_title[1],
  if_ytitle = TRUE,
  y_title = y_bgb_titles[1],
  ifagb = FALSE,
  lab = "(d)",
  hj = 10.3
)

pbgb_list[[2]] <- create_global_plot(
  check_belowCD_long_gmean_combined,
  y_var_m = "tempperci",
  y_var_sd = "tempperci_sd",
  ylimits = b_ylimits,
  if_title = FALSE,
  t_title = "temp&perci",
  if_xtitle = TRUE,
  x_title = bx_title[2],
  if_ytitle = FALSE,
  y_title = y_bgb_titles[2],
  ifagb = FALSE,
  lab = "(e)",
  hj = 10.3
)
   
 pbgb_list[[3]] <- create_global_plot(
  check_belowCD_long_gmean_combined,
  y_var_m = "N_dep",
  y_var_sd = "N_dep_sd",
  ylimits = b_ylimits,
  if_title = FALSE,
  t_title = "N deposition",
  if_xtitle = TRUE,
  x_title = bx_title[3],
  if_ytitle = FALSE,
  y_title = y_bgb_titles[3],
  ifagb = FALSE,
  lab = "(f)",
  hj = 13.5
)  

combined_bgb_plots <- wrap_plots(pbgb_list, nrow = 1)
 
############################################################################
p_global_legend <- 
  
  ggplot(check_belowCD_long_gmean_combined, aes(x = as.numeric(year), y = co2, group = harm_type, color = harm_type))+
    geom_ribbon(aes(ymin = co2 - co2_sd/2, ymax = co2 + co2_sd/2, fill = harm_type), color = NA, alpha = 0.2) +
    geom_line(aes(color = harm_type), size = 1) +
  labs(title = NULL,
       x = "Year",
       y = "",
       color = "Harmonized Types") +
  theme_minimal() +
  theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
        plot.title = element_text(hjust = 0.5))  +
  guides(color = guide_legend("Harmonized Types"), fill = guide_legend("Harmonized Types", override.aes = list(linetype = 1)))
  
  
  #################
  # ggplot(check_belowCD_long_gmean_combined, aes(x = as.numeric(year), y = co2, group = harm_type, color = harm_type)) +
  #   geom_line() +
  #   labs(title = "",
  #        x = "Year",
  #        y = y_titles[data_idx],
  #        color = "Harmonized Type") +
  #   theme_minimal() +
  #   theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
  #         plot.title = element_text(hjust = 0.5) ) 
########################################

global_legend <- cowplot::get_legend(p_global_legend)


agb_bgb_list<-c(pagb_list,pbgb_list)
combined_global_agbbgb_plots <- wrap_plots(agb_bgb_list, nrow = 2)  # Combine AGB plots into a single row


combined_global_agbbgb_plot <- plot_grid(
  combined_global_agbbgb_plots,  # Vertical stack of AGB and BGB plots
  global_legend,                 # Legend
  ncol = 2,                      # Two columns: one for plots, one for the legend
  rel_widths = c(1, 0.2)         # Relative widths, giving most space to the plots and less to the legend
)


save_combined_plot(combined_global_agbbgb_plot, "Sagbbgb_global_CC_component",wid_size=18*0.5,hei_size=10*0.5)


```



