---
title: "GTM_4_dim_var_process"
author: "Meng Luo"
date: "2023-08-29"
output: html_document
    toc: true
    toc_float: true
---
# use the mature age's FP as the input for GCAM


#########################################################
## update of the this version
# add FULL_matrix_for_MFP_continue

# Content
## link to github
  S0 link to github
## Setting Up
  S1 needed R package and dir
 
  
  
  
  
# link to github
```{r S0 link to github , include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
```

# Setting Up
## Loading Needed R Packages and Setting Directory

```{r S1 needed R package and dir }

#install.packages("drake")
library('drake')
#install.packages("cowplot")
library(cowplot)
############
require(devtools)
#Please use this in console if needed: install_github('JGCRI/rgcam', build_vignettes=TRUE, force =TRUE)
library (rgcam)
library(tidyverse)
library(tidyr)

library(rlang)
library(dplyr)
# install.packages("patchwork")
library(patchwork)
# install.packages("sf")
library(sf)
# install.packages("svglite")
library(svglite)
library(cowplot)
library(gridExtra)
library(ggthemes)
library(stringr)
library(ggplot2)
library(RColorBrewer)

library(scales)


## run this in console devtools::load_all()


version_num <-"4_2"
case_name<-"_climate_productivityC"
#################################################################################################
## need to modify 
# plot_case<-1 # diff SSPs
plot_case<-1 # diff CC component
 
cases<-c("3SSPs")

case<-cases[plot_case]


## end of need to modify 
# read from hard disk ##############################################################
# # Chen lab desktop
# # root<-"O:/"
# 
# # 2023 laptop
# root<-"D:/"
# 
# 
# main_Sagb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_aboveCD/region_5ymean_alltypes_wrapper/")
# 
# 
# main_Sbgb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_belowCD/region_5ymean_alltypes_wrapper/")
# 
# 
# 
# XML_version <- paste0(version_num ,case_name,"_ssp",case) 

####

# main_GTM_mid_xml_path  <-"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/useful/"
# main_my_XML_path <- "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/new_XML/"
# # produce outputs in GCAM 7.0 release package 
# main_v7_XML_path <- "E/Docker_GCAM_v7_forest/gcam-master/input/gcamdata/xml/"
# 
# fig_save_path <- paste0(root,"E/new laptop2/PHD/my_2024_1_manuscript/Figure&table/figure/check_npp_rh_scaler_4in1_file/")

# Harmolandtype_area_main_path<-paste0(root,"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/")
# read from 2023 laptop  ##############################################################

# 2023 laptop
# root <- "C:/MengLuo/chapter 2_backup/"

# NAS
root <- "Z:/Meng/back_up_all/9_updates/"

########################################################################################
main_Sagb_path <- paste0(root, "climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_aboveCD/grid/")


main_Sbgb_path <- paste0(root, "climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_belowCD/grid/")

XML_version <- paste0(version_num ,case_name,"_ssp",case)


#####

# main_GTM_mid_xml_path  <-"climate_FPC_GCAM/Data/GCAM data system_forestversion/useful/"
# main_my_XML_path <- "climate_FPC_GCAM/Data/GCAM data system_forestversion/new_XML/"
# # produce outputs in GCAM 7.0 release package 
# main_v7_XML_path <- "XML_save/"

fig_save_path <- paste0(root,"my_2024_1_manuscript/Figure&table/figure/C_scalar_grid_spatial/")

# Harmolandtype_area_main_path<-paste0(root,"climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/")


shp_path <- paste0(root, "climate_FPC_GCAM/Code/boundary/gcam_boundaries_moirai_3p1_0p5arcmin_wgs84/gcam_boundaries_moirai_3p1_0p5arcmin_wgs84/main_outputs/boundries5.shp")

data_sf <- st_read(shp_path)

```


## read GTM output txt file
separate each var and save in csv

# function section


```{r S2 function save_result }
save_csv_result <- function(result_DF, result_csv_name,row_names) {

full_save_path <- paste0(root,main_GTM_path, result_csv_name)
if (row_names == TRUE) {
write.csv(result_DF,full_save_path, row.names = TRUE)
} else {
write.csv(result_DF,full_save_path, row.names = FALSE)
}

}
```

# preprocessing for GCAM XML
## I am right here


```{r S2 automatically read the file}

# agb_files <- list.files(path = main_Sagb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)
# 
# 
# bgb_files <- list.files(path = main_Sbgb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)
# 
# print(agb_files)
# print(bgb_files)
```

```{r S2_2 read the file}

# forcing <- 1 # gfdl
# forcing <- 2 # ukesm


### diff SSPs
sub_case_names<-c("SSP126","SSP370","SSP585")

# if (forcing == 1){
  
# forcing_name2<-"gfdl_"

## gfdl ####################################
agb_file_SSP585_default_gfdl <- read.csv(paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_default_grid_scale_forest.csv"))%>%
  dplyr::select(center_lon,center_lat,npp)
agb_file_SSP585_2015co2_gfdl <- read.csv(paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_2015co2_grid_scale_forest.csv"))%>%
  dplyr::select(center_lon,center_lat,npp)
agb_file_SSP585_ndep_gfdl <- read.csv(paste0(main_Sagb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_ssp585ndep_grid_scale_forest.csv"))%>%
  dplyr::select(center_lon,center_lat,npp)


bgb_file_SSP585_default_gfdl <- read.csv(paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_default_grid_scale_forest.csv"))%>%
  dplyr::select(center_lon,center_lat,rh_npp)
bgb_file_SSP585_2015co2_gfdl <- read.csv(paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_2015co2_grid_scale_forest.csv"))%>%
  dplyr::select(center_lon,center_lat,rh_npp)
bgb_file_SSP585_ndep_gfdl <- read.csv(paste0(main_Sbgb_path, "classic_gfdl-esm4_w5e5_ssp585_2015soc-from-histsoc_ssp585ndep_grid_scale_forest.csv"))%>%
  dplyr::select(center_lon,center_lat,rh_npp)


  
agb_file_SSP585_default_ukesm <- read.csv(paste0(main_Sagb_path, "classic_ukesm1-0-ll_w5e5_ssp585_2015soc-from-histsoc_default_grid_scale_forest.csv"))%>%
  dplyr::select(center_lon,center_lat,npp)
agb_file_SSP585_2015co2_ukesm <- read.csv(paste0(main_Sagb_path, "classic_ukesm1-0-ll_w5e5_ssp585_2015soc-from-histsoc_2015co2_grid_scale_forest.csv"))%>%
  dplyr::select(center_lon,center_lat,npp)
agb_file_SSP585_ndep_ukesm <- read.csv(paste0(main_Sagb_path, "classic_ukesm1-0-ll_w5e5_ssp585_2015soc-from-histsoc_default_grid_scale_forest.csv"))%>%
  dplyr::select(center_lon,center_lat,npp)


bgb_file_SSP585_default_ukesm <- read.csv(paste0(main_Sbgb_path, "classic_ukesm1-0-ll_w5e5_ssp585_2015soc-from-histsoc_default_grid_scale_forest.csv"))%>%
  dplyr::select(center_lon,center_lat,rh_npp)
bgb_file_SSP585_2015co2_ukesm <- read.csv(paste0(main_Sbgb_path, "classic_ukesm1-0-ll_w5e5_ssp585_2015soc-from-histsoc_2015co2_grid_scale_forest.csv"))%>%
  dplyr::select(center_lon,center_lat,rh_npp)
bgb_file_SSP585_ndep_ukesm <- read.csv(paste0(main_Sbgb_path, "classic_ukesm1-0-ll_w5e5_ssp585_2015soc-from-histsoc_default_grid_scale_forest.csv"))%>%
  dplyr::select(center_lon,center_lat,rh_npp)



agb_file_CC_gfdl<-agb_file_SSP585_default_gfdl%>%
  rename(default = npp)%>%
  left_join(agb_file_SSP585_2015co2_gfdl%>%rename(co22015 = npp), by = c("center_lon","center_lat"))%>%
  distinct()%>%
  mutate(gfdl = default-co22015)%>%
  dplyr::select(-default, -co22015)%>%
   distinct()

agb_file_CO2_gfdl<-agb_file_SSP585_2015co2_gfdl%>%
  mutate(gfdl = npp-1)%>%
  dplyr::select(-npp)%>%
   distinct()


agb_file_N_gfdl<-agb_file_SSP585_default_gfdl%>%
  rename(default = npp)%>%
  left_join(agb_file_SSP585_ndep_gfdl%>%rename(ndep = npp), by = c("center_lon","center_lat"))%>%
  distinct()%>%
  mutate(gfdl = ndep-default)%>%
  dplyr::select(-default, -ndep)



agb_file_CC_ukesm<-agb_file_SSP585_default_ukesm%>%
  rename(default = npp)%>%
  left_join(agb_file_SSP585_2015co2_ukesm%>%rename(co22015 = npp), by = c("center_lon","center_lat"))%>%
  distinct()%>%
  mutate(ukesm = default-co22015)%>%
  dplyr::select(-default, -co22015)%>%
   distinct()

agb_file_CO2_ukesm<-agb_file_SSP585_2015co2_ukesm%>%
  mutate(ukesm = npp-1)%>%
  dplyr::select(-npp)%>%
   distinct()


agb_file_N_ukesm<-agb_file_SSP585_default_ukesm%>%
  rename(default = npp)%>%
  left_join(agb_file_SSP585_ndep_ukesm%>%rename(ndep = npp), by = c("center_lon","center_lat"))%>%
  distinct()%>%
  mutate(ukesm = ndep-default)%>%
  dplyr::select(-default, -ndep)%>%
   distinct()

#################

bgb_file_CC_gfdl<-bgb_file_SSP585_default_gfdl%>%
  rename(default = rh_npp)%>%
  left_join(bgb_file_SSP585_2015co2_gfdl%>%rename(co22015 = rh_npp), by = c("center_lon","center_lat"))%>%
  distinct()%>%
  mutate(gfdl = default-co22015)%>%
  dplyr::select(-default, -co22015)%>%
   distinct()

bgb_file_CO2_gfdl<-bgb_file_SSP585_2015co2_gfdl%>%
  mutate(gfdl = rh_npp-1)%>%
  dplyr::select(-rh_npp)%>%
   distinct()


bgb_file_N_gfdl<-bgb_file_SSP585_default_gfdl%>%
  rename(default = rh_npp)%>%
  left_join(bgb_file_SSP585_ndep_gfdl%>%rename(ndep = rh_npp), by = c("center_lon","center_lat"))%>%
  distinct()%>%
  mutate(gfdl = ndep-default)%>%
  dplyr::select(-default, -ndep)%>%
   distinct()



bgb_file_CC_ukesm<-bgb_file_SSP585_default_ukesm%>%
  rename(default = rh_npp)%>%
  left_join(bgb_file_SSP585_2015co2_ukesm%>%rename(co22015 = rh_npp), by = c("center_lon","center_lat"))%>%
  distinct()%>%
  mutate(ukesm = default-co22015)%>%
  dplyr::select(-default, -co22015)%>%
   distinct()

bgb_file_CO2_ukesm<-bgb_file_SSP585_2015co2_ukesm%>%
  mutate(ukesm = rh_npp-1)%>%
  dplyr::select(-rh_npp)%>%
   distinct()


bgb_file_N_ukesm<-bgb_file_SSP585_default_ukesm%>%
  rename(default = rh_npp)%>%
  left_join(bgb_file_SSP585_ndep_ukesm%>%rename(ndep = rh_npp), by = c("center_lon","center_lat"))%>%
  distinct()%>%
  mutate(ukesm = ndep-default)%>%
  dplyr::select(-default, -ndep)%>%
   distinct()

###################











agb_file_SSP126_mean<-read_rds("agb_file_SSP126_mean.RDS") 

not_NA_col_num <- which(is.na(agb_file_SSP126_mean$mean))

agb_file_N_mean <- agb_file_N_gfdl %>%
  left_join(agb_file_N_ukesm)  %>%
  mutate(mean = rowMeans(cbind(ukesm, gfdl), na.rm = TRUE))%>%
  mutate(mean=ifelse(is.na(mean),0,mean))%>%
  mutate(mean = ifelse(row_number() %in% not_NA_col_num, NA, mean))

agb_file_CC_mean <- agb_file_CC_gfdl %>%
  mutate(gfdl=ifelse(is.na(gfdl),0,gfdl))%>%
  left_join(agb_file_CC_ukesm, by = c("center_lon", "center_lat"))  %>%
  mutate(mean = rowMeans(cbind(ukesm, gfdl), na.rm = TRUE))%>%
  mutate(mean=ifelse(is.na(mean),0,mean))%>%
  mutate(mean = ifelse(row_number() %in% not_NA_col_num, NA, mean))

# Check for duplicates and fix joins
agb_file_CO2_mean <-
  agb_file_CO2_gfdl %>%
  left_join(agb_file_CC_ukesm, by = c("center_lon", "center_lat"))  %>%
  mutate(mean = rowMeans(cbind(ukesm, gfdl), na.rm = TRUE))%>%
  mutate(mean=ifelse(is.na(mean),0,mean))%>%
  mutate(mean = ifelse(row_number() %in% not_NA_col_num, NA, mean))





bgb_file_CC_mean<-bgb_file_CC_gfdl%>%
  left_join(bgb_file_CC_ukesm) %>%
  mutate(mean = rowMeans(cbind(ukesm, gfdl), na.rm = TRUE))%>%
  mutate(mean=ifelse(is.na(mean),0,mean))%>%
  mutate(mean = ifelse(row_number() %in% not_NA_col_num, NA, mean))


bgb_file_CO2_mean<-bgb_file_CO2_gfdl%>%
  left_join(
    bgb_file_CC_ukesm, by = c("center_lon", "center_lat")
  ) %>%
  mutate(mean = rowMeans(cbind(ukesm, gfdl), na.rm = TRUE))%>%
  mutate(mean=ifelse(is.na(mean),0,mean))%>%
  mutate(mean = ifelse(row_number() %in% not_NA_col_num, NA, mean))


 





bgb_file_N_mean<-bgb_file_N_gfdl%>%
  left_join(bgb_file_N_ukesm)%>%
  mutate(mean = rowMeans(cbind(ukesm, gfdl), na.rm = TRUE))%>%
  mutate(mean=ifelse(is.na(mean),0,mean))%>%
  mutate(mean = ifelse(row_number() %in% not_NA_col_num, NA, mean))

```


```{r S3 read harmonized land type area in each subregion table }

# Combine your three datasets (df1, df2, df3)


# Calculate global min and max for npp across all datasets
value_min <- min(
  agb_file_CC_mean$mean,
  agb_file_CO2_mean$mean,
  agb_file_N_mean$mean,
  bgb_file_CC_mean$mean,
  bgb_file_CO2_mean$mean,
  bgb_file_N_mean$mean,
  na.rm = TRUE
)
value_max <- max(agb_file_SSP585_default_gfdl$npp,
  agb_file_CC_mean$mean,
  agb_file_CO2_mean$mean,
  agb_file_N_mean$mean,
  bgb_file_CC_mean$mean,
  bgb_file_CO2_mean$mean,
  bgb_file_N_mean$mean,
  na.rm = TRUE)


value_min <--1
value_max <- 1


# Function to plot spatial data
plot_spatial_map <- function(data, npp_min, npp_max,show_legend = FALSE,if_ytitle=FALSE,ifxlabel=FALSE) {
  
  # data<-agb_file_CC_mean
  # value_min<-value_min
  # value_max<-value_max
  # 
  # if_ytitle<-TRUE
  # ifxlabel<-FALSE
  # show_legend <- TRUE
  
  
 
  
  p <- ggplot(data, aes(x = center_lon, y = center_lat, fill = mean)) +
  geom_tile() +  # Create the gridded map
  geom_sf(
    data = data_sf,  # Use the custom shapefile
    inherit.aes = FALSE,  # Prevent inheritance of fill = mean from ggplot()
    fill = NA,  # No fill color for the boundary
    color = "grey20",  # Boundary line color
    size = 0.4         # Line thickness
  ) +
  labs(
    y = '',
    x = '',
    title = ''
  ) +
  scale_fill_gradientn(
    # colors = c("#FF6503", "#ffffb2", "#2BA428"),
    colors = c("#D33300", "#ffffb2", "#169B13"),
    
    values = rescale(c(value_min, 0, value_max)),  # Normalize the values to include min, 0, and max
    limits = c(value_min, value_max),  # Set color scale limits
    name = "Carbon scalar",
    na.value = "grey80",  # Set NA or missing values to grey80
    guide = guide_colourbar(
      ticks.colour = "black",  # Set scale ticks color to grey20
      ticks.linewidth = 0.3,    # Adjust tick line width for better visibility
      frame.colour = "black",  # Set color bar border to grey20
      frame.linewidth = 0.3,    # Adjust the border line width
      # ticks = element_line(),             # Ensure ticks are shown
      # nbin = 100, 
      # draw.ulim = FALSE, 
      # draw.llim = FALSE,
      label.hjust = 1,  # Align the tick labels to the right
      # ticks.outside = TRUE  # Set ticks to appear only outside the color bar      # Place ticks outside the color bar border
    )
  ) +
  theme_minimal() +
  theme(
    panel.border = element_rect(color = "black", fill = NA, size = 0.5),
    panel.background = element_rect(fill = "white", colour = NA),
    plot.background = element_rect(fill = "white", colour = NA),
    axis.text.x = element_blank(),  # Remove X-axis tick labels
    axis.text.y = element_blank(),  # Remove Y-axis tick labels
    axis.ticks.x = element_blank(),  # Remove X-axis ticks
    axis.ticks.y = element_blank(),  # Remove Y-axis ticks
    axis.title.x = element_blank(),  # Remove X-axis title
    axis.title.y = element_blank(),  # Remove Y-axis title
    panel.grid.major = element_blank(),  # Hide major gridlines
    panel.grid.minor = element_blank(),  # Hide minor gridlines
    legend.text = element_text(size = 15),
    legend.title = element_text(size = 15),
    legend.position = ifelse(show_legend, "right", "none"),
    plot.margin = margin(t = 0, r = 0, b = 0, l = 0) , # Adjust margins
    legend.ticks.length = unit(c(-.15, 0), 'cm'), # different lengths for ticks on both sides
    legend.ticks = element_line(color='black') # just to show the ticks on a white background
  )



  
  
  if (!if_ytitle) {
    p <- p +
      theme(axis.text.y = element_blank(),
            axis.ticks.y = element_blank())
  }

  if (ifxlabel) {p<-p
    
  }else if (ifxlabel == FALSE) {
  p <- p +
      theme(axis.text.x = element_blank(),
            axis.ticks.x = element_blank())}
  
  return(p)
}





###############################
  # x_ticks <- seq(-180, 180, by = 90)  # Longitude range from -180 to 180 with 60-degree increments
  # y_ticks <- seq(-60, 85, by = 45)    # Latitude range from -90 to 90 with 30-degree increments
  # 
  # x_labels <- paste0(x_ticks, "째E")  # Append "째E" to each x tick label
  # y_labels <- paste0(y_ticks, "째N")  # Append "째N" to each y tick label
  # 
  # x_breaks <- seq(-180, 180, by = 90)  # Longitude graticule breaks
  # y_breaks <- seq(-60, 85, by = 45)     # Latitude graticule breaks
  # 
  # 
  # border <- ggplot(agb_file_SSP585_default_mean, aes(x = center_lon, y = center_lat, fill = mean)) +
  #     scale_fill_gradientn(
  #     colors = c("#FF6503", "#ffffb2", "#2BA428"),
  #     values = rescale(c(value_min, 1, value_max)), # Normalize the values to include min, 0, and max
  #     limits = c(value_min, value_max), # Set color scale limits
  #     name = "Carbon scalar",
  #     na.value = "grey80", # Set NA or missing values to grey20
  #     guide = guide_colourbar(  # Customize the legend ticks
  #       ticks.colour = "grey80",  # Change tick color to grey20
  #       ticks.linewidth = 0.5    # Adjust tick line width for better visibility
  #     )
  #   ) +
  #   
  #    scale_x_continuous(breaks = x_ticks, labels = x_labels) +
  #   scale_y_continuous(breaks = y_ticks, labels = y_labels) +
  #   theme_base() +
  #   labs(
  #     y = '',
  #     x = '',
  #     title = ''
  #   ) +
  #   theme(
  #     panel.background = element_rect(fill = "white", colour = NA),
  #     plot.background = element_rect(fill = "white", colour = NA),
  #     plot.title = element_text(hjust = 0.5, size = 15),
  #     axis.title.x = element_text(size = 15),
  #     axis.title.y = element_text(size = 15, face = "bold"),
  #     axis.text.x = element_text(size = 14.5),
  #     axis.text.y = element_text(size = 14.5),
  #     legend.text = element_text(size = 15),
  #     legend.title = element_text(size = 15),
  #     legend.position = ifelse(show_legend, "right", "none"),
  #     plot.margin = margin(t = 0, r = 1, b = 0, l = 0))
  #   
  # borderx <- border +
  #     theme(axis.text.y = element_blank(),
  #           axis.ticks.y = element_blank())
  # 
  # bordery <- border +
  #     theme(axis.text.x = element_blank(),
  #           axis.ticks.x = element_blank())
################################

# Example: Plot for the first dataset (replace df1 with your actual dataset name)
plot_agb_CC_mean <- plot_spatial_map(agb_file_CC_mean, value_min, value_max,if_ytitle=TRUE,ifxlabel=FALSE)

plot_agb_CO2_mean <- plot_spatial_map(agb_file_CO2_mean, value_min, value_max,if_ytitle=TRUE,ifxlabel=FALSE)

plot_agb_N_mean <- plot_spatial_map(agb_file_N_mean, value_min, value_max,if_ytitle=TRUE,ifxlabel=TRUE)



plot_bgb_CC_mean <- plot_spatial_map(bgb_file_CC_mean, value_min, value_max,if_ytitle=FALSE,ifxlabel=FALSE)

plot_bgb_CO2_mean <- plot_spatial_map(bgb_file_CO2_mean, value_min, value_max,if_ytitle=FALSE,ifxlabel=FALSE)

plot_bgb_N_mean <- plot_spatial_map(bgb_file_N_mean, value_min, value_max,if_ytitle=FALSE,ifxlabel=TRUE)





plot_legend<-plot_spatial_map(agb_file_N_mean, value_min, value_max, TRUE)
legend <- cowplot::get_legend(plot_legend)

```





```{r agb bgb save}


combined_agb_plots <- wrap_plots(plot_agb_CC_mean,plot_agb_CO2_mean,plot_agb_N_mean, nrow = 3)
combined_bgb_plots <- wrap_plots(plot_bgb_CC_mean,plot_bgb_CO2_mean,plot_bgb_N_mean, nrow = 3)
# combined_agbbgb_plots <- wrap_plots(p_C_126,p_bC_126,p_C_370,p_bC_370,p_C_585,p_bC_585, nrow = 3)
##############################################
combined_global_bgb_plot <- plot_grid(
  combined_agb_plots, 
  combined_bgb_plots,
  legend,                 # Legend
  ncol = 3,                      # Two columns: one for plots, one for the legend
  rel_widths = c(0.625,0.625, 0.2)         # Relative widths, giving most space to the plots and less to the legend
)





ggsave(paste0(fig_save_path, "/Fig63_CC_component_combined_Sagb_bgb_spatial_2forcing_mean_v",version_num,".pdf"), plot = combined_global_bgb_plot, width = 15*0.8, height = 10*0.8, units = "in")


# ggsave(paste0(fig_save_path, "/Fig63_CC_component_combined_Sagb_bgb_spatial_2forcing_mean_bounder_v",version_num,".pdf"), plot = border, width = 8*0.8, height = 4*0.8, units = "in")
# 
# ggsave(paste0(fig_save_path, "/Fig63_CC_component_combined_Sagb_bgb_spatial_2forcing_mean_bounderx_v",version_num,".pdf"), plot = borderx, width = 8*0.8, height = 4*0.8, units = "in")

# ggsave(paste0(fig_save_path, "/Fig63_CC_component_combined_Sagb_bgb_spatial_2forcing_mean_boundery_v",version_num,".pdf"), plot = bordery, width = 8*0.8, height = 4*0.8, units = "in")




```



