---
title: "GTM_4_dim_var_process"
author: "Meng Luo"
date: "2023-08-29"
output: html_document
    toc: true
    toc_float: true
---
# use the mature age's FP as the input for GCAM


#########################################################
## update of the this version
# add FULL_matrix_for_MFP_continue

# Content
## link to github
  S0 link to github
## Setting Up
  S1 needed R package and dir
 
  
  
  
  
# link to github
```{r S0 link to github , include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
```

# Setting Up
## Loading Needed R Packages and Setting Directory

```{r S1 needed R package and dir }
library(tidyverse)
library(tidyr)
#install.packages("rlang")
library(rlang)
library(dplyr)
library(gcamdata)
library('drake')
## run this in console devtools::load_all()

#################################################################################################
## need to modify 
 
# Chen lab desktop
root<-"O:/"

# 2023 laptop
root<-"D:/"

## ssp1




## ssp3




## ssp5
scenario<-"585" #  n for SSPn e.g. 1 for SSP1
version_num <-"1"
case_name<-"_climate_productivityC"




## end of need to modify 
#################################################################################################



main_Sagb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_aboveCD/region_5ymean_alltypes_wrapper/")


main_Sbgb_path <- paste0(root, "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/annual_wmean_belowCD/region_5ymean_alltypes_wrapper/")


# choose aggregation methods #####################
# 1 is agg A1 first, then LC1
# 2 is agg LC1 first, then A1
# 3 is using FP for the mature age


XML_version <- paste0(version_num ,case_name,"_ssp",scenario) 

## end need to modify 
#########################







main_GTM_mid_xml_path  <-"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/useful/"
main_my_XML_path <- "E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/GCAM data system_forestversion/new_XML/"
# produce outputs in GCAM 7.0 release package 
main_v7_XML_path <- "E/Docker_GCAM_v7_forest/gcam-master/input/gcamdata/xml/"

fig_save_path <- paste0(root,"E/new laptop2/PHD/my_2024_1_manuscript/Figure&table/figure/check_npp_rh_scaler_4in1_file/")

```


## read GTM output txt file
separate each var and save in csv

# function section


```{r S2 function save_result }
save_csv_result <- function(result_DF, result_csv_name,row_names) {

full_save_path <- paste0(root,main_GTM_path, result_csv_name)
if (row_names == TRUE) {
write.csv(result_DF,full_save_path, row.names = TRUE)
} else {
write.csv(result_DF,full_save_path, row.names = FALSE)
}

}
```

# preprocessing for GCAM XML
## I am right here


```{r S2 automatically read the file}




agb_files <- list.files(path = main_Sagb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)


bgb_files <- list.files(path = main_Sbgb_path, pattern = ".*_fullscalerc3c4.*\\.csv$", full.names = TRUE)

print(agb_files)
print(bgb_files)
```


```{r S3 read harmonized land type area in each subregion table }
Harmolandtype_area_main_path<-paste0(root,"E/new laptop2/PHD/phd_dissertation/climate_FPC_GCAM/Data/ISIMIP3b_processed/GCAM_subregion_mean/")

in_forest_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_forest.csv"))%>%
  mutate(harm_type="Forest")
  
in_c3crop_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_c3crop.csv"))%>%
  mutate(harm_type="c3Crop")

in_c4crop_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_c4crop.csv"))%>%
  mutate(harm_type="c4Crop")

in_grass_area<-read.csv(paste0(Harmolandtype_area_main_path,"Area_weight_grass.csv"))%>%
  mutate(harm_type="Grass")

in_Harmolandtype_area <-bind_rows(in_forest_area,in_c3crop_area,in_c4crop_area,in_grass_area)
  


```



```{r plot and save bgb scaler group map}

for (data_idx in c(1,2,4)) {
  # data_idx<-1
  in_Sbgb_file <- bgb_files[data_idx]
  in_Sbgb <- read.csv(in_Sbgb_file, check.names = FALSE)

  bgb_file_name <- basename(in_Sbgb_file)
  desired_name_part <- sub("_fullscaler.*", "", bgb_file_name)

  check_belowCD_long <- in_Sbgb %>%
    dplyr::select(-3,-2) %>%
    filter( harm_type!= "Other")%>%
    left_join(in_Harmolandtype_area,
              by = c("out_reg_code", "out_lu_code", "harm_type")) %>%
    
    group_by(region, harm_type) %>%
    mutate(region_pft_area = sum(pft_area_total, na.rm = TRUE)) %>%
    mutate(region_pft_area_weight = pft_area_total / region_pft_area) %>%
    summarize(across(
      .cols = 8:22,
      .fns = ~ weighted.mean(.x, w = region_pft_area_weight, na.rm = TRUE)
    )) %>%
    ungroup() %>%
    pivot_longer(cols = 3:ncol(.),
                 names_to = "year",
                 values_to = "scaler") %>%
    mutate(year = as.numeric(year)) %>%
    na.omit()
  
  
  # Create individual plots
  pc3 <- ggplot(check_belowCD_long %>% filter(harm_type == "c3Crop"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
    geom_line() +
    labs(title = paste0("bgb c3Crop scaler_", desired_name_part),
         x = "Year",
         y = "Value",
         color = "Region") +
    theme_minimal()+
  theme(
    panel.border = element_rect(color = "black", fill = NA, size = 1)  # Add a black outline frame
  )

  pc4 <- ggplot(check_belowCD_long %>% filter(harm_type == "c4Crop"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
    geom_line() +
    labs(title = paste0("bgb c4Crop scaler_", desired_name_part),
         x = "Year",
         y = "Value",
         color = "Region") +
    theme_minimal()+
  theme(
    panel.border = element_rect(color = "black", fill = NA, size = 1)  # Add a black outline frame
  )

  pf <- ggplot(check_belowCD_long %>% filter(harm_type == "Forest"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
    geom_line() +
    labs(title = paste0("bgb Forest scaler_", desired_name_part),
         x = "Year",
         y = "Value",
         color = "Region") +
    theme_minimal()+
  theme(
    panel.border = element_rect(color = "black", fill = NA, size = 1)  # Add a black outline frame
  )

  pg <- ggplot(check_belowCD_long %>% filter(harm_type == "Grass"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
    geom_line() +
    labs(title = paste0("bgb Grass scaler_", desired_name_part),
         x = "Year",
         y = "Value",
         color = "Region") +
    theme_minimal()+
  theme(
    panel.border = element_rect(color = "black", fill = NA, size = 1)  # Add a black outline frame
  )

  # Combine the plots into one figure
  combined_plot <- (pc3 + pc4) / (pf + pg) +
    # plot_layout(guides = 'collect') +
    plot_annotation(title = paste0("Combined bgb Scaler_", desired_name_part))

  
    # combined_plot <- (pc3 + pc4) / (pf + pg) + plot_annotation(title = paste0("Combined agb scaler_", desired_name_part))
  
  # Save the combined plot
  ggsave(paste0(fig_save_path, "/", desired_name_part, "_combined_Sbgb_regions.svg"), plot = combined_plot, width = 20, height = 20, units = "in")
  ggsave(paste0(fig_save_path, "/", desired_name_part, "_combined_Sbgb_regions.png"), plot = combined_plot, width = 20, height = 20, units = "in", dpi = 300)

  ####################################################################

  check_belowCD_long_gmean <- in_Sbgb %>%
    dplyr::select(-3, -2) %>%
  filter( harm_type!= "Other")%>%
    left_join(in_Harmolandtype_area,
              by = c("out_reg_code", "out_lu_code", "harm_type")) %>%
    
    group_by(harm_type) %>%
    mutate(global_pft_area = sum(pft_area_total, na.rm = TRUE)) %>%
    mutate(global_pft_area_weight = pft_area_total / global_pft_area) %>%
    summarize(across(
      .cols = 8:22,
      .fns = ~ weighted.mean(.x, w = global_pft_area_weight, na.rm = TRUE)
    )) %>%
    ungroup() %>%
    pivot_longer(cols = 3:ncol(.),
                 names_to = "year",
                 values_to = "scaler") %>%
    mutate(year = as.numeric(year)) %>%
    na.omit()

  p2 <- ggplot(check_belowCD_long_gmean, aes(x = as.numeric(year), y = scaler, group = harm_type, color = harm_type)) +
    geom_line() +
    labs(title = paste0("global mean bgb scaler_", desired_name_part),
         x = "Year",
         y = "Value",
         color = "Broad Type") +
    theme_minimal()+
  theme(
    panel.border = element_rect(color = "black", fill = NA, size = 1)  # Add a black outline frame
  )+ ylim(c(0.97,1.6))

  # Save the global mean plot
  ggsave(paste0(fig_save_path, "/", desired_name_part, "_Sbgb_global.svg"), plot = p2, width = 5, height = 5, units = "in")
  ggsave(paste0(fig_save_path, "/", desired_name_part, "_Sbgb_global.png"), plot = p2, width = 5, height = 5, units = "in", dpi = 300)
}

```

```{r plot and save agb scaler group map}
# library(ggplot2)
# library(dplyr)
# library(tidyr)
# library(patchwork) # For combining plots

for (data_idx in c(1,2,4)) {
  
  in_Sagb_file <- agb_files[data_idx]
  in_Sagb <- read.csv(in_Sagb_file, check.names = FALSE)
  
  agb_file_name <- basename(in_Sagb_file)
  desired_name_part <- sub("_fullscaler.*", "", agb_file_name)
  
  check_aboveCD_long <- in_Sagb %>%
    dplyr::select(-3, -2) %>%  
    group_by(region, harm_type) %>%
    summarize(across(.cols = 8:22, .fns = mean, na.rm = TRUE)) %>%
    ungroup() %>%
    pivot_longer(
      cols = 3:ncol(.),
      names_to = "year",
      values_to = "scaler"
    ) %>%
    mutate(year = as.numeric(year)) %>%
    na.omit()
  
  # Create individual line plots for each harm_type
  pc3 <- ggplot(check_aboveCD_long %>% filter(harm_type == "c3Crop"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
    geom_line() +
    labs(title = "agb c3Crop scaler",
         x = "Year",
         y = "Value",
         color = "Region") +
    theme_minimal()+
  theme(
    panel.border = element_rect(color = "black", fill = NA, size = 1)  # Add a black outline frame
  )
  
  pc4 <- ggplot(check_aboveCD_long %>% filter(harm_type == "c4Crop"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
    geom_line() +
    labs(title = "c4Crop agb scaler",
         x = "Year",
         y = "Value",
         color = "Region") +
    theme_minimal()+
  theme(
    panel.border = element_rect(color = "black", fill = NA, size = 1)  # Add a black outline frame
  )
  
  pf <- ggplot(check_aboveCD_long %>% filter(harm_type == "Forest"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
    geom_line() +
    labs(title = "Forest agb scaler",
         x = "Year",
         y = "Value",
         color = "Region") +
    theme_minimal()+
  theme(
    panel.border = element_rect(color = "black", fill = NA, size = 1)  # Add a black outline frame
  )
  
  pg <- ggplot(check_aboveCD_long %>% filter(harm_type == "Grass"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
    geom_line() +
    labs(title = "Grass agb scaler",
         x = "Year",
         y = "Value",
         color = "Region") +
    theme_minimal()+
  theme(
    panel.border = element_rect(color = "black", fill = NA, size = 1)  # Add a black outline frame
  )
  
  # Combine the plots into one grouped plot
  combined_plot <- (pc3 + pc4) / (pf + pg) + plot_annotation(title = paste0("Combined agb scaler_", desired_name_part))
  
  # Save the combined plot as an SVG file
  ggsave(paste0(fig_save_path, "/", desired_name_part, "_combined_Sagb_regions.svg"), plot = combined_plot, width = 20, height = 20, units = "in")
  ggsave(paste0(fig_save_path, "/", desired_name_part, "_combined_Sagb_regions.png"), plot = combined_plot, width = 20, height = 20, units = "in", dpi = 300)
  
  # Global mean plot
  check_aboveCD_long_gmean <- in_Sagb %>%
    dplyr::select(-3, -2) %>%  
    group_by(harm_type) %>%
    summarize(across(.cols = 7:22, .fns = mean, na.rm = TRUE)) %>%
    ungroup() %>%
    pivot_longer(
      cols = 2:ncol(.),
      names_to = "year",
      values_to = "scaler"
    ) %>%
    mutate(year = as.numeric(year)) %>%
    na.omit()
  
  p2 <- ggplot(check_aboveCD_long_gmean, aes(x = as.numeric(year), y = scaler, group = harm_type, color = harm_type)) +
    geom_line() +
    labs(title = paste0("Global mean agb scaler_", desired_name_part),
         x = "Year",
         y = "Value",
         color = "Broad Type") +
    theme_minimal()+
  theme(
    panel.border = element_rect(color = "black", fill = NA, size = 1)  # Add a black outline frame
  )+ ylim(c(0.97,1.6))
  
  # Save the global mean plot as an SVG file
  ggsave(paste0(fig_save_path, "/", desired_name_part, "_Sagb_global.svg"), plot = p2, width = 5, height = 5, units = "in")
  ggsave(paste0(fig_save_path, "/", desired_name_part, "_Sagb_global.png"), plot = p2, width = 5, height = 5, units = "in", dpi = 300)
}

```

```{r S5 check agb scaler}

# for (data_idx in 1:3) {
# 
#   
#   in_Sagb_file<-agb_files[data_idx]
# in_Sagb <-read.csv(in_Sagb_file,check.names = FALSE)
#   
# 
# agb_file_name <- basename(in_Sagb_file)
# desired_name_part <- sub("_fullscaler.*", "", agb_file_name)
# 
# check_aboveCD_long <- in_Sagb%>%
# dplyr::select(-3,-2) %>%  
#   filter( harm_type!= "Other")%>%
#     left_join(in_Harmolandtype_area,
#               by = c("out_reg_code", "out_lu_code", "harm_type")) %>%
#     
#     group_by(region, harm_type) %>%
#     mutate(region_pft_area = sum(pft_area_total, na.rm = TRUE)) %>%
#     mutate(region_pft_area_weight = pft_area_total / region_pft_area) %>%
#     summarize(across(
#       .cols = 8:22,
#       .fns = ~ weighted.mean(.x, w = region_pft_area_weight, na.rm = TRUE)
#     )) %>%
#     ungroup() %>%
#     pivot_longer(cols = 3:ncol(.),
#                  names_to = "year",
#                  values_to = "scaler") %>%
#     mutate(year = as.numeric(year)) %>%
#     na.omit()
# 
#   # Create a line plot for each region
# pc3<-ggplot(check_aboveCD_long%>%filter(harm_type=="c3Crop"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
#   geom_line() +
#   labs(title = paste0("agb c3Crop scaler_",desired_name_part),
#        x = "Year",
#        y = "Value",
#        color = "Region") +
#   theme_minimal()
# 
# pc4<-ggplot(check_aboveCD_long%>%filter(harm_type=="c4Crop"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
#   geom_line() +
#   labs(title = paste0("c4Crop agb scaler_",desired_name_part),
#        x = "Year",
#        y = "Value",
#        color = "Region") +
#   theme_minimal()
# 
# 
# pf<-ggplot(check_aboveCD_long%>%filter(harm_type=="Forest"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
#   geom_line() +
#   labs(title = paste0("Forest agb scaler_",desired_name_part),
#        x = "Year",
#        y = "Value",
#        color = "Region") +
#   theme_minimal()
# 
# pg<-ggplot(check_aboveCD_long%>%filter(harm_type=="Grass"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
#   geom_line() +
#   labs(title = paste0("Grass agb scaler_",desired_name_part),
#        x = "Year",
#        y = "Value",
#        color = "Region") +
#   theme_minimal()
# 
# ps<-ggplot(check_aboveCD_long%>%filter(harm_type=="Shrubland"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
#   geom_line() +
#   labs(title = paste0("Shrubland scaler_",desired_name_part),
#        x = "Year",
#        y = "Value",
#        color = "Region") +
#   theme_minimal()
# 
# ## save 
# 
# # Save the plot as an SVG file
# ggsave(paste0(fig_save_path,"/",desired_name_part,"_c3crop_Sagb_regions.svg"), plot = pc3, width = 10, height = 10, units = "in")
# ggsave(paste0(fig_save_path,"/",desired_name_part,"_c4crop_Sagb_regions.svg"), plot = pc4, width = 10, height = 10, units = "in")
# ggsave(paste0(fig_save_path,"/",desired_name_part,"_Forest_Sagb_regions.svg"), plot = pf, width = 10, height = 10, units = "in")
# ggsave(paste0(fig_save_path,"/",desired_name_part,"_Grass_Sagb_regions.svg"), plot = pg, width = 10, height = 10, units = "in")
# ggsave(paste0(fig_save_path,"/",desired_name_part,"_Shrubland_Sagb_regions.svg"), plot = ps, width = 10, height = 10, units = "in")
# 
# 
# 
# ####################################################################
# 
# 
# check_aboveCD_long_gmean <- in_Sagb%>%
# dplyr::select(-3,-2) %>%  
#    group_by(harm_type) %>%
#     summarize(across(.cols = 7:22, .fns = mean, na.rm = TRUE)) %>%
#     ungroup() %>%
#     pivot_longer(
#       cols = 2:ncol(.),
#       names_to = "year",
#       values_to = "scaler"
#     ) %>%
#     mutate(year = as.numeric(year)) %>%
#     na.omit()
# 
# 
# p2<-ggplot(check_aboveCD_long_gmean, aes(x = as.numeric(year), y = scaler, group = harm_type, color = harm_type)) +
#   geom_line() +
#   labs(title = paste0("global mean  agb scaler_",desired_name_part),
#        x = "Year",
#        y = "Value",
#        color = "harm_type") +
#   theme_minimal()
# 
# 
# 
# 
# 
# 
# 
# ## save 
# 
# # Save the plot as an SVG file
# ggsave(paste0(fig_save_path,"/",desired_name_part,"_Sagb_global.svg"), plot = p2, width = 10, height = 10, units = "in")
# ggsave(paste0(fig_save_path,"/",desired_name_part,"_Sagb_global.png"), plot = p2, width = 10, height = 10, units = "in", dpi = 300)
# 
# }

```

```{r S5 check bgb scaler}
# for (data_idx in 1:3) {
# 
#   
#   in_Sbgb_file<-bgb_files[data_idx]
# in_Sbgb <-read.csv(in_Sbgb_file,check.names = FALSE)
# 
# bgb_file_name <- basename(in_Sbgb_file)
# desired_name_part <- sub("_fullscaler.*", "", bgb_file_name)
# 
# check_belowCD_long <- in_Sbgb%>%
# dplyr::select(-3,-2) %>%  
#   group_by(region,harm_type)%>%
#   summarize(across(.cols = 8:22, .fns = mean, na.rm = TRUE))%>%
#   ungroup()%>%
#   pivot_longer(
#     cols = 3:ncol(.),
#     names_to = "year",
#     values_to = "scaler"
#   )%>%
#   mutate(year = as.numeric(year))%>%
#   na.omit()
# 
#   # Create a line plot for each region
# pc3<-ggplot(check_belowCD_long%>%filter(harm_type=="c3Crop"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
#   geom_line() +
#   labs(title = paste0("bgb c3Crop scaler_",desired_name_part),
#        x = "Year",
#        y = "Value",
#        color = "Region") +
#   theme_minimal()
# 
# pc4<-ggplot(check_belowCD_long%>%filter(harm_type=="c4Crop"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
#   geom_line() +
#   labs(title = paste0("bgb c4Crop scaler_",desired_name_part),
#        x = "Year",
#        y = "Value",
#        color = "Region") +
#   theme_minimal()
# 
# pf<-ggplot(check_belowCD_long%>%filter(harm_type=="Forest"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
#   geom_line() +
#   labs(title = paste0("bgb Forest scaler_",desired_name_part),
#        x = "Year",
#        y = "Value",
#        color = "Region") +
#   theme_minimal()
# 
# pg<-ggplot(check_belowCD_long%>%filter(harm_type=="Grass"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
#   geom_line() +
#   labs(title = paste0("bgb Grass scaler_",desired_name_part),
#        x = "Year",
#        y = "Value",
#        color = "Region") +
#   theme_minimal()
# 
# ps<-ggplot(check_belowCD_long%>%filter(harm_type=="Shrubland"), aes(x = as.numeric(year), y = scaler, group = region, color = region)) +
#   geom_line() +
#   labs(title = paste0("bgb Shrubland scaler_",desired_name_part),
#        x = "Year",
#        y = "Value",
#        color = "Region") +
#   theme_minimal()
# 
# ## save 
# 
# # Save the plot as an SVG file
# ggsave(paste0(fig_save_path,"/",desired_name_part,"_c3crop_Sbgb_regions.svg"), plot = pc3, width = 10, height = 10, units = "in")
# ggsave(paste0(fig_save_path,"/",desired_name_part,"_c4crop_Sbgb_regions.svg"), plot = pc4, width = 10, height = 10, units = "in")
# ggsave(paste0(fig_save_path,"/",desired_name_part,"_Forest_Sbgb_regions.svg"), plot = pf, width = 10, height = 10, units = "in")
# ggsave(paste0(fig_save_path,"/",desired_name_part,"_Grass_Sbgb_regions.svg"), plot = pg, width = 10, height = 10, units = "in")
# ggsave(paste0(fig_save_path,"/",desired_name_part,"_Shrubland_Sbgb_regions.svg"), plot = ps, width = 10, height = 10, units = "in")
# 
# 
# 
# ####################################################################
# 
# 
# check_belowCD_long_gmean <- in_Sbgb%>%
# dplyr::select(-3,-2) %>%  
#   group_by(harm_type)%>%
#   summarize(across(.cols = 7:22, .fns = mean, na.rm = TRUE))%>%
#   ungroup()%>%
#   pivot_longer(
#     cols = 2:ncol(.),
#     names_to = "year",
#     values_to = "scaler"
#   )%>%
#   mutate(year = as.numeric(year))%>%
#   na.omit()
# 
# 
# p2<-ggplot(check_belowCD_long_gmean, aes(x = as.numeric(year), y = scaler, group = harm_type, color = harm_type)) +
#   geom_line() +
#   labs(title = paste0("global mean  bgb scaler_",desired_name_part),
#        x = "Year",
#        y = "Value",
#        color = "harm_type") +
#   theme_minimal()
# 
# 
# 
# 
# 
# 
# 
# ## save 
# 
# # Save the plot as an SVG file
# ggsave(paste0(fig_save_path,"/",desired_name_part,"_Sbgb_global.svg"), plot = p2, width = 10, height = 10, units = "in")
# ggsave(paste0(fig_save_path,"/",desired_name_part,"_Sbgb_global.png"), plot = p2, width = 10, height = 10, units = "in", dpi = 300)
# 
# }

```

